---
title: "CPP hormone step 1 -- clean pubertal development data for caregiver and youth"
Written By: Megan M. Herting for CPP Puberty and Hormone ABCD
output: html_document
---
#####1ST THING TO DO: Clean up mis-match issues

#####2ND THING TO DO:Clean up PDS data

####  PLOT: sqc_qu_motion , fsqc_qu_pialover, fsqc_qu_wmunder, fsqc_qu_inhomogeneity, fsqc_qu_artifact

### FALSE discovery right -> rank p values and drop the non significant ones (narrow down on outcome data) FDR function for correcting for multiple comparisons https://stat.ethz.ch/R-manual/R-devel/library/stats/html/p.adjust.html

```{r}
rm(list=ls())
options(scipen=999)
require("tidyverse")
library(doBy)
library(Hmisc)
library(lme4)
library(lmerTest)
library(car)
require(lsmeans)
require(lattice)
require(ggpubr)
library(psych)
library(GGally)
library(here)
library(dplyr)
```

#1st step: read in data and reduce variables
```{r}
##Read in 3.0 data

data_dir = ((dirname(here()))) #figure out how to navigate to data source
data_folder <- file.path(data_dir,"ABCD","derivatives")  
file_name <- "nda20.csv" #specify file name here 
output_directory <- data_folder

nda30 <- read.table(file.path(data_folder,file_name),header=T, sep=",",as.is=TRUE,strip.white=TRUE,fill=TRUE)

#subset clean with all variables for analysis
##Let's reduce these variables to only those we care about
## This line is not working. Lucia to return to it after we have nda30 ready
## Also, Megan has used DEAP names, we are using NDA names. Need to update

myvars <- c("src_subject_id",
                    "interview_age",
                    "eventname",
                    "sex",
                    "site_id_l",
                    "mri_info_deviceserialnumber",
                    "rel_family_id",
                    "race.ethnicity.5level",
                    "race.eth.7level",
                    "demo_race_hispanic", # Do you consider the child Hispanic/Latino/Latina?
                    "high.educ",
                    "household.income",
                    "married.or.livingtogether",
                    "pds_1_p",
                    "pds_2_p",
                    "pds_3_p",
                    "pds_f4_p",
                    "pds_f5b_p",
                    "pds_f6_p",
                    "pds_m4_p",
                    "pds_m5_p",
                    )      


df<-  nda30  %>% 
  select (myvars)

df <- select = c('a' , 'b')

##Reduce to baseline data only N=11,875
df<- subset(df,eventname=="baseline_year_1_arm_1")


##Look at data formats
str(df)
describeBy(df, group=df$sex_at_birth)

##
write_rds(df, "df_puberty.rds")
```


###CAREGIVER REPORT -- CLEAN, VALIDATED, AND PREPARE FINAL SAMPLE
```{r}
##Let's create a caregiver PDS set to clean 
caregivervars <- c("src_subject_id", "eventname", "demo_prim_p", "interview_age", "sex_at_birth", "race_ethnicity",
"pubertdev_sex_p",
"pubertdev_select_language_p",
"pubertdev_1_p",
"pubertdev_2_p",
"pubertdev_3_p",
"pubertdev_m4_p",
"pubertdev_m5_p",
"pubertdev_f4_p",
"pubertdev_f5b_p",
"pubertdev_f6_p",
"pubertdev_f6_dk_p", 
"pubertdev_ss_female_category_p",
"pubertdev_ss_male_category_p",
"pubertdev_ss_male_cat_nt_p",
"pubertdev_ss_male_cat_nm_p",
"pubertdev_ss_female_cat_nt_p",
"pubertdev_ss_female_cat_nm_p")

df_caregiver <- df[caregivervars]
```


##STEP 1: Clean mis-match of data -- sex_at_birth = sex at birth
```{r}
##How many participants do we have for this analysis when we begin?
##Load library to explore data 
library(tidyverse)

library(dplyr)
df_caregiver %>% dplyr::count(sex_at_birth)

##Remove 6 people with blank sex_at_birth
df_caregiver<- df_caregiver[-which(is.na(df_caregiver$sex_at_birth)), ]
df_caregiver %>% dplyr::count(sex_at_birth)
```

### Check some more sex_at_birth/sex matching
```{r}
#PDS vs. sex_at_birth check
##Who has a PDS sex variable of "NA" and remove

df_caregiver %>%
dplyr::count(pubertdev_sex_p) ##5 NA
df_caregiver=df_caregiver[-c(which(is.na(df_caregiver$pubertdev_sex_p))),]

table(df_caregiver$sex_at_birth,df_caregiver$pubertdev_sex_p) ##Mismatch =63 


##Remove mismatches
df_caregiver <- df_caregiver[-c(which(df_caregiver$sex_at_birth == "M" & df_caregiver$pubertdev_sex_p == "Female"), which(df_caregiver$sex_at_birth == "F" & df_caregiver$pubertdev_sex_p == "Male")),]

##Check this worked and rerun descriptives
table(df_caregiver$sex_at_birth,df_caregiver$pubertdev_sex_p) #N=5659 F and N=6142 M

describeBy(df_caregiver, group=df_caregiver$sex_at_birth)

##Note NDAR_INV5D3CU8ML has Male sex_at_birth but female answers -- we will remove from dataset
c(which(df_caregiver$sex_at_birth == "M" & !is.na(df_caregiver$pubertdev_f4_p)))
df_caregiver=df_caregiver[-c(which(df_caregiver$sex_at_birth == "M" & !is.na(df_caregiver$pubertdev_f4_p))),]

##Final sample for PDS caregiver reporting = N=6141 MALES AND N=5659 FEMALES
xtabs(~df_caregiver$sex_at_birth+df_caregiver$pubertdev_sex_p)

```

#Get reporting of each item from caregiver
```{r}
##Now let's see what these caregivers report!
df_caregiver %>%
dplyr::count(pubertdev_select_language_p, pubertdev_sex_p)

##Double check the numbers For Table 1 to update tables: Note there are NO female answers for male questions and males answers for female questions --> Are cleaning worked
table(df_caregiver$pubertdev_1_p, df_caregiver$pubertdev_sex_p)
table(df_caregiver$pubertdev_2_p, df_caregiver$pubertdev_sex_p)
table(df_caregiver$pubertdev_3_p, df_caregiver$pubertdev_sex_p)
table(df_caregiver$pubertdev_m4_p, df_caregiver$pubertdev_sex_p)
table(df_caregiver$pubertdev_m5_p, df_caregiver$pubertdev_sex_p)
table(df_caregiver$pubertdev_f4_p, df_caregiver$pubertdev_sex_p)
table(df_caregiver$pubertdev_f5b_p, df_caregiver$pubertdev_sex_p)
table(df_caregiver$pubertdev_f6_p, df_caregiver$pubertdev_sex_p)

#Check the demographics of reporter for Don't know for menarche as inquired by Reviewer 1
xtabs(~df_caregiver$demo_prim_p+df_caregiver$pubertdev_f5b_p)
xtabs(~df_caregiver$race_ethnicity+df_caregiver$pubertdev_f5b_p)

```
#Make factors into numeric variables for equations below
```{r}
##PDS Recode categorical into variables with labels so we can sum and average; Note "I don't know is not numerically meaningful" so turned into NA for just these variables

df_caregiver$pubertdev_1_p_num=as.numeric(df_caregiver$pubertdev_1_p)
df_caregiver$pubertdev_1_p_num[df_caregiver$pubertdev_1_p_num == 5] <- NA
df_caregiver$pubertdev_2_p_num=as.numeric(df_caregiver$pubertdev_2_p)
df_caregiver$pubertdev_2_p_num[df_caregiver$pubertdev_2_p_num == 5] <- NA
df_caregiver$pubertdev_3_p_num=as.numeric(df_caregiver$pubertdev_3_p)
df_caregiver$pubertdev_3_p_num[df_caregiver$pubertdev_3_p_num == 5] <- NA
df_caregiver$pubertdev_m4_p_num=as.numeric(df_caregiver$pubertdev_m4_p)
df_caregiver$pubertdev_m4_p_num[df_caregiver$pubertdev_m4_p_num == 5] <- NA
df_caregiver$pubertdev_m5_p_num=as.numeric(df_caregiver$pubertdev_m5_p)
df_caregiver$pubertdev_m5_p_num[df_caregiver$pubertdev_m5_p_num == 5] <- NA
df_caregiver$pubertdev_f4_p_num=as.numeric(df_caregiver$pubertdev_f4_p)
df_caregiver$pubertdev_f4_p_num[df_caregiver$pubertdev_f4_p_num == 5] <- NA

#Make an empty variable
df_caregiver$pubertdev_f5b_p_num[df_caregiver$pubertdev_f5b_p == "Yes"] <- 4
df_caregiver$pubertdev_f5b_p_num[df_caregiver$pubertdev_f5b_p == "No"] <- 1

```

##Examine correlation of raw data for caregiver report
```{r}
##Split data base by male and female and only use those that have valid puberty
df_caregiverm=subset(df_caregiver, pubertdev_sex_p=="Male")
df_caregiverf=subset(df_caregiver, pubertdev_sex_p=="Female")

##Group female pds correlations
library(GGally)
keeps_pds_f=c("pubertdev_1_p_num","pubertdev_2_p_num", "pubertdev_3_p_num", "pubertdev_f4_p_num","pubertdev_f5b_p_num", "interview_age")
df_f_all_corr=ggpairs(df_caregiverf, keeps_pds_f, title = "Within PDS Females")
df_f_all_corr

##Group male pds correlations with age
keeps_pds_m=c("pubertdev_1_p_num","pubertdev_2_p_num", "pubertdev_3_p_num", "pubertdev_m4_p_num","pubertdev_m5_p_num", "interview_age")
df_m_all_corr=ggpairs(df_caregiverm, keeps_pds_m, title = "Within PDS Males")
df_m_all_corr
```

##PDS AVERAGE CAREGIVER- VALID AND COMPUTATION (4 OUT OF 5 VARIABLES NEEDED)
```{r}
#Male summary scores

#Sum puberty scores across rows for males. Then change female values for this field to NA
df_caregiver$pubertdev_maless_p <-rowSums(df_caregiver[,c("pubertdev_1_p_num","pubertdev_2_p_num", "pubertdev_3_p_num", "pubertdev_m4_p_num", "pubertdev_m5_p_num")], na.rm=T)
df_caregiver$pubertdev_maless_p[df_caregiver$pubertdev_maless_p == 0] <- NA
df_caregiver$pubertdev_maless_p[df_caregiver$sex_at_birth=="F"] <- NA

#Sum puberty scores across rows for females. Then change male values for this field to NA
df_caregiver$pubertdev_femaless_p <- rowSums(df_caregiver[,c("pubertdev_1_p_num","pubertdev_2_p_num", "pubertdev_3_p_num", "pubertdev_f4_p_num", "pubertdev_f5b_p_num")], na.rm=T)
df_caregiver$pubertdev_femaless_p[df_caregiver$pubertdev_femaless_p == 0] <- NA
df_caregiver$pubertdev_femaless_p[df_caregiver$sex_at_birth=="M"] <- NA

#Count number of Qs per subject in males that are not NA/DK
df_caregiver$pubertdev_males_Qcount_p <- rowSums(!is.na(df_caregiver[,c("pubertdev_1_p_num","pubertdev_2_p_num", "pubertdev_3_p_num", "pubertdev_m4_p_num", "pubertdev_m5_p_num")]))

df_caregiver$pubertdev_males_Qcount_p[df_caregiver$sex_at_birth=="F"] <- NA

#Count number of Qs per subject in females that are not NA/DK
df_caregiver$pubertdev_females_Qcount_p <- rowSums(!is.na(df_caregiver[,c("pubertdev_1_p_num","pubertdev_2_p_num", "pubertdev_3_p_num", "pubertdev_f4_p_num", "pubertdev_f5b_p_num")]))
df_caregiver$pubertdev_females_Qcount_p[df_caregiver$sex_at_birth=="M"] <- NA

#This will give total number of NAs in males per pubertdev column
apply(subset(df_caregiver, sex_at_birth=="M")[,c("pubertdev_1_p_num","pubertdev_2_p_num", "pubertdev_3_p_num", "pubertdev_m4_p_num", "pubertdev_m5_p_num")], 2, function(x) sum(is.na(x)))
#And total number of NAs in females per pubertdev column
apply(subset(df_caregiver, sex_at_birth=="F")[,c("pubertdev_1_p_num","pubertdev_2_p_num", "pubertdev_3_p_num", "pubertdev_f4_p_num", "pubertdev_f5b_p_num")], 2, function(x) sum(is.na(x)))

#If more than 1 IDK/NA for males. Then code to not valid.
df_caregiver$pubertdev_males_valid_for_avg<-NA
df_caregiver$pubertdev_males_valid_for_avg <- ifelse(df_caregiver$sex_at_birth=="M" & df_caregiver$pubertdev_males_Qcount_p>=4, 1, 0)

#If more than 1 IDK/NA for females. Then code to not valid.
df_caregiver$pubertdev_females_valid_for_avg<-NA
df_caregiver$pubertdev_females_valid_for_avg <- ifelse(df_caregiver$sex_at_birth=="F" & df_caregiver$pubertdev_females_Qcount_p>=4, 1, 0)

##Count who is valid
df_caregiver %>% dplyr::count(pubertdev_females_valid_for_avg)
df_caregiver %>% dplyr::count(pubertdev_males_valid_for_avg)

##Count who is valid based on sex 
xtabs(~df_caregiver$pubertdev_males_valid_for_avg+df_caregiver$pubertdev_sex_p)
xtabs(~df_caregiver$pubertdev_females_valid_for_avg+df_caregiver$pubertdev_sex_p)

##ONLY for valid PDS calculate the folowing meaningful average and category scores of puberty: 
##Calculate average of PDS values for males for only those with valid data (see definition of valid above)
df_caregiver$pubertdev_maleAvg_p <- df_caregiver$pubertdev_maless_p/df_caregiver$pubertdev_males_Qcount_p
df_caregiver$pubertdev_maleAvg_p[df_caregiver$pubertdev_males_valid_for_avg==0] <- NA

##Calculate average of PDS values for females for only those with valid data (see definition of valid above)
df_caregiver$pubertdev_femaleAvg_p <- df_caregiver$pubertdev_femaless_p/df_caregiver$pubertdev_females_Qcount_p
df_caregiver$pubertdev_femaleAvg_p[df_caregiver$pubertdev_females_valid_for_avg==0] <- NA

#Make a single variable for PDS Average
df_caregiver$pubertdev_Avg_p_all<-coalesce(df_caregiver$pubertdev_femaleAvg_p,df_caregiver$pubertdev_maleAvg_p)

##Plot the data
M_Avg=ggplot(subset(df_caregiver, sex_at_birth=="M"),aes(x=pubertdev_maleAvg_p))+geom_histogram(position="dodge",na.rm = TRUE,alpha=0.5,binwidth=0.25)+theme_bw()
F_Avg=ggplot(subset(df_caregiver, sex_at_birth=="F"),aes(x=pubertdev_femaleAvg_p))+geom_histogram(position="dodge",na.rm = TRUE,alpha=0.5,binwidth=0.25)+theme_bw()

Both_Avg=ggplot(df_caregiver,aes(x=pubertdev_Avg_p_all,group=sex_at_birth,fill=sex_at_birth))+geom_histogram(na.rm = TRUE,alpha=0.5,binwidth=0.25)+theme_bw()


##Fancy plots
install.packages("devtools")
library(devtools)
install_github("kassambara/easyGgplot2")
library(easyGgplot2)
AvgPDS=ggplot2.histogram(data=df_caregiver, xName='pubertdev_Avg_p_all',binwidth=0.2,
    groupName='sex_at_birth', legendPosition="top",
        alpha=0.3, position="identity")+theme_bw()+theme(axis.text.x  = element_text(size=12), axis.text.y  = element_text(size=12))+theme( axis.title.x=element_blank(), axis.title.y=element_blank())+facet_grid(~sex_at_birth)
ggsave(AvgPDS,  file="AvgPDS.tiff", width = 12, height = 8, units = "in",
  dpi = 300)

ggplot2.histogram(data=df_caregiver, xName='pubertdev_Avg_p_all',addDensity=TRUE,groupName='sex_at_birth', legendPosition="top",alpha=0.5,addMeanLine=TRUE, meanLineColor="white", meanLineSize=1.5, binwidth=.2)+theme_bw()

```
  
##CROCKETT TANNER STAGE CAREGIVER REPORT- VALID AND COMPUTATION (3 OUT OF 3 VARIABLES NEEDED)
```{r}
##Check category score already in NDAR dataset
##How many  missing
xtabs(~df_caregiver$pubertdev_ss_female_cat_nm_p+df_caregiver$pubertdev_sex_p)
xtabs(~df_caregiver$pubertdev_ss_male_cat_nm_p+df_caregiver$pubertdev_sex_p)

##Make a single variable
df_caregiver$pubertdev_ss_category_p_all<-coalesce(df_caregiver$pubertdev_ss_female_category_p, df_caregiver$pubertdev_ss_male_category_p)

##Code into Tanner Stage Based on Petersen, A. C., Crockett, L., et al. (1988) A self-report measure of pubertal status: Reliability, validity, and initial norms. J Youth Adolesc 17(2): 117-133. Puberty Category Scores for boys used body hair growth, voice... https://www.jahonline.org/article/1054-139X(93)90004-9/pdf

# MALES Prepubertal = 3; early Pubertal = 4 or 5 (no 3-point responses); Midpubertal = 6,7, or 8 (no 4-point responses; Late pubertal = 9-11; Postpubertal = 12. 


## FEMALES Prepubertal = 3; Early Puberty = 3 and no menarche; Midpubertal = 4 and no menarche; Late Puberty = <=7 and menarche; Postpubertal = 8 and menarche

df_caregiver$pubertdev_ss_category_p_all<-factor(df_caregiver$pubertdev_ss_category_p_all,
levels = c(1,2,3,4,5), labels=c("Pre", "Early", "Mid", "Late","Post"))

xtabs(~df_caregiver$pubertdev_ss_category_p_all+df_caregiver$pubertdev_sex_p)

PubertyCategory=ggplot(subset(df_caregiver, !is.na(pubertdev_ss_category_p_all)),aes(x=factor(pubertdev_ss_category_p_all,levels=c("Pre", "Early", "Mid", "Late","Post")),group=sex_at_birth,fill=sex_at_birth))+geom_histogram(stat="count",position="dodge",na.rm = TRUE,alpha=0.5,binwidth=0.25)+theme_bw()+theme(axis.text.x  = element_text(size=12), axis.text.y  = element_text(size=12))+theme( axis.title.x=element_blank(), axis.title.y=element_blank())+facet_grid(~sex_at_birth)


ggsave(PubertyCategory,  file="PubertyCategory.tiff", width = 12, height = 8, units = "in",
  dpi = 300)

```

##GONADAL AND ADRENAL AVERAGES FOR CAREGIVER REPORT- VALID AND COMPUTATION (3 OUT OF 3 VARIABLES NEEDED FOR GONAD AND 2/2 for ADRENAL)
```{r}
##Shirtcliff 2009 method: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2727719/; In girls, growth spurt, breast development, and menarche are associated with gonadal hormonal signals. In boys, growth spurt, deepening of voice and facial hair growth are associated with gonadal hormones. For both sexes, pubic/body hair and skin changes are associated with adrenal hormones. Doesn't say if items were summed or averaged. To be consistent with Herting et al 2017, we will average.

#Male Gonads
df_caregiver$pubertdev_malegonadss_p <-rowSums(df_caregiver[,c("pubertdev_1_p_num", "pubertdev_m4_p_num", "pubertdev_m5_p_num")], na.rm=T)
df_caregiver$pubertdev_malegonad_Qcount_p <- rowSums(!is.na(df_caregiver[,c("pubertdev_1_p_num", "pubertdev_m4_p_num", "pubertdev_m5_p_num")]))
df_caregiver$pubertdev_malegonad_Qcount_p[df_caregiver$pubertdev_malegonad_Qcount_p == 0] <- NA
df_caregiver$pubertdev_malegonad_Qcount_p[df_caregiver$sex_at_birth=="F"] <- NA

#ANY IDK/NA for males in these 3 variables for gonad. Then code to not valid.
df_caregiver$pubertdev_males_valid_for_gonad<-NA
df_caregiver$pubertdev_males_valid_for_gonad<-ifelse(df_caregiver$sex_at_birth=="M" & df_caregiver$pubertdev_malegonad_Qcount_p==3, 1, 0)


#Compute male gonad avg
df_caregiver$pubertdev_malegonadAvg_p <- df_caregiver$pubertdev_malegonadss_p/df_caregiver$pubertdev_malegonad_Qcount_p
df_caregiver$pubertdev_malegonadAvg_p[df_caregiver$pubertdev_males_valid_for_gonad==0] <- NA


#Female Gonads
df_caregiver$pubertdev_femalegonadss_p <-rowSums(df_caregiver[,c("pubertdev_1_p_num", "pubertdev_f4_p_num", "pubertdev_f5b_p_num")], na.rm=T)
df_caregiver$pubertdev_femalegonad_Qcount_p <- rowSums(!is.na(df_caregiver[,c("pubertdev_1_p_num", "pubertdev_f4_p_num", "pubertdev_f5b_p_num")]))
df_caregiver$pubertdev_femalegonad_Qcount_p[df_caregiver$pubertdev_femalegonad_Qcount_p == 0] <- NA
df_caregiver$pubertdev_femalegonad_Qcount_p[df_caregiver$sex_at_birth=="M"] <- NA

#ANY IDK/NA for males in these 3 variables for gonad. Then code to not valid.
df_caregiver$pubertdev_females_valid_for_gonad<-NA
df_caregiver$pubertdev_females_valid_for_gonad<-ifelse(df_caregiver$sex_at_birth=="F" & df_caregiver$pubertdev_femalegonad_Qcount_p==3, 1, 0)

#Compute female gonad avg
df_caregiver$pubertdev_femalegonadAvg_p <- df_caregiver$pubertdev_femalegonadss_p/df_caregiver$pubertdev_femalegonad_Qcount_p
df_caregiver$pubertdev_femalegonadAvg_p[df_caregiver$pubertdev_females_valid_for_gonad==0] <- NA

##Count who is valid based on sex 
xtabs(~df_caregiver$pubertdev_males_valid_for_gonad+df_caregiver$pubertdev_sex_p)
xtabs(~df_caregiver$pubertdev_females_valid_for_gonad+df_caregiver$pubertdev_sex_p)

#Adrenal
df_caregiver$pubertdevadrenalss_p <-rowSums(df_caregiver[,c("pubertdev_2_p_num", "pubertdev_3_p_num")], na.rm=T)
df_caregiver$pubertdev_adrenal_Qcount_p <- rowSums(!is.na(df_caregiver[,c("pubertdev_2_p_num", "pubertdev_3_p_num")]))
df_caregiver$pubertdev_adrenal_Qcount_p[df_caregiver$pubertdev_adrenal_Qcount_p == 0] <- NA

#ANY IDK/NA in these 2 variables for adrenal. Then code to not valid.
df_caregiver$pubertdev_valid_for_adrenal<-NA
df_caregiver$pubertdev_valid_for_adrenal<-ifelse(df_caregiver$pubertdev_adrenal_Qcount_p==2, 1, 0)

##Count who is valid based on sex 
xtabs(~df_caregiver$pubertdev_valid_for_adrenal+df_caregiver$pubertdev_sex_p)

#Compute adrenal avg
df_caregiver$pubertdev_adrenalAvg_p <- df_caregiver$pubertdevadrenalss_p/df_caregiver$pubertdev_adrenal_Qcount_p
df_caregiver$pubertdev_adrenalAvg_p[df_caregiver$pubertdev_valid_for_adrenal==0] <- NA

##Plot the data
Avg_adrenal=ggplot(df_caregiver,aes(x=pubertdev_adrenalAvg_p,group=sex_at_birth,fill=sex_at_birth))+geom_histogram(position="dodge",na.rm = TRUE,alpha=0.5,binwidth=0.25)+theme_bw()

df_caregiver$pubertdev_gonadAvg_p_all<-coalesce(df_caregiver$pubertdev_femalegonadAvg_p,df_caregiver$pubertdev_malegonadAvg_p)

AdrenalAvg=ggplot2.histogram(data=df_caregiver, xName='pubertdev_adrenalAvg_p' ,binwidth=0.5,
    groupName='sex_at_birth', legendPosition="top",
        alpha=0.3, position="identity")+theme_bw()+theme(axis.text.x  = element_text(size=12), axis.text.y  = element_text(size=12))+theme( axis.title.x=element_blank(), axis.title.y=element_blank())+facet_grid(~sex_at_birth)

ggsave(AdrenalAvg,  file="AdrenalAvg.tiff", width = 12, height = 8, units = "in",
  dpi = 300)

GonadalAvg=ggplot2.histogram(data=df_caregiver, xName='pubertdev_gonadAvg_p_all' ,binwidth=0.5,
    groupName='sex_at_birth', legendPosition="top",
        alpha=0.3, position="identity")+theme_bw()+theme(axis.text.x  = element_text(size=12), axis.text.y  = element_text(size=12))+theme( axis.title.x=element_blank(), axis.title.y=element_blank())+facet_grid(~sex_at_birth)

ggsave(GonadalAvg,  file="GonadalAvg.tiff", width = 12, height = 8, units = "in",
  dpi = 300)

ggplot2.histogram(data=df_caregiver, xName='pubertdev_adrenalAvg_p',addDensity=TRUE,groupName='sex_at_birth', legendPosition="top",alpha=0.5,addMeanLine=TRUE, meanLineColor="white", meanLineSize=1.5, binwidth=.5)+theme_bw()

ggplot2.histogram(data=df_caregiver, xName='pubertdev_gonadAvg_p_all',addDensity=TRUE,groupName='sex_at_birth', legendPosition="top",alpha=0.5,addMeanLine=TRUE, meanLineColor="white", meanLineSize=1.5, binwidth=.5)+theme_bw()

```

```{r}
##Create CAREGIVER PDS dataset for covariates in other projects
PDSCaregivervars <- c("src_subject_id", "sex_at_birth", "eventname", "demo_prim_p", "interview_age", "pubertdev_sex_p", "pubertdev_Avg_p_all","pubertdev_ss_category_p_all", "pubertdev_gonadAvg_p_all", "pubertdev_adrenalAvg_p","pubertdev_1_p","pubertdev_2_p", "pubertdev_3_p", "pubertdev_m4_p", "pubertdev_m5_p", "pubertdev_f4_p", "pubertdev_f5b_p", "pubertdev_1_p_num","pubertdev_2_p_num", "pubertdev_3_p_num", "pubertdev_m4_p_num", "pubertdev_m5_p_num", "pubertdev_f4_p_num", "pubertdev_f5b_p_num")
PDSCaregiver <- df_caregiver[PDSCaregivervars]
saveRDS(PDSCaregiver, "PDS_caregiver_clean.rds")
```

###CHILD SELF-REPORT -- CLEAN, VALIDATED, AND PREPARE FINAL SAMPLE
```{r}
##Remove previous variables and datasets to reduce mistakes
rm(list=ls())
df<-readRDS("df_pubertyCPP.rds")

##Let's create a caregiver PDS set to clean 
youthvars <- c("src_subject_id", "eventname", "demo_prim_p", "interview_age", "sex_at_birth", 
"pubertdev_sex",
"pubertdev_ht",
"pubertdev_bdyhair",
"pubertdev_skin",
"pubertdev_m4",
"pubertdev_m5",
"pubertdev_f4",
"pubertdev_f5",
"pubertdev_f6",
"pubertdev_f6_dk",
"pubertdev_ss_female_category",
"pubertdev_ss_male_category",
"pubertdev_ss_male_cat_nt",
"pubertdev_ss_male_cat_nm",
"pubertdev_ss_female_cat_nt",
"pubertdev_ss_female_cat_nm")

df_youth <- df[youthvars]

```

##STEP 1: Clean mis-match of data -- sex_at_birth = sex at birth/sex matching
```{r}
##Remove 6 people with blank sex_at_birth
df_youth<- df_youth[-which(is.na(df_youth$sex_at_birth)), ]
df_youth %>% dplyr::count(sex_at_birth)

### Check some more sex_at_birth/sex matching

#PDS vs. sex_at_birth check
##Who has a PDS sex variable of "NA" and remove

df_youth %>%
dplyr::count(pubertdev_sex) ##20
df_youth=df_youth[-c(which(is.na(df_youth$pubertdev_sex))),]

table(df_youth$sex_at_birth,df_youth$pubertdev_sex) ##Mismatch 63 

##Remove mismatches
df_youth <- df_youth[-c(which(df_youth$sex_at_birth == "M" & df_youth$pubertdev_sex == "Female"), which(df_youth$sex_at_birth == "F" & df_youth$pubertdev_sex == "Male")),]

##Check this worked and rerun descriptives
table(df_youth$sex_at_birth,df_youth$pubertdev_sex) #N=5628 F and N=6158 M

describeBy(df_youth, group=df_youth$sex_at_birth)

##Final sample for PDS youth reporting #N=5628 F and N=6158 M
table(df_youth$sex_at_birth,df_youth$pubertdev_sex) 

```

#Get reporting from youth for each item
```{r}
##Now let's see what these youth report!

##Double check the numbers For Table 1 to update tables: Note there are NO female answers for male questions and males answers for female questions --> Are cleaning worked
table(df_youth$pubertdev_ht, df_youth$pubertdev_sex)
table(df_youth$pubertdev_bdyhair, df_youth$pubertdev_sex)
table(df_youth$pubertdev_skin, df_youth$pubertdev_sex)
table(df_youth$pubertdev_m4, df_youth$pubertdev_sex)
table(df_youth$pubertdev_m5, df_youth$pubertdev_sex)
table(df_youth$pubertdev_f4, df_youth$pubertdev_sex)
table(df_youth$pubertdev_f5, df_youth$pubertdev_sex)
table(df_youth$pubertdev_f6, df_youth$pubertdev_sex)

##See the average age of those that don't know if they have menarche per reviewer 1's inquiry.
describeBy(df_youth$interview_age, group=df_youth$pubertdev_f5)
```
```{r}
##PDS Recode categorical into variables with labels so we can sum and average; Note "I don't know is not numerically meaningful" so turned into NA for just these variables

df_youth$pubertdev_ht_num=as.numeric(df_youth$pubertdev_ht)
df_youth$pubertdev_ht_num[df_youth$pubertdev_ht_num == 5] <- NA
df_youth$pubertdev_ht_num[df_youth$pubertdev_ht_num == 6] <- NA
df_youth$pubertdev_bdyhair_num=as.numeric(df_youth$pubertdev_bdyhair)
df_youth$pubertdev_bdyhair_num[df_youth$pubertdev_bdyhair_num == 5] <- NA
df_youth$pubertdev_bdyhair_num[df_youth$pubertdev_bdyhair_num == 6] <- NA
df_youth$pubertdev_skin_num=as.numeric(df_youth$pubertdev_skin)
df_youth$pubertdev_skin_num[df_youth$pubertdev_skin_num == 5] <- NA
df_youth$pubertdev_skin_num[df_youth$pubertdev_skin_num == 6] <- NA
df_youth$pubertdev_m4_num=as.numeric(df_youth$pubertdev_m4)
df_youth$pubertdev_m4_num[df_youth$pubertdev_m4_num == 5] <- NA
df_youth$pubertdev_m4_num[df_youth$pubertdev_m4_num == 6] <- NA
df_youth$pubertdev_m5_num=as.numeric(df_youth$pubertdev_m5)
df_youth$pubertdev_m5_num[df_youth$pubertdev_m5_num == 5] <- NA
df_youth$pubertdev_m5_num[df_youth$pubertdev_m5_num == 6] <- NA
df_youth$pubertdev_f4_num=as.numeric(df_youth$pubertdev_f4)
df_youth$pubertdev_f4_num[df_youth$pubertdev_f4_num == 5] <- NA
df_youth$pubertdev_f4_num[df_youth$pubertdev_f4_num == 6] <- NA
#Make an empty variable
df_youth$pubertdev_f5_num[df_youth$pubertdev_f5 == "Yes"] <- 4
df_youth$pubertdev_f5_num[df_youth$pubertdev_f5 == "No"] <- 1

```

##Examine correlation of raw data for youth
```{r}
##Split data base by male and female and only use those that have valid puberty
df_youthm=subset(df_youth, pubertdev_sex=="Male")
df_youthf=subset(df_youth, pubertdev_sex=="Female")

##Group female pds correlations
library(GGally)
keeps_pds_f=c("pubertdev_ht_num","pubertdev_bdyhair_num", "pubertdev_skin_num", "pubertdev_f4_num","pubertdev_f5_num", "interview_age")
df_f_all_corr=ggpairs(df_youthf, keeps_pds_f, title = "Within PDS Females")
df_f_all_corr

##Group male pds correlations with age
keeps_pds_m=c("pubertdev_ht_num","pubertdev_bdyhair_num", "pubertdev_skin_num", "pubertdev_m4_num","pubertdev_m5_num", "interview_age")
df_m_all_corr=ggpairs(df_youthm, keeps_pds_m, title = "Within PDS Males")
df_m_all_corr
```

##PDS AVERAGE YOUTH- VALID AND COMPUTATION (4 OUT OF 5 VARIABLES NEEDED)
```{r}
#Male summary scores

#Sum puberty scores across rows for males. Then change female values for this field to NA
df_youth$pubertdev_maless <-rowSums(df_youth[,c("pubertdev_ht_num","pubertdev_bdyhair_num", "pubertdev_skin_num", "pubertdev_m4_num", "pubertdev_m5_num")], na.rm=T)
df_youth$pubertdev_maless[df_youth$pubertdev_maless == 0] <- NA
df_youth$pubertdev_maless[df_youth$sex_at_birth=="F"] <- NA

#Sum puberty scores across rows for females. Then change male values for this field to NA
df_youth$pubertdev_femaless <- rowSums(df_youth[,c("pubertdev_ht_num","pubertdev_bdyhair_num", "pubertdev_skin_num", "pubertdev_f4_num", "pubertdev_f5_num")], na.rm=T)
df_youth$pubertdev_femaless[df_youth$pubertdev_femaless == 0] <- NA
df_youth$pubertdev_femaless[df_youth$sex_at_birth=="M"] <- NA

#Count number of Qs per subject in males that are not NA/DK
df_youth$pubertdev_males_Qcount <- rowSums(!is.na(df_youth[,c("pubertdev_ht_num","pubertdev_bdyhair_num", "pubertdev_skin_num", "pubertdev_m4_num", "pubertdev_m5_num")]))

df_youth$pubertdev_males_Qcount[df_youth$sex_at_birth=="F"] <- NA

#Count number of Qs per subject in females that are not NA/DK
df_youth$pubertdev_females_Qcount <- rowSums(!is.na(df_youth[,c("pubertdev_ht_num","pubertdev_bdyhair_num", "pubertdev_skin_num", "pubertdev_f4_num", "pubertdev_f5_num")]))
df_youth$pubertdev_females_Qcount[df_youth$sex_at_birth=="M"] <- NA

#This will give total number of NAs in males per pubertdev column
apply(subset(df_youth, sex_at_birth=="M")[,c("pubertdev_ht_num","pubertdev_bdyhair_num", "pubertdev_skin_num", "pubertdev_m4_num", "pubertdev_m5_num")], 2, function(x) sum(is.na(x)))
#And total number of NAs in females per pubertdev column
apply(subset(df_youth, sex_at_birth=="F")[,c("pubertdev_ht_num","pubertdev_bdyhair_num", "pubertdev_skin_num", "pubertdev_f4_num", "pubertdev_f5_num")], 2, function(x) sum(is.na(x)))

#If more than 1 IDK/NA for males. Then code to not valid.
df_youth$pubertdev_males_valid_for_avg<-NA
df_youth$pubertdev_males_valid_for_avg <- ifelse(df_youth$sex_at_birth=="M" & df_youth$pubertdev_males_Qcount>=4, 1, 0)

#If more than 1 IDK/NA for females. Then code to not valid.
df_youth$pubertdev_females_valid_for_avg<-NA
df_youth$pubertdev_females_valid_for_avg <- ifelse(df_youth$sex_at_birth=="F" & df_youth$pubertdev_females_Qcount>=4, 1, 0)

##Count who is valid
df_youth %>% dplyr::count(pubertdev_females_valid_for_avg)
df_youth %>% dplyr::count(pubertdev_males_valid_for_avg)

##Count who is valid based on sex 
xtabs(~df_youth$pubertdev_males_valid_for_avg+df_youth$pubertdev_sex)
xtabs(~df_youth$pubertdev_females_valid_for_avg+df_youth$pubertdev_sex)

##ONLY for valid PDS calculate the folowing meaningful average and category scores of puberty: 
##Calculate average of PDS values for males for only those with valid data (see definition of valid above)
df_youth$pubertdev_maleAvg <- df_youth$pubertdev_maless/df_youth$pubertdev_males_Qcount
df_youth$pubertdev_maleAvg[df_youth$pubertdev_males_valid_for_avg==0] <- NA

##Calculate average of PDS values for females for only those with valid data (see definition of valid above)
df_youth$pubertdev_femaleAvg <- df_youth$pubertdev_femaless/df_youth$pubertdev_females_Qcount
df_youth$pubertdev_femaleAvg[df_youth$pubertdev_females_valid_for_avg==0] <- NA

#Make a single variable for PDS Average
df_youth$pubertdev_Avg_all<-coalesce(df_youth$pubertdev_femaleAvg,df_youth$pubertdev_maleAvg)

##Plot the data
M_Avg=ggplot(subset(df_youth, sex_at_birth=="M"),aes(x=pubertdev_maleAvg))+geom_histogram(position="dodge",na.rm = TRUE,alpha=0.5,binwidth=0.25)+theme_bw()
F_Avg=ggplot(subset(df_youth, sex_at_birth=="F"),aes(x=pubertdev_femaleAvg))+geom_histogram(position="dodge",na.rm = TRUE,alpha=0.5,binwidth=0.25)+theme_bw()

Both_Avg=ggplot(df_youth,aes(x=pubertdev_Avg_all,group=sex_at_birth,fill=sex_at_birth))+geom_histogram(na.rm = TRUE,alpha=0.5,binwidth=0.25)+theme_bw()


##Fancy plots
install.packages("devtools")
library(devtools)
install_github("kassambara/easyGgplot2")
library(easyGgplot2)
AvgPDS=ggplot2.histogram(data=df_youth, xName='pubertdev_Avg_all',binwidth=0.2,
    groupName='sex_at_birth', legendPosition="top",
        alpha=0.3, position="identity")+theme_bw()+theme(axis.text.x  = element_text(size=12), axis.text.y  = element_text(size=12))+theme( axis.title.x=element_blank(), axis.title.y=element_blank())+facet_grid(~sex_at_birth)
ggsave(AvgPDS,  file="AvgPDS_youth.tiff", width = 12, height = 8, units = "in",
  dpi = 300)

ggplot2.histogram(data=df_youth, xName='pubertdev_Avg_all',addDensity=TRUE,groupName='sex_at_birth', legendPosition="top",alpha=0.5,addMeanLine=TRUE, meanLineColor="white", meanLineSize=1.5, binwidth=.2)+theme_bw()

```


##CROCKETT TANNER STAGE YOUTH REPORT- VALID AND COMPUTATION (3 OUT OF 3 VARIABLES NEEDED)
```{r}
##Check category score already in NDAR dataset
##How many  missing
xtabs(~df_youth$pubertdev_ss_female_cat_nm+df_youth$pubertdev_sex)
xtabs(~df_youth$pubertdev_ss_male_cat_nm+df_youth$pubertdev_sex)

##Make a single variable
df_youth$pubertdev_ss_category_all<-coalesce(df_youth$pubertdev_ss_female_category, df_youth$pubertdev_ss_male_category)

##Code into Tanner Stage Based on Petersen, A. C., Crockett, L., et al. (1988) A self-report measure of pubertal status: Reliability, validity, and initial norms. J Youth Adolesc 17(2): 117-133. Puberty Category Scores for boys used body hair growth, voice... https://www.jahonline.org/article/1054-139X(93)90004-9/pdf

# MALES Prepubertal = 3; early Pubertal = 4 or 5 (no 3-point responses); Midpubertal = 6,7, or 8 (no 4-point responses; Late pubertal = 9-11; Postpubertal = 12. 


## FEMALES Prepubertal = 3; Early Puberty = 3 and no menarche; Midpubertal = 4 and no menarche; Late Puberty = <=7 and menarche; Postpubertal = 8 and menarche

df_youth$pubertdev_ss_category_all<-factor(df_youth$pubertdev_ss_category_all,
levels = c(1,2,3,4,5), labels=c("Pre", "Early", "Mid", "Late","Post"))

xtabs(~df_youth$pubertdev_ss_category_all+df_youth$pubertdev_sex)

PubertyCategory=ggplot(subset(df_youth, !is.na(pubertdev_ss_category_all)),aes(x=factor(pubertdev_ss_category_all,levels=c("Pre", "Early", "Mid", "Late","Post")),group=sex_at_birth,fill=sex_at_birth))+geom_histogram(stat="count",position="dodge",na.rm = TRUE,alpha=0.5,binwidth=0.25)+theme_bw()+theme(axis.text.x  = element_text(size=12), axis.text.y  = element_text(size=12))+theme( axis.title.x=element_blank(), axis.title.y=element_blank())+facet_grid(~sex_at_birth)


ggsave(PubertyCategory,  file="PubertyCategory_Youth.tiff", width = 12, height = 8, units = "in",
  dpi = 300)

```


##GONADAL AND ADRENAL AVERAGES FOR YOUTH REPORT- VALID AND COMPUTATION (3 OUT OF 3 VARIABLES NEEDED FOR GONAD AND 2/2 for ADRENAL)
```{r}
##Shirtcliff 2009 method: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2727719/; In girls, growth spurt, breast development, and menarche are associated with gonadal hormonal signals. In boys, growth spurt, deepening of voice and facial hair growth are associated with gonadal hormones. For both sexes, pubic/body hair and skin changes are associated with adrenal hormones. Doesn't say if items were summed or averaged. To be consistent with Herting et al 2017, we will average.

#Male Gonads
df_youth$pubertdev_malegonadss <-rowSums(df_youth[,c("pubertdev_ht_num", "pubertdev_m4_num", "pubertdev_m5_num")], na.rm=T)
df_youth$pubertdev_malegonad_Qcount <- rowSums(!is.na(df_youth[,c("pubertdev_ht_num", "pubertdev_m4_num", "pubertdev_m5_num")]))
df_youth$pubertdev_malegonad_Qcount[df_youth$pubertdev_malegonad_Qcount == 0] <- NA
df_youth$pubertdev_malegonad_Qcount[df_youth$sex_at_birth=="F"] <- NA

#ANY IDK/NA for males in these 3 variables for gonad. Then code to not valid.
df_youth$pubertdev_males_valid_for_gonad<-NA
df_youth$pubertdev_males_valid_for_gonad<-ifelse(df_youth$sex_at_birth=="M" & df_youth$pubertdev_malegonad_Qcount==3, 1, 0)


#Compute male gonad avg
df_youth$pubertdev_malegonadAvg <- df_youth$pubertdev_malegonadss/df_youth$pubertdev_malegonad_Qcount
df_youth$pubertdev_malegonadAvg[df_youth$pubertdev_males_valid_for_gonad==0] <- NA


#Female Gonads
df_youth$pubertdev_femalegonadss <-rowSums(df_youth[,c("pubertdev_ht_num", "pubertdev_f4_num", "pubertdev_f5_num")], na.rm=T)
df_youth$pubertdev_femalegonad_Qcount <- rowSums(!is.na(df_youth[,c("pubertdev_ht_num", "pubertdev_f4_num", "pubertdev_f5_num")]))
df_youth$pubertdev_femalegonad_Qcount[df_youth$pubertdev_femalegonad_Qcount == 0] <- NA
df_youth$pubertdev_femalegonad_Qcount[df_youth$sex_at_birth=="M"] <- NA

#ANY IDK/NA for males in these 3 variables for gonad. Then code to not valid.
df_youth$pubertdev_females_valid_for_gonad<-NA
df_youth$pubertdev_females_valid_for_gonad<-ifelse(df_youth$sex_at_birth=="F" & df_youth$pubertdev_femalegonad_Qcount==3, 1, 0)

#Compute female gonad avg
df_youth$pubertdev_femalegonadAvg <- df_youth$pubertdev_femalegonadss/df_youth$pubertdev_femalegonad_Qcount
df_youth$pubertdev_femalegonadAvg[df_youth$pubertdev_females_valid_for_gonad==0] <- NA

##Count who is valid based on sex 
xtabs(~df_youth$pubertdev_males_valid_for_gonad+df_youth$pubertdev_sex)
xtabs(~df_youth$pubertdev_females_valid_for_gonad+df_youth$pubertdev_sex)

#Adrenal
df_youth$pubertdevadrenalss_p <-rowSums(df_youth[,c("pubertdev_bdyhair_num", "pubertdev_skin_num")], na.rm=T)
df_youth$pubertdev_adrenal_Qcount <- rowSums(!is.na(df_youth[,c("pubertdev_bdyhair_num", "pubertdev_skin_num")]))
df_youth$pubertdev_adrenal_Qcount_p[df_youth$pubertdev_adrenal_Qcount == 0] <- NA

#ANY IDK/NA in these 2 variables for adrenal. Then code to not valid.
df_youth$pubertdev_valid_for_adrenal<-NA
df_youth$pubertdev_valid_for_adrenal<-ifelse(df_youth$pubertdev_adrenal_Qcount==2, 1, 0)

##Count who is valid based on sex 
xtabs(~df_youth$pubertdev_valid_for_adrenal+df_youth$pubertdev_sex)

#Compute adrenal avg
df_youth$pubertdev_adrenalAvg <- df_youth$pubertdevadrenalss/df_youth$pubertdev_adrenal_Qcount
df_youth$pubertdev_adrenalAvg[df_youth$pubertdev_valid_for_adrenal==0] <- NA

##Plot the data
Avg_adrenal=ggplot(df_youth,aes(x=pubertdev_adrenalAvg,group=sex_at_birth,fill=sex_at_birth))+geom_histogram(position="dodge",na.rm = TRUE,alpha=0.5,binwidth=0.25)+theme_bw()

df_youth$pubertdev_gonadAvg_all<-coalesce(df_youth$pubertdev_femalegonadAvg,df_youth$pubertdev_malegonadAvg)

AdrenalAvg=ggplot2.histogram(data=df_youth, xName='pubertdev_adrenalAvg' ,binwidth=0.5,
    groupName='sex_at_birth', legendPosition="top",
        alpha=0.3, position="identity")+theme_bw()+theme(axis.text.x  = element_text(size=12), axis.text.y  = element_text(size=12))+theme( axis.title.x=element_blank(), axis.title.y=element_blank())+facet_grid(~sex_at_birth)

ggsave(AdrenalAvg,  file="AdrenalAvg_Youth.tiff", width = 12, height = 8, units = "in",
  dpi = 300)

GonadalAvg=ggplot2.histogram(data=df_youth, xName='pubertdev_gonadAvg_all' ,binwidth=0.5,
    groupName='sex_at_birth', legendPosition="top",
        alpha=0.3, position="identity")+theme_bw()+theme(axis.text.x  = element_text(size=12), axis.text.y  = element_text(size=12))+theme( axis.title.x=element_blank(), axis.title.y=element_blank())+facet_grid(~sex_at_birth)

ggsave(GonadalAvg,  file="GonadalAvg_Youth.tiff", width = 12, height = 8, units = "in",
  dpi = 300)

ggplot2.histogram(data=df_youth, xName='pubertdev_adrenalAvg',addDensity=TRUE,groupName='sex_at_birth', legendPosition="top",alpha=0.5,addMeanLine=TRUE, meanLineColor="white", meanLineSize=1.5, binwidth=.5)+theme_bw()

ggplot2.histogram(data=df_youth, xName='pubertdev_gonadAvg_all',addDensity=TRUE,groupName='sex_at_birth', legendPosition="top",alpha=0.5,addMeanLine=TRUE, meanLineColor="white", meanLineSize=1.5, binwidth=.5)+theme_bw()

```

```{r}
##Create YOUTH PDS dataset for covariates in other projects
PDSYouthvars <- c("src_subject_id", "sex_at_birth", "eventname", "demo_prim_p", "interview_age", "pubertdev_sex", "pubertdev_Avg_all","pubertdev_ss_category_all", "pubertdev_gonadAvg_all", "pubertdev_adrenalAvg","pubertdev_ht","pubertdev_bdyhair", "pubertdev_skin", "pubertdev_m4", "pubertdev_m5", "pubertdev_f4", "pubertdev_f5", "pubertdev_ht_num","pubertdev_bdyhair_num", "pubertdev_skin_num", "pubertdev_m4_num", "pubertdev_m5_num", "pubertdev_f4_num", "pubertdev_f5_num")
PDSYouth <- df_youth[PDSYouthvars]
saveRDS(PDSYouth, "PDS_youth_clean.rds")
```