---
title: "Research Question 1: Research Question 1: Does pubertal development relate to neural and behavioral responses to reward?"
date: "August 2020"
output:
  html_document: default
  pdf_document: default
authors: Natalie Saragosa-Harris 
---
``` {r loadPackages, echo = FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(gamm4)
library(dplyr)
library(sjPlot)
library(here)
```

```{r LoadData, echo = FALSE}

# Elizabeth.
# Data: Desktop⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code: Desktop⁩ ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code⁩

# Lucia.
# Data:  Github⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Github ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# Natalie.
# Data:  Desktop ▸ ABCD⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Desktop ▸ ABCD ⁩▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# LMW alternative to read in the data.

data_dir = ((dirname(here()))) 

phase_folder = "exploratory"  # select the appropiate folder.
#phase_folder = "confirmatory"  # select the appropiate folder.

data_folder <- file.path(data_dir,"ABCD","derivatives",phase_folder)

file_name <- "nda20_exploratory.csv" # specify file name here. 

fulldata <- read.csv(file.path(data_folder,file_name))
length(fulldata$src_subject_id) # 5934.

# Call function to define all of the dataframes.
script_path <- file.path(data_dir,"rewardprocesses_internalizing_puberty_exploratory","code","define_dataframes.R")
source(script_path)

```

```{r settheme, echo = FALSE}
nsh_theme <- theme(title= element_text(size=26, vjust=2, face="bold"),
         plot.title = element_blank(),
         axis.title.x= element_text(size=18, vjust=-0.3),
         axis.title.y= element_text(size=18, vjust=1.5),
         axis.text.x= element_text(size=18, colour="black"),
         axis.text.y= element_text(size=18, colour="black"),
         strip.text = element_text(size=24, face="bold"),
         panel.background = element_blank(),
         axis.line = element_line(colour = "black"))

```

# Confirmatory Hypothesis 1: We hypothesize that pubertal stage will be associated with neural response to reward during a monetary incentive delay task (Braams et al., 2015). In particular, we expect heightened striatal activation during reward anticipation for more advanced pubertal stages.
## Model: Striatal activation (anticipation stage) ~ Pubertal stage

#### Female.
```{r Confirmatory1Female, echo = FALSE}
dataformodel <- data_no_striatal_ant_outliers_females

confirmatory1_females <- gamm4(striatum_rvsn_ant_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(confirmatory1_females$gam)

# None of these plots are working?
#plot.gam(confirmatory1_females$gam,residuals=TRUE,all.terms=TRUE)
#plot_model(confirmatory1_females$mer,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_females$mer,type = "est", show.data = FALSE) # forest plot.
```

#### Male.
```{r Confirmatory1Male, echo = FALSE}
dataformodel <- data_no_striatal_ant_outliers_males

confirmatory1_males<- gamm4(striatum_rvsn_ant_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(confirmatory1_males$gam)

#plot_model(confirmatory1_males,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_males,type = "est", show.data = FALSE) # forest plot.
```

# Exploratory Hypothesis 1A: We will explore whether striatal activation during reward feedback is related to pubertal stage.
## Model: Striatal activation (feedback stage) ~ Pubertal stage
## Females.
```{r Exploratory1AFemales, echo = FALSE}
dataformodel <- data_no_striatal_feed_outliers_females

exploratory1A_females <- gamm4(striatum_posvsneg_feedback_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(exploratory1A_females$gam)

```

## Males.
```{r Exploratory1AMales, echo = FALSE}
dataformodel <- data_no_striatal_feed_outliers_males

exploratory1A_males <- gamm4(striatum_posvsneg_feedback_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(exploratory1A_males$gam)

```
# Exploratory Hypothesis 1B: We hypothesize that more advanced pubertal stages will be associated with greater self-reported reward responsiveness (BAS - RR) (Harden et al. 2018).
## Model: BIS-BAS-RR ~ Pubertal stage
# Females.
```{r Exploratory1BFemales, echo = FALSE}
dataformodel <- data_no_bisbas_outliers_females
bisbas_ss_basm_rr_z
```
# Males.
```{r Exploratory1BMales, echo = FALSE}
dataformodel <- data_no_bisbas_outliers_males
bisbas_ss_basm_rr_z
```
# Exploratory Hypothesis 1C: We hypothesize that greater pubertal stage will be associated with greater behavioral reactivity to reward (i.e., reaction time on reward vs. neutral trials).
## Model: Reaction Time ~ Pubertal Stage
```{r Exploratory1C, echo = FALSE}

```
# Exploratory Hypothesis 1D: We hypothesize that testosterone will be positively associated with our indicators of reward (neural activity, behavioral reaction time, and self-reported reward responsiveness).
## Model A: Striatal activation (anticipation stage) ~ Testosterone
## Model B: Striatal activation (feedback stage) ~ Testosterone
## Model C: OFC activation (anticipation stage) ~ Testosterone
## Model D: OFC activation (feedback stage) ~ Testosterone
## Model E: MID Reaction Time ~ Testosterone
## Model F: BIS-BAS-RR ~ Testosterone
```{r Exploratory1D, echo = FALSE}

```