---
title: "Research Question 3: Do neural, behavioral, and self-reported responsivity to reward relate to internalizing symptoms?"
author: "Natalie Saragosa-Harris"
date: "July 2021"
output:
  html_document:
    toc: true
  pdf_document:
    toc: true
---
---
``` {r loadPackages, echo = FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(gamm4)
library(dplyr)
library(sjPlot)
library(here)
```

```{r LoadData, echo = FALSE}

# Elizabeth.
# Data: Desktop⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code: Desktop⁩ ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code⁩

# Lucia.
# Data:  Github⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Github ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# Natalie.
# Data:  Desktop ▸ ABCD⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Desktop ▸ ABCD ⁩▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# LMW alternative to read in the data.

data_dir = ((dirname(here()))) 

phase_folder = "confirmatory"  # select the appropriate folder.

data_folder <- file.path(data_dir,"ABCD","derivatives",phase_folder)

file_name <- "nda30_confirmatory.csv" # specify file name here. 

fulldata <- read.csv(file.path(data_folder,file_name))
#nrow(fulldata) # 27331 (confirmatory).

# Call function to define all of the dataframes.
script_path <- file.path(data_dir,"rewardprocesses_internalizing_puberty_exploratory","code","define_dataframes.R")
source(script_path)

```

```{r settheme, echo = FALSE}
nsh_theme <- theme(title= element_text(size=26, vjust=2, face="bold"),
         plot.title = element_blank(),
         axis.title.x= element_text(size=18, vjust=-0.3),
         axis.title.y= element_text(size=18, vjust=1.5),
         axis.text.x= element_text(size=18, colour="black"),
         axis.text.y= element_text(size=18, colour="black"),
         strip.text = element_text(size=24, face="bold"),
         panel.background = element_blank(),
         axis.line = element_line(colour = "black"))

```

# Confirmatory Hypothesis 3: We hypothesize that striatal and orbitofrontal cortex activity during the reward anticipation and feedback stages of the MID task will be negatively associated with internalizing symptoms (Forbes et al., 2010; Ubl et al., 2015; Luking et al., 2016).

## Model A: CBCL internalizing factor ~ Striatal activity (anticipation stage - All reward v. neutral)
### Females.
```{r Confirmatory3AFemale, echo = FALSE}
#dataformodel <- data_no_CBCL_striatal_ant_outliers_females # Not excluding CBCL outliers.
dataformodel <- data_no_striatal_ant_outliers_females 

confirmatory3A_females <- gamm4(cbcl_scr_syn_internal_r ~ striatum_rvsn_ant_z +
                                interview_age +
                                race.ethnicity.5level +
                                #high.educ +
                                #household.income +
                                #married.or.livingtogether +
                                demo_race_hispanic, 
                                random = ~ (1 | site_id_l/rel_family_id),
                                data = dataformodel)

summary(confirmatory3A_females$gam)


```
### Males.
```{r Confirmatory3AMale, echo = FALSE}
dataformodel <- data_no_striatal_ant_outliers_males
confirmatory3A_males <- gamm4(cbcl_scr_syn_internal_r ~ striatum_rvsn_ant_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(confirmatory3A_males$gam)

```

## Model A: CBCL internalizing factor ~ Nucleus Accumbens activity (anticipation stage - All reward v. neutral)
### Females.
```{r Confirmatory3AFemaleAccumbens, echo = FALSE}

dataformodel <- data_no_accumbens_ant_outliers_females

confirmatory3A_nacc_females <- gamm4(cbcl_scr_syn_internal_r ~ accumbens_rvsn_ant_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3A_nacc_females$gam)


```
### Males.
```{r Confirmatory3AMaleAccumbens, echo = FALSE}
dataformodel <- data_no_accumbens_ant_outliers_males

confirmatory3A_nacc_males <- gamm4(cbcl_scr_syn_internal_r ~ accumbens_rvsn_ant_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(confirmatory3A_nacc_males$gam)

```

## Model A: CBCL internalizing factor ~ Caudate activity (anticipation stage - All reward v. neutral)
### Females.
```{r Confirmatory3AFemaleCaudate, echo = FALSE}
dataformodel <- data_no_caudate_ant_outliers_females

confirmatory3A_caud_females <- gamm4(cbcl_scr_syn_internal_r ~ caudate_rvsn_ant_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(confirmatory3A_caud_females$gam)


```
### Males.
```{r Confirmatory3AMaleCaudate, echo = FALSE}
dataformodel <- data_no_caudate_ant_outliers_males

confirmatory3A_caud_males <- gamm4(cbcl_scr_syn_internal_r ~ caudate_rvsn_ant_z +
                               interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(confirmatory3A_caud_males$gam)


```

## Model A: CBCL internalizing factor ~ Putamen activity (anticipation stage - All reward v. neutral)
### Females.
```{r Confirmatory3AFemalePutamen, echo = FALSE}
dataformodel <- data_no_putamen_ant_outliers_females

confirmatory3A_putamen_females <- gamm4(cbcl_scr_syn_internal_r ~ putamen_rvsn_ant_z +
                               interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(confirmatory3A_putamen_females$gam)


```
### Males.
```{r Confirmatory3AMalePutamen, echo = FALSE}
dataformodel <- data_no_putamen_ant_outliers_males

confirmatory3A_putamen_males <- gamm4(cbcl_scr_syn_internal_r ~ putamen_rvsn_ant_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3A_putamen_males$gam)

```

## Model B: CBCL internalizing factor ~ Average striatal activity (feedback stage)
### Females.
```{r Confirmatory3BFemale, echo = FALSE}
dataformodel <- data_no_striatal_feed_outliers_females

confirmatory3B_females <- gamm4(cbcl_scr_syn_internal_r ~ striatum_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3B_females$gam)
```
### Males.
```{r Confirmatory3BMale, echo = FALSE}
dataformodel <- data_no_striatal_feed_outliers_males

confirmatory3B_males <- gamm4(cbcl_scr_syn_internal_r ~ striatum_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3B_males$gam)
```
## Model B: CBCL internalizing factor ~ Accumbens activity (feedback stage)
### Females.
```{r Confirmatory3BFemaleAccumbens, echo = FALSE}
dataformodel <- data_no_accumbens_feed_outliers_females

confirmatory3B_accumbens_females <- gamm4(cbcl_scr_syn_internal_r ~ accumbens_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3B_accumbens_females$gam)

```
### Males.
```{r Confirmatory3BMaleAccumbens, echo = FALSE}
dataformodel <- data_no_accumbens_feed_outliers_males

confirmatory3B_accumbens_males <- gamm4(cbcl_scr_syn_internal_r ~ accumbens_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(confirmatory3B_accumbens_males$gam)
```

## Model B: CBCL internalizing factor ~ Caudate activity (feedback stage)
### Females.
```{r Confirmatory3BFemaleCaudate, echo = FALSE}
dataformodel <- data_no_caudate_feed_outliers_females

confirmatory3B_caudate_females <- gamm4(cbcl_scr_syn_internal_r ~ caudate_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(confirmatory3B_caudate_females$gam)

```
### Males.
```{r Confirmatory3BMaleCaudate, echo = FALSE}
dataformodel <- data_no_caudate_feed_outliers_males

confirmatory3B_caudate_males <- gamm4(cbcl_scr_syn_internal_r ~ caudate_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(confirmatory3B_caudate_males$gam)
```

## Model B: CBCL internalizing factor ~ Putamen activity (feedback stage)
### Females.
```{r Confirmatory3BFemalePutamen, echo = FALSE}
dataformodel <- data_no_putamen_feed_outliers_females

confirmatory3B_putamen_females <- gamm4(cbcl_scr_syn_internal_r ~ putamen_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3B_putamen_females$gam)

```
### Males.
```{r Confirmatory3BMalePutamen, echo = FALSE}
dataformodel <- data_no_putamen_feed_outliers_males

confirmatory3B_putamen_males <- gamm4(cbcl_scr_syn_internal_r ~ putamen_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(confirmatory3B_putamen_males$gam)
```

## Model C: CBCL internalizing factor ~ Orbitofrontal cortex activity (anticipation stage)
### Females.
```{r Confirmatory3CFemale, echo = FALSE}
# Lateral OFC.
dataformodel <- data_no_lOFC_ant_outliers_females
confirmatory3C_lOFC_females <- gamm4(cbcl_scr_syn_internal_r ~ lOFC_rvsn_ant_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3C_lOFC_females$gam)

# Medial OFC.
dataformodel <- data_no_mOFC_ant_outliers_females
confirmatory3C_mOFC_females <- gamm4(cbcl_scr_syn_internal_r ~ mOFC_rvsn_ant_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3C_mOFC_females$gam)
```
### Males.
```{r Confirmatory3CMale, echo = FALSE}
# Lateral OFC.
dataformodel <- data_no_lOFC_ant_outliers_males
confirmatory3C_lOFC_males <- gamm4(cbcl_scr_syn_internal_r ~ lOFC_rvsn_ant_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(confirmatory3C_lOFC_males$gam)

# Medial OFC.
dataformodel <- data_no_mOFC_ant_outliers_males
confirmatory3C_mOFC_males <- gamm4(cbcl_scr_syn_internal_r ~ mOFC_rvsn_ant_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3C_mOFC_males$gam)
```

## Model D: CBCL internalizing factor ~ Orbitofrontal cortex activity (feedback stage)
### Females.
```{r Confirmatory3DFemale, echo = FALSE}
# Lateral OFC.
dataformodel <- data_no_lOFC_feed_outliers_females

confirmatory3D_lOFC_females <- gamm4(cbcl_scr_syn_internal_r ~ lOFC_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(confirmatory3D_lOFC_females$gam)

# Medial OFC.
dataformodel <- data_no_mOFC_feed_outliers_females
confirmatory3D_mOFC_females <- gamm4(cbcl_scr_syn_internal_r ~ mOFC_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3D_mOFC_females$gam)

```
### Males.
```{r Confirmatory3DMale, echo = FALSE}
# Lateral OFC.
dataformodel <- data_no_lOFC_feed_outliers_males

confirmatory3D_lOFC_males <- gamm4(cbcl_scr_syn_internal_r ~ lOFC_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3D_lOFC_males$gam)


# Medial OFC.
dataformodel <- data_no_mOFC_feed_outliers_males
confirmatory3D_mOFC_males <- gamm4(cbcl_scr_syn_internal_r ~ mOFC_posvsneg_feedback_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(confirmatory3D_mOFC_males$gam)
```

# Exploratory Hypothesis 3A: We hypothesize that self-reported reward responsiveness (BAS - RR) will be negatively associated with internalizing symptoms.
## Model: CBCL internalizing factor ~ BIS-BAS-RR
### Females.
```{r Exploratory3AFemale, echo = FALSE}
dataformodel <- data_no_bisbas_outliers_females

exploratory3A_females <- gamm4(cbcl_scr_syn_internal_r ~ bisbas_ss_basm_rr +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(exploratory3A_females$gam)

```
### Males.
```{r Exploratory3AMale, echo = FALSE}
dataformodel <- data_no_bisbas_outliers_males

exploratory3A_males <- gamm4(cbcl_scr_syn_internal_r ~ bisbas_ss_basm_rr +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(exploratory3A_males$gam)

```

# Exploratory Hypothesis 3B: We hypothesize that behavioral reward responsiveness (i.e., MID Reaction Time reward vs. neutral trials) will be associated with internalizing symptoms, such that individuals with higher internalizing symptoms will have slower reaction times in response to reward.
# Model: CBCL internalizing factor ~ MID Reaction Time (reward vs. neutral trials)
### Females.
```{r Exploratory3BFemale, echo = FALSE}

# Large reward vs. neutral trial reaction time.
dataformodel <- data_no_RT_MID_outliers_females

exploratory3B_females_largereward_neutral <- gamm4(cbcl_scr_syn_internal_r ~ rt_diff_large_neutral_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(exploratory3B_females_largereward_neutral$gam)

# Large reward vs. small reward trial reaction time.
dataformodel <- data_no_RT_MID_outliers_females

exploratory3B_females_largesmallreward <- gamm4(cbcl_scr_syn_internal_r ~ rt_diff_large_small_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)
summary(exploratory3B_females_largesmallreward$gam)

```
### Males.
```{r Exploratory3BMale, echo = FALSE}

# Large reward vs. neutral trial reaction time.
dataformodel <- data_no_RT_MID_outliers_males

exploratory3B_males_largereward_neutral <- gamm4(cbcl_scr_syn_internal_r ~ rt_diff_large_neutral_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(exploratory3B_males_largereward_neutral$gam)

# Large reward vs. small reward trial reaction time.
dataformodel <- data_no_RT_MID_outliers_males

exploratory3B_males_largesmallreward <- gamm4(cbcl_scr_syn_internal_r ~ rt_diff_large_small_z +
                              interview_age +
                              race.ethnicity.5level +
                              demo_race_hispanic, 
                              random = ~ (1 | site_id_l/rel_family_id),
                              data = dataformodel)

summary(exploratory3B_males_largesmallreward$gam)
```

# Exploratory Hypothesis 3C: For any models within Hypothesis 3 that are significant using the CBCL internalizing scale, we will then investigate whether a more specific CBCL subscale (i.e., anxious/depressive, withdrawn/depressive, or the DSM-based affective scale) is a better fit to our models. 

