---
title: "Research Question 1: Does pubertal development relate to neural and behavioral responses to reward?"
date: "July 2021"
output:
  html_document: default
  pdf_document: default
authors: Natalie Saragosa-Harris 
---
``` {r loadPackages, echo = FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(gamm4)
library(dplyr)
library(sjPlot)
library(here)
```

```{r LoadData, echo = FALSE}

# Elizabeth.
# Data: Desktop⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code: Desktop⁩ ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code⁩

# Lucia.
# Data:  Github⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Github ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# Natalie.
# Data:  Desktop ▸ ABCD⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Desktop ▸ ABCD ⁩▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# LMW alternative to read in the data.

data_dir = ((dirname(here()))) 

phase_folder = "exploratory"  # select the appropriate folder.
#phase_folder = "confirmatory"  # select the appropriate folder.

data_folder <- file.path(data_dir,"ABCD","derivatives",phase_folder)

file_name <- "nda30_exploratory.csv" # specify file name here. 

fulldata <- read.csv(file.path(data_folder,file_name))
nrow(fulldata) # 27321 (exploratory). When call the define_dataframes script, will keep only the baseline data.

# Call function to define all of the dataframes.
script_path <- file.path(data_dir,"rewardprocesses_internalizing_puberty_exploratory","code","define_dataframes.R")
source(script_path)
```

# Demographics
```{r}
min(PDS_correct$interview_age)
max(PDS_correct$interview_age)
mean(PDS_correct$interview_age)
nrow(PDS_correct) # 5631 (exploratory).
female_subset <- subset(PDS_correct, sex=="F")
male_subset <- subset(PDS_correct, sex=="M")

nrow(female_subset)
nrow(male_subset)
#Full data females N=2840
#PDS_correct females N=2701

#Full data males N=3094
#PDS_correct males N=2930
library(psych)
describe(female_subset$interview_age)
describe(male_subset$interview_age)

#Female Race & Ethnicity
female_racethnicity_table <- table(female_subset$race.ethnicity.5level)
library(stats)
addmargins(female_racethnicity_table)
sum(is.na(female_subset$race.ethnicity.5level))

#Hispanic or Latina/o/x = 1
female_ethnicity_table <- table(female_subset$demo_race_hispanic)
addmargins(female_ethnicity_table)

#Male Race & Ethnicity
male_racethnicity_table <- table(male_subset$race.ethnicity.5level)
library(stats)
addmargins(male_racethnicity_table)
sum(is.na(male_subset$race.ethnicity.5level))

#Hispanic or Latina/o/x = 1
male_ethnicity_table <- table(male_subset$demo_race_hispanic)
addmargins(male_ethnicity_table)

#PDS Score
describe(female_subset$PDS_score)
describe(male_subset$PDS_score)

#PDS Stage Category
female_pds_category_table <- table(female_subset$pds_p_ss_category)
addmargins(female_pds_category_table)
prop.table(female_pds_category_table)

male_pds_category_table <- table(male_subset$pds_p_ss_category)
addmargins(male_pds_category_table)
prop.table(male_pds_category_table)


#CBCL Internalizing Raw Score
describe(female_subset$cbcl_scr_syn_internal_r)
describe(male_subset$cbcl_scr_syn_internal_r)


#BIS/BAS
describe(data_no_bisbas_outliers_females$bisbas_ss_basm_rr)
describe(data_no_bisbas_outliers_males$bisbas_ss_basm_rr)

# List of covariates that are no longer included in these models.
# Note: only include race and ethnicity as covariates when PDS is a predictor *and* CBCL is the outcome in the model.
#race.ethnicity.5level
#demo_race_hispanic
#high.educ
#household.income
#married.or.livingtogether

```

```{r settheme, echo = FALSE}
nsh_theme <- theme(title= element_text(size=26, vjust=2, face="bold"),
         plot.title = element_blank(),
         axis.title.x= element_text(size=18, vjust=-0.3),
         axis.title.y= element_text(size=18, vjust=1.5),
         axis.text.x= element_text(size=18, colour="black"),
         axis.text.y= element_text(size=18, colour="black"),
         strip.text = element_text(size=24, face="bold"),
         panel.background = element_blank(),
         axis.line = element_line(colour = "black"))

```

# Confirmatory Hypothesis 1: We hypothesize that pubertal stage will be associated with neural response to reward during a monetary incentive delay task (Braams et al., 2015). In particular, we expect heightened striatal activation during reward anticipation for more advanced pubertal stages.
## Model: Striatal activation (anticipation stage) ~ Pubertal stage

#### Females.
```{r Confirmatory1Female_Striatum, echo = FALSE}
dataformodel <- data_no_striatal_ant_outliers_females

# Note: only include race and ethnicity as covariates when PDS is a predictor *and* CBCL is the outcome in the model.
confirmatory1_females <- gamm4(striatum_rvsn_ant_z ~ PDS_score + interview_age,
                               #race.ethnicity.5level +
                               #demo_race_hispanic,
                               #high.educ +
                               #household.income +
                               #married.or.livingtogether
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(confirmatory1_females$gam)

#plot.gam(confirmatory1_females$gam,residuals=TRUE,all.terms=TRUE)
#plot_model(confirmatory1_females$mer,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_females$mer,type = "est", show.data = FALSE) # forest plot.
```

#### Males.
```{r Confirmatory1Male_Striatum, echo = FALSE}
dataformodel <- data_no_striatal_ant_outliers_males

confirmatory1_males<- gamm4(striatum_rvsn_ant_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)
summary(confirmatory1_males$gam)
library(stargazer)
stargazer(confirmatory1_males$mer)
#plot_model(confirmatory1_males,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_males,type = "est", show.data = FALSE) # forest plot.
```

# Exploratory Hypothesis 1A: We will explore whether striatal activation during reward feedback is related to pubertal stage.
## Model: Striatal activation (feedback stage) ~ Pubertal stage
### Females.
```{r Exploratory1AFemales, echo = FALSE}
dataformodel <- data_no_striatal_feed_outliers_females

exploratory1A_females <- gamm4(striatum_posvsneg_feedback_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1A_females$gam)

```

### Males.
```{r Exploratory1AMales, echo = FALSE}
dataformodel <- data_no_striatal_feed_outliers_males

exploratory1A_males <- gamm4(striatum_posvsneg_feedback_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1A_males$gam)

```
# Exploratory Hypothesis 1B: We hypothesize that more advanced pubertal stages will be associated with greater self-reported reward responsiveness (BAS - RR) (Harden et al. 2018).
## Model: BIS-BAS-RR ~ Pubertal stage
### Females.
```{r Exploratory1BFemales, echo = FALSE}
dataformodel <- data_no_bisbas_outliers_females

exploratory1B_females <- gamm4(bisbas_ss_basm_rr_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1B_females$gam)

```
### Males.
```{r Exploratory1BMales, echo = FALSE}
dataformodel <- data_no_bisbas_outliers_males

exploratory1B_males <- gamm4(bisbas_ss_basm_rr_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1B_males$gam)

```
# Exploratory Hypothesis 1C: We hypothesize that greater pubertal stage will be associated with greater behavioral reactivity to reward (i.e., reaction time on reward vs. neutral trials).
## Model: Reaction Time ~ Pubertal Stage

### Females.
```{r Exploratory1CFemales, echo = FALSE}
dataformodel <- data_no_RT_MID_outliers_females

# Large reward vs. neutral positive.
exploratory1C_lg_neutral_RT_females <- gamm4(rt_diff_large_neutral_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1C_lg_neutral_RT_females$gam)


# Large reward vs. small positive.
exploratory1C_lg_small_RT_females <- gamm4(rt_diff_large_small_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1C_lg_small_RT_females$gam)
```

### Males.
```{r Exploratory1CMales, echo = FALSE}
dataformodel <- data_no_RT_MID_outliers_males

# Large reward vs. neutral positive.
exploratory1C_lg_neutral_RT_males <- gamm4(rt_diff_large_neutral_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1C_lg_neutral_RT_males$gam)


# Large reward vs. small positive.
exploratory1C_lg_small_RT_males <- gamm4(rt_diff_large_small_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1C_lg_small_RT_males$gam)
```
# Exploratory Hypothesis 1D: We hypothesize that testosterone will be positively associated with our indicators of reward (neural activity, behavioral reaction time, and self-reported reward responsiveness).
## Model A: Striatal activation (anticipation stage) ~ Testosterone
### Females.
```{r Exploratory1D_A, echo = FALSE}
## Model A: Striatal activation (anticipation stage) ~ Testosterone
# Females.
dataformodel <- data_no_striatal_ant_test_outliers_females # No striatal anticipation or testosterone outliers.
modelA_females <- gamm4(striatum_rvsn_ant_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelA_females$gam)
```

### Males.
```{r}
# Males.
dataformodel <- data_no_striatal_ant_test_outliers_males # No striatal anticipation or testosterone outliers.
modelA_males <- gamm4(striatum_rvsn_ant_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelA_males$gam)
```

## Model B: Striatal activation (feedback stage) ~ Testosterone
### Females.
```{r Exploratory1D_B, echo = FALSE}
## Model B: Striatal activation (feedback stage) ~ Testosterone
# Females.
dataformodel <- data_no_striatal_feed_test_outliers_females # No striatal feedback or testosterone outliers.
modelB_females <- gamm4(striatum_posvsneg_feedback_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelB_females$gam)
```

### Males.
```{r}
# Males.
dataformodel <- data_no_striatal_feed_test_outliers_males # No striatal feedback or testosterone outliers.
modelB_males <- gamm4(striatum_posvsneg_feedback_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelB_males$gam)
```

## Model C: OFC activation (anticipation stage) ~ Testosterone
### Females.
```{r Exploratory1D_C, echo = FALSE}
## Model C: OFC activation (anticipation stage) ~ Testosterone

# Females (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_ant_test_outliers_females
modelC_females_lOFC <- gamm4(lOFC_rvsn_ant_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelC_females_lOFC$gam)


# Females (medial OFC; mOFC).
dataformodel <- data_no_mOFC_ant_test_outliers_females
modelC_females_mOFC <- gamm4(mOFC_rvsn_ant_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelC_females_mOFC$gam)

```

### Males.
```{r}
# Males (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_ant_test_outliers_males
modelC_males_lOFC <- gamm4(lOFC_rvsn_ant_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelC_males_lOFC$gam)


# Males (medial OFC; mOFC).
dataformodel <- data_no_mOFC_ant_test_outliers_males
modelC_males_mOFC <- gamm4(mOFC_rvsn_ant_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelC_males_mOFC$gam)
```

## Model D: OFC activation (feedback stage) ~ Testosterone
### Females.
```{r Exploratory1D_D, echo = FALSE}
## Model D: OFC activation (feedback stage) ~ Testosterone

# Females (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_feed_test_outliers_females
modelD_females_lOFC <- gamm4(lOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelD_females_lOFC$gam)


# Females (medial OFC; mOFC).
dataformodel <- data_no_mOFC_feed_test_outliers_females
modelD_females_mOFC <- gamm4(mOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelD_females_mOFC$gam)
```

### Males.
```{r}

# Males (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_feed_test_outliers_males
modelD_males_lOFC <- gamm4(lOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelD_males_lOFC$gam)


# Males (medial OFC; mOFC).
dataformodel <- data_no_mOFC_feed_test_outliers_males
modelD_males_mOFC <- gamm4(mOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelD_males_mOFC$gam)
```

## Model E: MID Reaction Time ~ Testosterone
### Females.
```{r Exploratory1D, echo = FALSE}
## Model E: MID Reaction Time ~ Testosterone
# Females: large reward vs. neutral.
dataformodel <- data_no_RT_test_outliers_females # No MID RT difference score or testosterone outliers.
modelE_lg_neutral_RT_females <- gamm4(rt_diff_large_neutral_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelE_lg_neutral_RT_females$gam)

# Females: large reward vs. small reward.
dataformodel <- data_no_RT_test_outliers_females # No MID RT difference score or testosterone outliers.
modelE_lg_small_RT_females <- gamm4(rt_diff_large_small_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelE_lg_small_RT_females$gam)
```

### Males.
```{r}
# Males: large reward vs. neutral.
dataformodel <- data_no_RT_test_outliers_males # No MID RT difference score or testosterone outliers.

modelE_lg_neutral_RT_males <- gamm4(rt_diff_large_neutral_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelE_lg_neutral_RT_males$gam)

# Males: large reward vs. small reward.
modelE_lg_small_RT_males <- gamm4(rt_diff_large_small_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelE_lg_small_RT_males$gam)
```

## Model F: BIS-BAS-RR ~ Testosterone
### Females.
```{r Exploratory1D_F, echo = FALSE}
## Model F: BIS-BAS-RR ~ Testosterone
#Females
dataformodel <- data_no_bisbas_test_outliers_females
modelF_females <- gamm4(bisbas_ss_basm_rr_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelF_females$gam)
```
### Males.
```{r}
dataformodel <- data_no_bisbas_test_outliers_males
modelF_males <- gamm4(bisbas_ss_basm_rr_z ~ hormone_scr_ert_mean_z + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(modelF_males$gam)
```

# Confirmatory Hypothesis 1 SEPARATE STRIATAL REGIONS (anticipation stage) 
## Model A: Caudate Anticipation ~ Pubertal stage
### Females.
```{r Confirmatory1Female_Caudate, echo = FALSE}
dataformodel <- data_no_caudate_ant_outliers_females 

confirmatory1_caudate_females <- gamm4(caudate_rvsn_ant_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(confirmatory1_caudate_females$gam)

# None of these plots are working?
#plot.gam(confirmatory1_females$gam,residuals=TRUE,all.terms=TRUE)
#plot_model(confirmatory1_females$mer,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_females$mer,type = "est", show.data = FALSE) # forest plot.
```

### Males.
```{r Confirmatory1Male, echo = FALSE}
dataformodel <- data_no_striatal_ant_outliers_males

confirmatory1_caudate_males<- gamm4(caudate_rvsn_ant_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(confirmatory1_caudate_males$gam)

#plot_model(confirmatory1_males,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_males,type = "est", show.data = FALSE) # forest plot.
```

## Model B: Putamen Anticipation ~ Pubertal stage
### Females.
```{r Confirmatory1Female_Putamen, echo = FALSE}
dataformodel <- data_no_putamen_ant_outliers_females 

confirmatory1_putamen_females <- gamm4(putamen_rvsn_ant_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(confirmatory1_putamen_females$gam)

# None of these plots are working?
#plot.gam(confirmatory1_females$gam,residuals=TRUE,all.terms=TRUE)
#plot_model(confirmatory1_females$mer,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_females$mer,type = "est", show.data = FALSE) # forest plot.
```

### Males.
```{r Confirmatory1Male_Putamen, echo = FALSE}
dataformodel <- data_no_putamen_ant_outliers_males 

confirmatory1_putamen_males <- gamm4(putamen_rvsn_ant_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(confirmatory1_putamen_males$gam)
```

## Model C: Accumbens Anticipation ~ Pubertal stage
### Females.
```{r Confirmatory1Female_Accumbens, echo = FALSE}
dataformodel <- data_no_accumbens_ant_outliers_females 

confirmatory1_accumbens_females <- gamm4(accumbens_rvsn_ant_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(confirmatory1_accumbens_females$gam)

```

### Males.
```{r Confirmatory1Male_Accumbens, echo = FALSE}
dataformodel <- data_no_accumbens_ant_outliers_males 

confirmatory1_accumbens_males <- gamm4(accumbens_rvsn_ant_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(confirmatory1_accumbens_males$gam)

```

# Exploratory Hypothesis 1A: SEPARATE STRIATAL REGIONS (feedback stage)
## Model A: Caudate Feedback  ~ Pubertal stage
### Females.
```{r Exploratory1A_Caudate_Females, echo = FALSE}
dataformodel <- data_no_caudate_feed_outliers_females

exploratory1A_caudate_females <- gamm4(caudate_posvsneg_feedback_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1A_caudate_females$gam)

```

### Males.
```{r Exploratory1A_Caudate_Males, echo = FALSE}
dataformodel <- data_no_caudate_feed_outliers_males

exploratory1A_caudate_males <- gamm4(caudate_posvsneg_feedback_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1A_caudate_males$gam)

```
## Model B: Putamen Feedback ~ Pubertal stage
### Females.
```{r Exploratory1A_Putamen_Females, echo = FALSE}
dataformodel <- data_no_putamen_feed_outliers_females

exploratory1A_putamen_females <- gamm4(putamen_posvsneg_feedback_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1A_putamen_females$gam)

```

### Males.
```{r Exploratory1A_Putamen_males, echo = FALSE}
dataformodel <- data_no_putamen_feed_outliers_males

exploratory1A_putamen_males <- gamm4(putamen_posvsneg_feedback_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1A_putamen_males$gam)

```
## Model C: Accumbens Feedback ~ Pubertal stage
### Females.
```{r Exploratory1A_Accumbens_Females, echo = FALSE}
dataformodel <- data_no_accumbens_feed_outliers_females

exploratory1A_accumbens_females <- gamm4(accumbens_posvsneg_feedback_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1A_accumbens_females$gam)

```

### Males.
```{r Exploratory1A_Accumbens_Males, echo = FALSE}
dataformodel <- data_no_accumbens_feed_outliers_males

exploratory1A_accumbens_males <- gamm4(accumbens_posvsneg_feedback_z ~ PDS_score + interview_age,
                               random = ~ (1 | site_id_l/rel_family_id),
                               data = dataformodel)

summary(exploratory1A_accumbens_males$gam)

```
