---
title: "Research Question 1: Research Question 1: Does pubertal development relate to neural and behavioral responses to reward?"
date: "August 2020"
output:
  html_document: default
  pdf_document: default
authors: Natalie Saragosa-Harris 
---
``` {r loadPackages, echo = FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(gamm4)
library(dplyr)
library(sjPlot)
```

```{r setdirectories, echo = FALSE}
# Change this to your directory and the name of your data file.
datapath <- "/Users/nataliesaragosa-harris/Desktop/ABCD/output"
datafile <- "nda20_exploratory.csv"
setwd(datapath)

# Covariates.
#      Random effects.
#           1. Family. (rel_family_id) # Make sure this is nested correctly and looks about right.
#           2. Site. (site_id_l)
#           3. Subject. (src_subject_id) # There is only one timepoint so we cannot do a random effect for each participant.
#           4. Device. # mri_info_deviceserialnumber.

          #  Random effects are nested: (1|abcd_site/device/rel_family_id) [unless some siblings went in different scanners?]

#      Fixed effects.
#           1. Race parent. (race.eth.7level).
#           2. Education parent. (high.educ).
#           3. Income parent. (household.income)
#           4. Marital status parent. (married.or.livingtogether)
#           5. Age. (interview_age).
#           6. Hispanic. (demo_race_hispanic).
#           7. Maternal Depression (Yes/No). (fam_history_q6d_depression). This is specific to the mother; do we want
#              to use the one about the family history in general?

```

```{r GetData, echo = FALSE}
fulldata <- read.table(datafile, header=T, sep=",",as.is=TRUE,strip.white=TRUE,fill=TRUE)
length(fulldata$src_subject_id) # 5934.
# Because this is such a big data file, let's only keep the columns that we need for this analysis.
data <- fulldata[,c("src_subject_id",
                "interview_age",
                "eventname",
                "sex",
                "site_id_l",
                "mri_info_deviceserialnumber",
                "rel_family_id",
                "race.ethnicity.5level",
                "race.eth.7level",
                "demo_race_hispanic", # Do you consider the child Hispanic/Latino/Latina?
                "high.educ",
                "household.income",
                "married.or.livingtogether",
                "cbcl_scr_syn_internal_t",
                "cbcl_scr_syn_anxdep_t",
                "cbcl_scr_syn_withdep_t",
                "cbcl_scr_dsm5_depress_t",
                "PDS_score_f",
                "PDS_score_m",
                "PDS_score",
                "PDS_sum_f",
                "PDS_sum_m",
                "PDS_sum",
                "fam_history_q6d_depression",
                "tfmri_ma_acdn_b_scs_aarh", # Accumbens reward vs. neutral anticipation.
                "tfmri_ma_acdn_b_scs_aalh",
                "tfmri_ma_acdn_b_scs_cdrh", # Caudate reward vs. neutral anticipation.
                "tfmri_ma_acdn_b_scs_cdlh",
                "tfmri_ma_acdn_b_scs_ptrh", # Putamen reward vs. neutral anticipation.
                "tfmri_ma_acdn_b_scs_ptlh",
                "tfmri_ma_arvn_b_cds_mobofrrh", # Medial OFC reward vs. neutral anticipation.
                "tfmri_ma_arvn_b_cds_mobofrlh",
                "tfmri_ma_arvn_b_cds_lobofrrh", # Lateral OFC reward vs. neutral anticipation.
                "tfmri_ma_arvn_b_cds_lobofrlh",
                "tfmri_ma_rpvnfb_b_scs_aarh", # Accumbens reward positive versus negative feedback.
                "tfmri_ma_rpvnfb_b_scs_aalh",
                "tfmri_ma_rpvnfb_b_scs_cdrh", # Caudate reward positive versus negative feedback.
                "tfmri_ma_rpvnfb_b_scs_cdlh",
                "tfmri_ma_rpvnfb_b_scs_ptrh", # Putamen reward positive versus negative feedback.
                "tfmri_ma_rpvnfb_b_scs_ptlh",
                "tfmri_ma_rpvnfb_b_cds_mobofrrh", # Medial OFC reward positive versus negative feedback.
                "tfmri_ma_rpvnfb_b_cds_mobofrlh",
                "tfmri_ma_rpvnfb_b_cds_lobofrrh", # Lateral OFC reward positive versus negative feedback.
                "tfmri_ma_rpvnfb_b_cds_lobofrlh",
                "accumbens_rvsn_ant", # Reward vs. neutral during anticipation stage.
                "caudate_rvsn_ant",
                "putamen_rvsn_ant",
                "mOFC_rvsn_ant",
                "lOFC_rvsn_ant",
                "accumbens_posvsneg_feedback", # All positive vs. negative feedback.
                "caudate_posvsneg_feedback",
                "putamen_posvsneg_feedback",
                "mOFC_posvsneg_feedback",
                "lOFC_posvsneg_feedback",
                "striatum_rvsn_ant", # reward vs. neutral anticipation.
                "striatum_posvsneg_feedback"
                )]

data$src_subject_id <- as.factor(data$src_subject_id)
data$rel_family_id <- as.factor(data$rel_family_id)
data$eventname <- as.factor(data$eventname)
data$sex <- as.factor(data$sex)
data$demo_race_hispanic <- as.factor(data$demo_race_hispanic)
data$site_id_l <- as.factor(data$site_id_l)
data$mri_info_deviceserialnumber <- as.factor(data$mri_info_deviceserialnumber)
data$race.eth.7level <- as.factor(data$race.eth.7level)
data$high.educ <- as.factor(data$high.educ)
data$household.income <- as.factor(data$household.income)
data$married.or.livingtogether <- as.factor(data$married.or.livingtogether)

```

# Confirmatory Hypothesis 1: We hypothesize that pubertal stage will be associated with neural response to reward during a monetary incentive delay task (Braams et al., 2015). In particular, we expect heightened striatal activation during reward anticipation for more advanced pubertal stages.
## Model: Striatal activation (anticipation stage) ~ Pubertal stage
```{r Confirmatory1, echo = FALSE}
# Use data with only correct PDS scores.
PDS_correct <- subset(data, PDS_score < 5)

confirmatory1 <- lm(striatum_rvsn_ant ~ PDS_score +
                      race.eth.7level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      data = PDS_correct)
summary(confirmatory1)
# (1|site_id_l/rel_family_id), # Not sure how to write this part?
plot_model(confirmatory1,type = "pred", terms = "PDS_score", show.data = FALSE) 

#      Random effects.
#           1. Family. (rel_family_id) # Make sure this is nested correctly and looks about right.
#           2. Site. (site_id_l)
#           3. Subject. (src_subject_id) # There is only one timepoint so we cannot do a random effect for each participant.
#           4. Device. # mri_info_deviceserialnumber.

```
# Exploratory Hypothesis 1A: We will explore whether striatal activation during reward feedback is related to pubertal stage.
## Model: Striatal activation (feedback stage) ~ Pubertal stage 
```{r Exploratory1A, echo = FALSE}

```
# Exploratory Hypothesis 1B: We hypothesize that more advanced pubertal stages will be associated with greater self-reported reward responsiveness (BAS - RR) (Harden et al. 2018).
## Model: BIS-BAS-RR ~ Pubertal stage
```{r Exploratory1B, echo = FALSE}

```
# Exploratory Hypothesis 1C: We hypothesize that greater pubertal stage will be associated with greater behavioral reactivity to reward (i.e., reaction time on reward vs. neutral trials).
## Model: Reaction Time ~ Pubertal Stage
```{r Exploratory1C, echo = FALSE}

```
# Exploratory Hypothesis 1D: We hypothesize that testosterone will be positively associated with our indicators of reward (neural activity, behavioral reaction time, and self-reported reward responsiveness).
## Model A: Striatal activation (anticipation stage) ~ Testosterone
## Model B: Striatal activation (feedback stage) ~ Testosterone
## Model C: OFC activation (anticipation stage) ~ Testosterone
## Model D: OFC activation (feedback stage) ~ Testosterone
## Model E: MID Reaction Time ~ Testosterone
## Model F: BIS-BAS-RR ~ Testosterone
```{r Exploratory1D, echo = FALSE}

```