---
title: "Research Question 2: Does pubertal development relate to internalizing symptoms?"
date: "August 2020"
output:
  html_document: default
  pdf_document: default
authors: Natalie Saragosa-Harris 
---

``` {r loadPackages, echo = FALSE, message=FALSE, warning=FALSE}
#install.packages("gamm4.test")
#install.packages("mgcv")
install.packages("gamm4")

library(ggplot2)
library(gamm4)
library(dplyr)
library(sjPlot)
library(lmerTest)
library(here)
library(gamm4.test)
library(mgcv)
```

```{r LoadData, echo = FALSE}

# Elizabeth.
# Data: Desktop⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code: Desktop⁩ ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code⁩

# Lucia.
# Data:  Github⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Github ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# Natalie.
# Data:  Desktop ▸ ABCD⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Desktop ▸ ABCD ⁩▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# LMW alternative to read in the data.

data_dir = ((dirname(here()))) 

phase_folder = "exploratory"  # select the appropiate folder.
#phase_folder = "confirmatory"  # select the appropiate folder.

data_folder <- file.path(data_dir,"ABCD","derivatives",phase_folder)

file_name <- "nda20_exploratory.csv" # specify file name here. 

fulldata <- read.csv(file.path(data_folder,file_name))
length(fulldata$src_subject_id) # 5934.

# Call function to define all of the dataframes.
script_path <- file.path(data_dir,"rewardprocesses_internalizing_puberty_exploratory","code","define_dataframes.R")
source(script_path)

```

# Are there general gender differences in CBCL scores?
```{r CBCLDescriptives, echo = FALSE}
# Use data with only correct PDS scores, excluding CBCL outliers.
dataformodel <- data_no_CBCL_outliers
females <- data_no_CBCL_outliers_females
males <- data_no_CBCL_outliers_males

# Get an idea of the sample.
mean(dataformodel$cbcl_scr_syn_internal_r,na.rm= TRUE) # 4.633976.
mean(females$cbcl_scr_syn_internal_r,na.rm= TRUE) # 4.635062.
mean(males$cbcl_scr_syn_internal_r,na.rm= TRUE) # 4.632941.
min(females$cbcl_scr_syn_internal_r,na.rm= TRUE) # 0.0.
min(males$cbcl_scr_syn_internal_r,na.rm= TRUE) # 0.0.
t.test(males$cbcl_scr_syn_internal_r,females$cbcl_scr_syn_internal_r) # Not significant.

```
## All CBCL data
```{r CBCLDescriptives, echo = FALSE}
# Use data with only correct PDS scores, excluding CBCL outliers.
dataformodel <- PDS_correct
females <- PDS_correct_females
males <- PDS_correct_males

# Get an idea of the sample.
mean(dataformodel$cbcl_scr_syn_internal_r,na.rm= TRUE) # 4.633976.
mean(females$cbcl_scr_syn_internal_r,na.rm= TRUE) # 4.635062.
mean(males$cbcl_scr_syn_internal_r,na.rm= TRUE) # 4.632941.
min(females$cbcl_scr_syn_internal_r,na.rm= TRUE) # 0.0.
min(males$cbcl_scr_syn_internal_r,na.rm= TRUE) # 0.0.
t.test(males$cbcl_scr_syn_internal_r,females$cbcl_scr_syn_internal_r) # Not significant.

```



# Plot data.
## CBCL internalizing factor ~ Pubertal stage
```{r Confirmatory2, echo = FALSE}
# Excluding CBCL outliers.
dataformodel <- data_no_CBCL_outliers

ggplot(dataformodel, aes(x=PDS_score, y = cbcl_scr_syn_internal_r, group = src_subject_id, color=sex, fill = sex)) +
  geom_point(size = 4, alpha = 0.8,position = position_jitterdodge()) +
  scale_color_manual(values = c("#7BACAB", "gray40"), labels = c("Female", "Male"), name = "Sex") +
  scale_fill_manual(values = c("#7BACAB", "gray40"), labels = c("Female", "Male"), name = "Sex") +
  ylab("CBCL Internalizing") +
  xlab("PDS Score")

```

## All CBCL: CBCL internalizing factor ~ Pubertal stage
```{r Confirmatory2, echo = FALSE}
# Including CBCL outliers.
dataformodel <- PDS_correct

ggplot(dataformodel, aes(x=PDS_score, y = cbcl_scr_syn_internal_r, group = src_subject_id, color=sex, fill = sex)) +
  geom_point(size = 4, alpha = 0.8,position = position_jitterdodge()) +
  scale_color_manual(values = c("#7BACAB", "gray40"), labels = c("Female", "Male"), name = "Sex") +
  scale_fill_manual(values = c("#7BACAB", "gray40"), labels = c("Female", "Male"), name = "Sex") +
  ylab("CBCL Internalizing") +
  xlab("PDS Score")

```


# Confirmatory Hypothesis 2: We hypothesize that advanced pubertal stage will be associated with higher internalizing symptoms as measured by the Child Behavior Checklist (CBCL) internalizing factor (Ullsperger & Nikolas, 2017).

## Model: CBCL internalizing factor ~ Pubertal stage
## Females and males modeled separately.
```{r Confirmatory2, echo = FALSE}
# Excluding CBCL outliers.
dataformodel <- data_no_CBCL_outliers_females

# Females.
confirmatory2_females <- gamm4(cbcl_scr_syn_internal_r ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      data = dataformodel, 
                      random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2_females$gam) # PDS p < 0.001; R squared = 0.0388.

# Males.
dataformodel <- data_no_CBCL_outliers_males
confirmatory2_males <- gamm4(cbcl_scr_syn_internal_r ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      data = dataformodel, 
                      random = ~ (1 | site_id_l/rel_family_id))
          
summary(confirmatory2_males$gam) # PDS p < 0.001; R squared = 0.024.

```

## All CBCL: Females and males modeled separately.
```{r Confirmatory2, echo = FALSE}
# Excluding CBCL outliers.
dataformodel <- PDS_correct_females

# Females.
confirmatory2_females <- gamm4(cbcl_scr_syn_internal_r ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      data = dataformodel, 
                      random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2_females$gam)

# Males.
dataformodel <- PDS_correct_males

confirmatory2_males <- gamm4(cbcl_scr_syn_internal_r ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      data = dataformodel, 
                      random = ~ (1 | site_id_l/rel_family_id))
          
summary(confirmatory2_males$gam)

```


# What about PDS category (instead of continuous)?
## Females and males modeled separately.
```{r Confirmatory2_category, echo = FALSE}
# Females.
dataformodel <- data_no_CBCL_outliers_females
confirmatory2_category_females <- gamm4(cbcl_scr_syn_internal_r ~ pds_p_ss_category +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      data = dataformodel, 
                      random = ~ (1 | site_id_l/rel_family_id))
summary(confirmatory2_category_females$gam) # PDS category 2: p < 0.001, PDS category 3: p < 0.001, PDS category 4 = 0.03; R squared = 0.406.

# Males.
dataformodel <- data_no_CBCL_outliers_males
confirmatory2_category_males <- gamm4(cbcl_scr_syn_internal_r ~ pds_p_ss_category +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      data = dataformodel, 
                      random = ~ (1 | site_id_l/rel_family_id))
summary(confirmatory2_category_males$gam) # PDS category 2: p = 0.1859, PDS category 3: p < 0.001, PDS category 4 = 0.10; R squared = 00275.
```

## All CBCL: Females and males modeled separately.
```{r Confirmatory2_category, echo = FALSE}
# Females.
dataformodel <- PDS_correct_females
confirmatory2_category_females <- gamm4(cbcl_scr_syn_internal_r ~ pds_p_ss_category +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      data = dataformodel, 
                      random = ~ (1 | site_id_l/rel_family_id))
summary(confirmatory2_category_females$gam) 

# Males.
dataformodel <- PDS_correct_males
confirmatory2_category_males <- gamm4(cbcl_scr_syn_internal_r ~ pds_p_ss_category +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      data = dataformodel, 
                      random = ~ (1 | site_id_l/rel_family_id))
summary(confirmatory2_category_males$gam)
```


# Is there a quadratic effect of PDS score? Maybe something about the initial transition to puberty?
## Females and males modeled separately.
```{r Confirmatory2_quadratic, echo = FALSE}

# Create quadratic PDS score variable.
data_no_CBCL_outliers_females$PDS_score_squared <- (data_no_CBCL_outliers_females$PDS_score)^2
data_no_CBCL_outliers_males$PDS_score_squared <- (data_no_CBCL_outliers_males$PDS_score)^2

# Females.
dataformodel <- data_no_CBCL_outliers_females
confirmatory2_quadratic_females <- gamm4(cbcl_scr_syn_internal_r ~ PDS_score + PDS_score_squared +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      data = dataformodel, 
                      random = ~ (1 | site_id_l/rel_family_id))
summary(confirmatory2_quadratic_females$gam)
# Quadratic effect p = 0.08 (not significant); linear effect p = 0.00121.

# Males.
dataformodel <- data_no_CBCL_outliers_males
confirmatory2_quadratic_males <- gamm4(cbcl_scr_syn_internal_r ~ PDS_score + PDS_score_squared +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      data = dataformodel, 
                      random = ~ (1 | site_id_l/rel_family_id))
summary(confirmatory2_quadratic_males$gam)
# Quadratic effect p = 0.18 (not significant); linear effect p = 0.0576.

# So there is a significant linear effect, but not a significant quadratic effect, of PDS for both males and females.
plot_model(confirmatory2_quadratic, type = "pred", terms = c("PDS_score")) # Can't figure out how to plot quadratic estimate from multilevel model.

# Trying a simpler model first, just for plotting purposes.
confirmatory2_quadratic_simple <-lm(cbcl_scr_syn_internal_r ~ PDS_score + PDS_score_squared, data = dataformodel)
summary(confirmatory2_quadratic_simple)
plotdata <-dataformodel
plotdata$predicted <- fortify(confirmatory2_quadratic_simple)$.fitted # Add predicted values from model to the data to plot.

# Just plot the model predictions (to make sure later graphs are correct when the predicted quadratic is added to original data).
ggplot(plotdata,aes(x=PDS_score, y=predicted)) +
      geom_point() +
      ylim(min(dataformodel$cbcl_scr_syn_internal_r),max(dataformodel$cbcl_scr_syn_internal_r)) +
      xlab("PDS Score") +
      ylab("Model Predicted CBCL score") 
# In the quadratic effect, it does not predict CBCL to be above 5.27? Why?
max(predict(confirmatory2_quadratic_simple)) #5.271192
min(predict(confirmatory2_quadratic_simple)) #3.98063
```
#### Quick plots (Females)
```{r}
#Quick plots
#plot_model(confirmatory2_females,type = "pred", show.data = TRUE) # Interaction plot.

#plot_model(confirmatory2_females,type = "std", show.data = TRUE) # Forest plot with standarized coefficients.
```

#### Quick plots (Males)
```{r}
#Quick plots
#plot_model(confirmatory2_males,type = "pred", show.data = FALSE) #Interaction plot.

#plot_model(confirmatory2_males,type = "std", show.data = FALSE) #Forest plot with standarized coefficients.
```


# Exploratory Hypothesis 2: We will investigate whether testosterone relates to internalizing symptoms and whether this relationship is present after controlling for PDS.
## Model A: CBCL internalizing factor ~ Testosterone
```{r Exploratory2A, echo = FALSE}
# Get an idea of the sample.
mean(data_no_CBCL_test_outliers$hormone_scr_ert_mean,na.rm= TRUE) # 34.33287.
mean(data_no_CBCL_test_outliers_females$hormone_scr_ert_mean,na.rm= TRUE) # 36.38213.
mean(data_no_CBCL_test_outliers_males$hormone_scr_ert_mean,na.rm= TRUE) # 32.38652.
range(data_no_CBCL_test_outliers_females$hormone_scr_ert_mean,na.rm= TRUE) # 5.0200 to 88.1075.
range(data_no_CBCL_test_outliers_males$hormone_scr_ert_mean,na.rm= TRUE) # 2.2725 to 89.5700.
range(data_no_CBCL_test_outliers_females$hormone_scr_ert_mean_z,na.rm= TRUE) # -1.616918 to 2.834996 (z scores).
range(data_no_CBCL_test_outliers_males$hormone_scr_ert_mean_z,na.rm= TRUE) # -1.764131 to 2.913358 (z scores).
t.test(data_no_CBCL_test_outliers_males$hormone_scr_ert_mean,data_no_CBCL_test_outliers_females$hormone_scr_ert_mean)
# average for males is 32.39, and average for females is 36.38; p < 0.001.
```

```{r}
dataformodel <- data_no_CBCL_test_outliers

confirmatory2_testosterone_CBCL <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,
                      random = ~(1 | site_id_l/rel_family_id))
                      
summary(confirmatory2_testosterone_CBCL$gam)
```


#### Female.
```{r}
dataformodel <- data_no_CBCL_test_outliers_females

confirmatory2_testosterone_CBCL_female <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2_testosterone_CBCL_female$gam)
```

#### Male.
```{r}
dataformodel <- data_no_CBCL_test_outliers_males

confirmatory2_testosterone_CBCL_male <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2_testosterone_CBCL_male$gam)
```



#### All CBCL: Female.
```{r}
dataformodel <- data_no_test_outliers_females

confirmatory2_testosterone_CBCL_female <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2_testosterone_CBCL_female$gam)
```

#### All CBCL: Male.
```{r}
dataformodel <- data_no_test_outliers_males

confirmatory2_testosterone_CBCL_male <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2_testosterone_CBCL_male$gam)
```




## Model B: CBCL internalizing factor ~ Testosterone + Pubertal stage 
#### Female.
```{r Exploratory2B, echo = FALSE}

dataformodel <- data_no_CBCL_test_outliers_females

confirmatory2B_testosterone_CBCL_female <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z + PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,  
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2B_testosterone_CBCL_female$gam)

# PDS category.

dataformodel <- subset(PDS_correct_females, hormone_scr_ert_mean_z > -3 & hormone_scr_ert_mean_z < 3 & cbcl_scr_syn_internal_r_z > -3 & cbcl_scr_syn_internal_r_z < 3 & pds_p_ss_category !="5")

confirmatory2B_testosterone_CBCL_female_category <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z + pds_p_ss_category +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,  
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2B_testosterone_CBCL_female_category$gam)
```

#### Male.
```{r}
dataformodel <- data_no_CBCL_test_outliers_males %>% 
  

confirmatory2B_testosterone_CBCL_male <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z + PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2B_testosterone_CBCL_male$gam)

# PDS category.
confirmatory2B_testosterone_CBCL_male_category <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z + pds_p_ss_category +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2B_testosterone_CBCL_male_category$gam)
```


#### All CBCL: Female.
```{r Exploratory2B, echo = FALSE}

dataformodel <- data_no_test_outliers_females

confirmatory2B_testosterone_CBCL_female <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z + PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,  
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2B_testosterone_CBCL_female$gam)

# PDS category.

dataformodel <- subset(PDS_correct_females, hormone_scr_ert_mean_z > -3 & hormone_scr_ert_mean_z < 3 & pds_p_ss_category !="5")

confirmatory2B_testosterone_CBCL_female_category <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z + pds_p_ss_category +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,  
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2B_testosterone_CBCL_female_category$gam)
```

#### All CBCL: Male.
```{r}
dataformodel <- data_no_test_outliers_males 
  

confirmatory2B_testosterone_CBCL_male <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z + PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2B_testosterone_CBCL_male$gam)

# PDS category.
confirmatory2B_testosterone_CBCL_male_category <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean_z + pds_p_ss_category +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic,
                      #fam_history_q6d_depression + #added mother's depression
                      data = dataformodel,
                      random = ~ (1 | site_id_l/rel_family_id))
                      
summary(confirmatory2B_testosterone_CBCL_male_category$gam)
```
