---
title: "Research Question 4: Do neural and self-reported responses to reward moderate the relationship between pubertal development and internalizing symptoms?"
date: "August 2020"
output:
  html_document: default
  pdf_document: default
authors: Natalie Saragosa-Harris 
---
``` {r loadPackages, echo = FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(gamm4)
library(dplyr)
library(sjPlot)
library(here)
library(jtools)
library(interactions)
library(gamm4.test)
library(ggstatsplot)
```

```{r LoadData, echo = FALSE}

# Elizabeth.
# Data: Desktop⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code: Desktop⁩ ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code⁩

# Lucia.
# Data:  Github⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Github ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# Natalie.
# Data:  Desktop ▸ ABCD⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Desktop ▸ ABCD ⁩▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# LMW alternative to read in the data.

data_dir = ((dirname(here()))) 

phase_folder = "exploratory"  # select the appropiate folder.
#phase_folder = "confirmatory"  # select the appropiate folder.

data_folder <- file.path(data_dir,"ABCD","derivatives",phase_folder)

file_name <- "nda20_exploratory.csv" # specify file name here. 

fulldata <- read.csv(file.path(data_folder,file_name))
length(fulldata$src_subject_id) # 5934.

# Call function to define all of the dataframes.
script_path <- file.path(data_dir,"rewardprocesses_internalizing_puberty_exploratory","code","define_dataframes.R")
source(script_path)
```

# Confirmatory Hypothesis 4: We predict that striatal responses to reward will moderate the effect of pubertal stage such that the relationship between advanced pubertal status and internalizing symptoms will be stronger among participants with attenuated activation in striatal reward circuitry during reward anticipation.

#Basic data checks and transformations
```{r Confirmatory4, echo = FALSE}
# Use combined score for accumbens, caudate, and putamen?
# Jen: I would probably run the 3 separately and control for multiple comparisons. If the three give you highly correlated results you could take a composite measure for subsequent analyses.
cor.test(data$accumbens_rvsn_ant_z,data$caudate_rvsn_ant_z) # 0.64.
cor.test(data$accumbens_rvsn_ant_z,data$putamen_rvsn_ant_z) # 0.63.
cor.test(data$caudate_rvsn_ant_z,data$putamen_rvsn_ant_z) # 0.851. 

#Explore outliers
boxplot(data$accumbens_rvsn_ant_z)
boxplot(data$caudate_rvsn_ant_z)
boxplot(data$putamen_rvsn_ant_z)
boxplot(data$cbcl_scr_syn_internal_r)
```
#Count NAs per variable 
```{r}
#Count NAs per variable 
# We are missing many cases of maternal depression - consider dropping
dataformodel <- data_no_CBCL_striatal_ant_outliers 

sum(is.na(dataformodel$src_subject_id)) #0 missing  
sum(is.na(dataformodel$sex))  #0 missing   
sum(is.na(dataformodel$mri_info_deviceserialnumber)) #0 missing 
sum(is.na(dataformodel$rel_family_id)) #0 missing 
sum(is.na(dataformodel$race.ethnicity.5level)) #41
sum(is.na(dataformodel$demo_race_hispanic))  #50
sum(is.na(dataformodel$high.educ))  #3
sum(is.na(dataformodel$household.income)) #293
sum(is.na(dataformodel$married.or.livingtogether))  #22
sum(is.na(dataformodel$fam_history_q6d_depression)) #1937 missing!

#summary(dataformodel)

#Also, some brain variables seem to have large outliers. Check before including in the models 
```

##  Model: CBCL internalizing factor ~ PDS*Striatal activity (anticipation stage)
##  N o
```{r Confirmatory4, echo = FALSE}
# Composite striatum score, exlcuding outliers.
# No CBCL exclusions
# With covariates

dataformodel <- data_no_striatal_ant_outliers  #Specify data subset here

confirmatory4_compositestriatum <- gamm4(cbcl_scr_syn_internal_r ~ 
                            interview_age+
                            PDS_score_z+
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether 
                            , data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4_compositestriatum$gam)

plot_model(confirmatory4_compositestriatum,type = "pred", show.data = TRUE) #Interaction plot

plot_model(confirmatory4_compositestriatum,type = "est", show.data = TRUE) #Forest plot

#p <- plot_model(confirmatory4_compositestriatum,type = "int", terms = "PDS_score",            show.data = TRUE, jitter = 0.1, line.size = 2) +

#file.name = (here("output","question4_exploratory.tiff"))
#ggsave(file.name,plot = last_plot(), dpi = 150, device = "tiff")

#p <- ggplot( data = subset(PDS_correct, striatum_rvsn_ant_z > -3 & striatum_rvsn_ant_z < 3), aes(x=sex, y=striatum_rvsn_ant_z)) + 
#  geom_boxplot()
#p
```

# Core model (no covariates)
```{r}
# Core model (no covariates)
# Composite striatum score.
# Excluding CBCL outliers 
# Without covariates

dataformodel <- data_no_CBCL_striatal_ant_outliers

#Select only cases that have complete data for all covariates of intest. It seems that we are missing many cases of maternal depression. We might drop it going forwards. 
tempdata <- dataformodel[which(complete.cases(dataformodel[,c("race.ethnicity.5level",
                            "demo_race_hispanic",
                            "high.educ",
                            "household.income",
                            "married.or.livingtogether",
                            "interview_age"
                            )])),]
nrow(dataformodel)
nrow(tempdata)

confirmatory4_compositestriatum_excludingoutliers_core <- gamm4(cbcl_scr_syn_internal_r ~
                                           PDS_score*striatum_rvsn_ant_z+
                                           sex,
                                           data = tempdata,random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4_compositestriatum_excludingoutliers_core)

print.gamtest(confirmatory4_compositestriatum_excludingoutliers_core,2)

plot_model(confirmatory4_compositestriatum_excludingoutliers_core,type = "int", show.data = FALSE, show.p = TRUE) #Interaction plot

plot_model(confirmatory4_compositestriatum_excludingoutliers_core,type = "std", show.data = FALSE) #Forest plot

# p <- plot_model(confirmatory4_compositestriatum_excludingoutliers_core,
#                 type = "pred", # To specify values for striatal response, have to use "pred" instead.
#                 terms = c("PDS_score","striatum_rvsn_ant_z [-2.0,0,2.0]"),
#                 show.data = TRUE, jitter = 0.1, line.size = 2) +
#                 ylab("Internalizing Score") +
#                 xlab("Average PDS score") +
#                 labs(colour = "MID Striatal activity z-score \n (reward anticipation vs neutral)")+
#                 scale_y_continuous(breaks = seq(0, 45, by = 10), limits = c(0,45)) +
#                 theme(title= element_text(size=20, vjust=2, face="bold"),
#                 plot.title = element_blank(),
#                 axis.title.x= element_text(size=18, vjust=-0.3),
#                 axis.title.y= element_text(size=18, vjust=1.5),
#                 axis.text.x= element_text(size=18, colour="black"),
#                 axis.text.y= element_text(size=18, colour="black"),
#                 legend.title=element_text(size=12, colour = "black"),
#                 legend.position = c(.80, .80),
#                 # legend.position="none",
#                 strip.text = element_text(size=18, face="bold"),
#                 panel.background = element_blank(),
#                 axis.line = element_line(colour = "black"))
# p 

```

```{r}
#Exploring PDS outliers
d <- density(PDS_correct_females$PDS_score) # returns the density data
plot(d) # plots the results

p2 <- ggplot(data=PDS_correct, aes(x=PDS_score, group=sex, fill=sex)) +
    geom_density(adjust=1.5, alpha=.4) 
p2

summary(PDS_correct$PDS_score)
boxplot(PDS_correct$PDS_score,spread_text = F)

ggbetweenstats(data = PDS_correct, 
               x = sex,
               y = PDS_score, 
               outlier.coef = 3.0,
               outlier.tagging = TRUE,
               outlier.label = src_subject_id)
```


```{r}
#Excluding outliers in CBCL 
#Reveals main effect of striatum as well as interaction, but in the opposite way?

dataformodel<- data_no_CBCL_striatal_ant_outliers_males
dataformodel<-data_no_CBCL_striatal_ant_outliers_females_pubertal

#Select only cases that have complete data for all covariates of intest. It seems that we are missing many cases of maternal depression. We might drop it going forwards. 
tempdata <- dataformodel[which(complete.cases(dataformodel[,c("race.ethnicity.5level",
                            "demo_race_hispanic",
                            "high.educ",
                            "household.income",
                            "married.or.livingtogether",
                            "interview_age"
                            )])),]

confirmatory4_compositestriatum_excludingoutliers <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z+
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

confirmatory4_compositestriatum_excludingoutliers <- lme4::lmer(cbcl_scr_syn_internal_r ~ 
                            pds_p_ss_category*
                            striatum_rvsn_ant_z+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age+
                          #  fam_history_q6d_depression + #added mother's depression
                            (1 | site_id_l/rel_family_id),  #same thing as site is the same thing as (1|site) + (1|family:site), this is what done in paper by Paulus et al. (2019), 22 sites 
#data = subset(PDS_correct, striatum_rvsn_ant_z > -3 & striatum_rvsn_ant_z < 3 & cbcl_scr_syn_internal_r_z > -3 & cbcl_scr_syn_internal_r_z < 3))
data = tempdata)
summary(confirmatory4_compositestriatum_excludingoutliers)


mod <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z^2+
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

plot_model(mod$mer,type = "est", show.data = FALSE, show.p = TRUE) #Interaction plot


print(mod$gam)
print(summary(mod))

summary(mod$gam)

vis.gam(mod$gam)

summary(confirmatory4_compositestriatum_excludingoutliers)
gam.grptest(confirmatory4_compositestriatum_excludingoutliers)

```

```{r}
#Quick plots
plot_model(confirmatory4_compositestriatum_excludingoutliers,type = "int", show.data = FALSE) #Interaction plot

plot_model(confirmatory4_compositestriatum_excludingoutliers,type = "std", show.data = FALSE) #Forest plot with standarized coefficients
```

```{r}
#Compare model with and without covariates - adding covariates makes the model significantly improve
anova(confirmatory4_compositestriatum_excludingoutliers_core,confirmatory4_compositestriatum_excludingoutliers)
```

```{r}
#Publication plot
#Both sexes

p <- plot_model(confirmatory4_compositestriatum_excludingoutliers,
                type = "pred", # To specify values for striatal response, have to use "pred" instead.
                terms = c("PDS_score","striatum_rvsn_ant_z [-2.0,0,2.0]"),
                show.data = TRUE, jitter = 0.1, line.size = 2) +
                ylab("Internalizing Score") +
                xlab("Average PDS score") +
                labs(colour = "MID Striatal activity z-score \n (reward anticipation vs neutral)")+
                scale_y_continuous(breaks = seq(0, 45, by = 10), limits = c(0,45)) +
                theme(title= element_text(size=20, vjust=2, face="bold"),
                plot.title = element_blank(),
                axis.title.x= element_text(size=18, vjust=-0.3),
                axis.title.y= element_text(size=18, vjust=1.5),
                axis.text.x= element_text(size=18, colour="black"),
                axis.text.y= element_text(size=18, colour="black"),
                legend.title=element_text(size=12, colour = "black"),
                legend.position = c(.80, .80),
                # legend.position="none",
                strip.text = element_text(size=18, face="bold"),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"))
p 
                 
file.name = (here("output","question4_exploratory_excludingCBCLoutliers.tiff"))
#ggsave(file.name,plot = last_plot(), dpi = 150, device = "tiff")
```

# Excluding outliers in CBCL 
## Splitting by sex
## FEMALES
```{r}
# Excluding outliers in CBCL 
# Splitting by sex
# FEMALES

dataformodel <- data_no_CBCL_striatal_ant_outliers_females

confirmatory4_compositestriatum_excludingoutliers <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z+
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(PDS_correct_females$interview_age)
summary(confirmatory4_compositestriatum_excludingoutliers_femalesonly)
```
```{r}
#Quick plots
plot_model(confirmatory4_compositestriatum_excludingoutliers_femalesonly,type = "pred", terms = c("PDS_score","striatum_rvsn_ant_z [-2.0,0,2.0]"),show.data = FALSE) #Interaction plot

plot_model(confirmatory4_compositestriatum_excludingoutliers_femalesonly, type= "std",how.data = FALSE) #Forest plot with standardized coefficients
```

```{r}
# Excluding outliers in CBCL 
# Splitting by sex
# MALES

dataformodel <- data_no_CBCL_striatal_ant_outliers_males

confirmatory4_compositestriatum_excludingoutliers_malesonly <- lmer(cbcl_scr_syn_internal_r ~ 
                            PDS_score*striatum_rvsn_ant_z +
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age+
                            #fam_history_q6d_depression + #added mother's depression
                            (1 | site_id_l/rel_family_id),
                            dataformodel)

summary(confirmatory4_compositestriatum_excludingoutliers_malesonly)
```
```{r}
#Quick plots
plot_model(confirmatory4_compositestriatum_excludingoutliers_malesonly,type = "pred", terms = c("PDS_score","striatum_rvsn_ant_z [-2.0,0,2.0]"),show.data = FALSE) #Interaction plot

plot_model(confirmatory4_compositestriatum_excludingoutliers_malesonly,type = "std", show.data = FALSE) #Forest plot with standarized coefficients
```


```{r}
#Excluding outliers in CBCL 
#PDS category 

confirmatory4_compositestriatum_excludingoutliers_cat <- lmer(cbcl_scr_syn_internal_r ~                                       pds_p_ss_category*striatum_rvsn_ant_z +
                            race.eth.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age+
                            fam_history_q6d_depression + #added mother's depression
                            (1 | site_id_l/rel_family_id),
                            data = subset(PDS_correct, 
                                          striatum_rvsn_ant_z > -3 & striatum_rvsn_ant_z < 3 & cbcl_scr_syn_internal_r_z > -3 & cbcl_scr_syn_internal_r_z < 3))

summary(confirmatory4_compositestriatum_excludingoutliers_cat)

plot_model(confirmatory4_compositestriatum_excludingoutliers_cat,type = "int", show.data = FALSE) #Interaction plot

plot_model(confirmatory4_compositestriatum_excludingoutliers,type = "est", show.data = FALSE) #Forest plot

p <- plot_model(confirmatory4_compositestriatum_excludingoutliers_cat,
                type = "pred", # To specify values for striatal response, have to use "pred" instead.
                terms = c("pds_p_ss_category","striatum_rvsn_ant_z [-2.0,0,2.0]"),
                show.data = TRUE, jitter = 0.1, line.size = 2) +
                ylab("Internalizing Score") +
                xlab("PDS category") +
                labs(colour = "MID Striatal activity z-score \n (reward anticipation vs neutral)")+
                scale_y_continuous(breaks = seq(0, 45, by = 10), limits = c(0,45)) +
                theme(title= element_text(size=20, vjust=2, face="bold"),
                plot.title = element_blank(),
                axis.title.x= element_text(size=18, vjust=-0.3),
                axis.title.y= element_text(size=18, vjust=1.5),
                axis.text.x= element_text(size=18, colour="black"),
                axis.text.y= element_text(size=18, colour="black"),
                legend.title=element_text(size=12, colour = "black"),
                legend.position = c(.80, .80),
                # legend.position="none",
                strip.text = element_text(size=18, face="bold"),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"))
p 
                   
file.name = (here("output","question4_exploratory_excludingCBCLoutliers_PDScat.tiff"))
ggsave(file.name,plot = last_plot(), dpi = 150, device = "tiff")

```



```{r}
#Quickly checking whether reward is associated with pubertal development
#This needs to be moved to the another script
exploratory_compositestriatum_puberty <- lmer(striatum_rvsn_ant_z ~ 
                                           PDS_score +
                            race.eth.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age+
                            fam_history_q6d_depression + #added mother's depression
                            (1 | site_id_l/rel_family_id),
                            data = subset(PDS_correct, 
                                          striatum_rvsn_ant_z > -3 & striatum_rvsn_ant_z < 3))
summary(exploratory_compositestriatum_puberty )

plot_model(confirmatory4_compositestriatum_excludingoutliers,type = "int", show.data = FALSE) #Interaction plot

plot_model(exploratory_compositestriatum_puberty,type = "est", show.data = FALSE) #Forest plot

p <- plot_model(exploratory_compositestriatum_puberty,type,
                type = "pred", # To specify values for striatal response, have to use "pred" instead.
                terms = c("PDS_score"),
                show.data = TRUE, jitter = 0.1, line.size = 2) +
                ylab("MID Striatal activity z-score \n (reward anticipation vs neutral)") +
                xlab("Average PDS score") +
                #labs(colour = "MID Striatal activity z-score \n (reward anticipation vs neutral)")+
                #scale_y_continuous(breaks = seq(0, 45, by = 10), limits = c(0,45)) +
                theme(title= element_text(size=20, vjust=2, face="bold"),
                plot.title = element_blank(),
                axis.title.x= element_text(size=18, vjust=-0.3),
                axis.title.y= element_text(size=18, vjust=1.5),
                axis.text.x= element_text(size=18, colour="black"),
                axis.text.y= element_text(size=18, colour="black"),
                legend.title=element_text(size=12, colour = "black"),
                legend.position = c(.80, .80),
                # legend.position="none",
                strip.text = element_text(size=18, face="bold"),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"))
p 
                   
                   
                   

file.name = (here("output","striatum_puberty.tiff"))
#ggsave(file.name,plot = last_plot(), dpi = 150, device = "tiff")

```


# Exploratory Hypothesis 4A: We will investigate whether striatal responses to reward during reward feedback moderates the effect of pubertal stage on internalizing symptoms. 
## Model: CBCL internalizing factor ~ PDS*Striatal activity (feedback stage) Females
```{r Exploratory4A, echo = FALSE}
#Composite striatum score, FEMALES

dataformodel <- data_no_CBCL_striatal_feed_outliers_females

exploratory4a_compositestriatum_feedback_excludingoutliers_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4a_compositestriatum_feedback_excludingoutliers_females$mer )
```
## Model: CBCL internalizing factor ~ PDS*Striatal activity (feedback stage) Males
```{r Exploratory4A, echo = FALSE}
#Composite striatum score, MALES

dataformodel <- data_no_CBCL_striatal_feed_outliers_males

exploratory4a_compositestriatum_feedback_excludingoutliers_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4a_compositestriatum_feedback_excludingoutliers_males$gam )
```


# Exploratory Hypothesis 4B: We will investigate whether OFC activation during reward anticipation and feedback moderates the relationship between pubertal stage and internalizing symptoms.
## Model A: CBCL internalizing factor ~ PDS*OFC activity (anticipation stage)
## Model B: CBCL internalizing factor ~ PDS*OFC activity (feedback stage)
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, FEMALES

dataformodel <- data_no_CBCL_lOFC_ant_outliers_females

exploratory4b_OFC_ant_excludingoutliers_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_ant_excludingoutliers_females$gam )
```

# Exploratory Hypothesis 4B: We will investigate whether OFC activation during reward anticipation and feedback moderates the relationship between pubertal stage and internalizing symptoms.
## Model A: CBCL internalizing factor ~ PDS*OFC activity (anticipation stage) MALES
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, MALES

dataformodel <- data_no_CBCL_lOFC_ant_outliers_males

exploratory4b_OFC_ant_excludingoutliers_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_ant_excludingoutliers_males$gam )
```

# Exploratory Hypothesis 4B: We will investigate whether OFC activation during reward anticipation and feedback moderates the relationship between pubertal stage and internalizing symptoms.
## Model A: CBCL internalizing factor ~ PDS*OFC activity (feedback stage) FEMALES
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, MALES

dataformodel <- data_no_CBCL_lOFC_feed_outliers_females

exploratory4b_OFC_feed_excludingoutliers_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_feed_excludingoutliers_females$gam )
```


# Exploratory Hypothesis 4B: We will investigate whether OFC activation during reward anticipation and feedback moderates the relationship between pubertal stage and internalizing symptoms.
## Model A: CBCL internalizing factor ~ PDS*OFC activity (feedback stage) MALES
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, MALES

dataformodel <- data_no_CBCL_lOFC_feed_outliers_males

exploratory4b_OFC_feed_excludingoutliers_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_feed_excludingoutliers_males$gam )
```


# Exploratory Hypothesis 4C: We hypothesize that the association between advanced puberty and internalizing symptoms will be moderated by self-reported reward responsiveness. We predict that advanced puberty will be associated with higher internalizing in individuals who report lower reward responsiveness on the BIS-BAS questionnaire.
## Model: CBCL internalizing factor ~ PDS*BIS-BAS
```{r Exploratory4C, echo = FALSE}
#FEMALES
dataformodel <- data_no_CBCL_outliers_females

exploratory4c_bisbas_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            bisbas_ss_basm_rr+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4c_bisbas_females$gam )
```

# Exploratory Hypothesis 4C: We hypothesize that the association between advanced puberty and internalizing symptoms will be moderated by self-reported reward responsiveness. We predict that advanced puberty will be associated with higher internalizing in individuals who report lower reward responsiveness on the BIS-BAS questionnaire.
## Model: CBCL internalizing factor ~ PDS*BIS-BAS
```{r Exploratory4C, echo = FALSE}
#MALES
dataformodel <- data_no_CBCL_outliers_males

exploratory4c_bisbas_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            bisbas_ss_basm_rr+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4c_bisbas_males$gam )
```



# Exploratory Hypothesis 4D: We hypothesize that the association between advanced puberty and internalizing symptoms will be moderated by behavioral reward responsiveness (i.e., MID reaction time). We predict that advanced puberty will be associated with higher internalizing in individuals who demonstrate lower behavioral reward responsiveness.
## Model: CBCL internalizing factor ~ PDS*MID reaction time
```{r Exploratory4D, echo = FALSE}
##Lucia: pick up here!

```

# Exploratory Hypothesis 4E: We will investigate whether testosterone, and its relationship with reward, relates to internalizing symptoms, while controlling for PDS.
## Model A: CBCL internalizing factor ~ Testosterone*Striatal activity (anticipation stage) + PDS
## Model B: CBCL internalizing factor ~ Testosterone*Striatal activity (feedback stage) + PDS
## Model C: CBCL internalizing factor ~ Testosterone*OFC activity (anticipation stage) + PDS
## Model D: CBCL internalizing factor ~ Testosterone*OFC activity (feedback stage) + PDS
## Model E: CBCL internalizing factor ~ Testosterone*BIS-BAS RR
## Model F: CBCL internalizing factor ~ Testosterone*MID Reaction Time
```{r Exploratory4E, echo = FALSE}


```