---
title: 'Supplement C: Testosterone Models Only (With Testosterone Outliers)'
subtitle: 'Reward sensitivity and internalizing symptoms during the transition to puberty: An examination of 9- and 10-year-olds in the ABCD Study.'
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
  html_document:
    toc: yes
    toc_depth: '3'
    toc_float:
      collapsed: true
---
# Sensitivity Analysis Results for Sample 1
  
```{r loadPackages, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(gamm4)
library(dplyr)
library(insight)
library(here)
library(lmerTest)
library(gamm4.test)
library(mgcv)
library(jtools)
library(interactions)
#library(ggstatsplot)

data_dir = ((dirname(here()))) 

phase_folder = "exploratory"  # select the appropriate folder.

data_folder <- file.path(data_dir,"ABCD","derivatives",phase_folder)

file_name <- "nda30_exploratory.csv" # specify file name here. 

fulldata <- read.csv(file.path(data_folder,file_name))
nrow(fulldata) # 27321 (exploratory). When call the define_dataframes script, will keep only the baseline data.

# Call function to define all of the dataframes.
script_path <- file.path(data_dir,"rewardprocesses_internalizing_puberty_exploratory","code","define_dataframes_keeptestosteroneoutliers.R")
source(script_path)

```

# 1---Internalizing~Puberty---

## 1.9 Model: CBCL internalizing factor ~ Testosterone
### Female participants
```{r, echo=FALSE}
dataformodel <- data_no_test_outliers_females

confirmatory2_testosterone_CBCL_female <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight + 
                                                  
                                                  race.ethnicity.5level +
                                                  interview_age + bmi + household.income + high.educ +
                                                  demo_race_hispanic,
                                                data = dataformodel,
                                                random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2_testosterone_CBCL_female$gam)
```
### Male participants
```{r, echo=FALSE}
dataformodel <- data_no_test_outliers_males

confirmatory2_testosterone_CBCL_male <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +
                                                race.ethnicity.5level +
                                                interview_age + bmi + household.income + high.educ +
                                                demo_race_hispanic,
                                              data = dataformodel,
                                              random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2_testosterone_CBCL_male$gam)
```
## 1.10 Model: CBCL Anxious-Depressed ~ Testosterone
### Female participants
```{r, echo=FALSE}
dataformodel <- data_no_test_outliers_females

confirmatory2_testosterone_CBCL_female <- gamm4(cbcl_scr_syn_anxdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight + 
                                                  race.ethnicity.5level +
                                                  interview_age + bmi + household.income + high.educ +
                                                  demo_race_hispanic,
                                                data = dataformodel,
                                                random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2_testosterone_CBCL_female$gam)
```
### Male participants
```{r, echo=FALSE}
dataformodel <- data_no_test_outliers_males

confirmatory2_testosterone_CBCL_male <- gamm4(cbcl_scr_syn_anxdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight + 
                                                race.ethnicity.5level +
                                                interview_age + bmi + household.income + high.educ +
                                                demo_race_hispanic,
                                              data = dataformodel,
                                              random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2_testosterone_CBCL_male$gam)
```

## 1.11 Model: CBCL Withdrawn-Depressed ~ Testosterone
### Female participants
```{r, echo=FALSE}
dataformodel <- data_no_test_outliers_females

confirmatory2_testosterone_CBCL_female <- gamm4(cbcl_scr_syn_withdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight + 
                                                  race.ethnicity.5level +
                                                  interview_age + bmi + household.income + high.educ +
                                                  demo_race_hispanic,
                                                data = dataformodel,
                                                random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2_testosterone_CBCL_female$gam)
```

### Male participants
```{r, echo=FALSE}
dataformodel <- data_no_test_outliers_males

confirmatory2_testosterone_CBCL_male <- gamm4(cbcl_scr_syn_withdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight + 
                                                race.ethnicity.5level +
                                                interview_age + bmi + household.income + high.educ +
                                                demo_race_hispanic,
                                              data = dataformodel,
                                              random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2_testosterone_CBCL_male$gam)
```
## 1.12 Model: CBCL Depressed DSM-5 ~ Testosterone
### Female participants
```{r, echo=FALSE}
dataformodel <- data_no_test_outliers_females

confirmatory2_testosterone_CBCL_female <- gamm4(cbcl_scr_dsm5_depress_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight + 
                                                  race.ethnicity.5level +
                                                  interview_age + bmi + household.income + high.educ +
                                                  demo_race_hispanic,
                                                data = dataformodel,
                                                random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2_testosterone_CBCL_female$gam)
```
### Male participants
```{r, echo=FALSE}
dataformodel <- data_no_test_outliers_males

confirmatory2_testosterone_CBCL_male <- gamm4(cbcl_scr_dsm5_depress_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight + 
                                                race.ethnicity.5level +
                                                interview_age + bmi + household.income + high.educ +
                                                demo_race_hispanic,
                                              data = dataformodel,
                                              random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2_testosterone_CBCL_male$gam)
```


## 1.13 Model: CBCL internalizing factor ~ Testosterone + PDS 
### Female participants
```{r, echo=FALSE}

dataformodel <- data_no_test_outliers_females

confirmatory2B_testosterone_CBCL_female <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  PDS_score +
                                                   race.ethnicity.5level +
                                                   interview_age + bmi + household.income + high.educ +
                                                   demo_race_hispanic,
                                                 data = dataformodel,  
                                                 random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_female$gam)
```
### Male participants
```{r, echo=FALSE}
dataformodel <- data_no_test_outliers_males 


confirmatory2B_testosterone_CBCL_male <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  PDS_score +
                                                 race.ethnicity.5level +
                                                 interview_age + bmi + household.income + high.educ +
                                                 demo_race_hispanic,
                                               data = dataformodel,
                                               random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_male$gam)
```

## 1.14 Model: CBCL internalizing factor ~ Testosterone + Pubertal category 
### Female participants
```{r, echo=FALSE}
# PDS category.

#dataformodel <- subset(PDS_correct_females, hormone_scr_ert_mean_z > -3 & hormone_scr_ert_mean_z < 3 & pds_p_ss_category !="5")
dataformodel <- subset(PDS_correct_females, pds_p_ss_category !="5")

confirmatory2B_testosterone_CBCL_female_category <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  pds_p_ss_category +
                                                            race.ethnicity.5level +
                                                            interview_age + bmi + household.income + high.educ +
                                                            demo_race_hispanic,
                                                          data = dataformodel,  
                                                          random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_female_category$gam)
```
### Male participants
```{r, echo=FALSE}
# PDS category.

#dataformodel <- subset(PDS_correct_males, hormone_scr_ert_mean_z > -3 & hormone_scr_ert_mean_z < 3 & pds_p_ss_category !="5")
dataformodel <- subset(PDS_correct_males, pds_p_ss_category !="5")

confirmatory2B_testosterone_CBCL_male_category <- gamm4(cbcl_scr_syn_internal_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  pds_p_ss_category +
                                                          race.ethnicity.5level +
                                                          interview_age + bmi + household.income + high.educ +
                                                          demo_race_hispanic,
                                                        data = dataformodel,
                                                        random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_male_category$gam)
```
## 1.15 Model: CBCL Anxious-Depressed ~ Testosterone + PDS 
### Female participants
```{r, echo=FALSE}

dataformodel <- data_no_test_outliers_females

confirmatory2B_testosterone_CBCL_female <- gamm4(cbcl_scr_syn_anxdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  PDS_score +
                                                   race.ethnicity.5level +
                                                   interview_age + bmi + household.income + high.educ +
                                                   demo_race_hispanic,
                                                 data = dataformodel,  
                                                 random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_female$gam)
```
### Male participants
```{r, echo=FALSE}

dataformodel <- data_no_test_outliers_males 

confirmatory2B_testosterone_CBCL_male <- gamm4(cbcl_scr_syn_anxdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  PDS_score +
                                                 race.ethnicity.5level +
                                                 interview_age + bmi + household.income + high.educ +
                                                 demo_race_hispanic,
                                               data = dataformodel,
                                               random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_male$gam)
```

## 1.16 Model: CBCL Anxious-Depressed ~ Testosterone + Pubertal category
### Female participants
```{r, echo=FALSE}
# PDS category.

#dataformodel <- subset(PDS_correct_females, hormone_scr_ert_mean_z > -3 & hormone_scr_ert_mean_z < 3 & pds_p_ss_category !="5")
dataformodel <- subset(PDS_correct_females, pds_p_ss_category !="5")

confirmatory2B_testosterone_CBCL_female_category <- gamm4(cbcl_scr_syn_anxdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  pds_p_ss_category +
                                                            race.ethnicity.5level +
                                                            interview_age + bmi + household.income + high.educ +
                                                            demo_race_hispanic,
                                                          data = dataformodel,  
                                                          random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_female_category$gam)
```
### Male participants
```{r, echo=FALSE}
# PDS category.

#dataformodel <- subset(PDS_correct_males, hormone_scr_ert_mean_z > -3 & hormone_scr_ert_mean_z < 3 & pds_p_ss_category !="5")
dataformodel <- subset(PDS_correct_males, pds_p_ss_category !="5")

confirmatory2B_testosterone_CBCL_male_category <- gamm4(cbcl_scr_syn_anxdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  pds_p_ss_category +
                                                          race.ethnicity.5level +
                                                          interview_age + bmi + household.income + high.educ +
                                                          demo_race_hispanic,
                                                        data = dataformodel,
                                                        random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_male_category$gam)
```
## 1.17 Model: CBCL Withdrawn-Depressed ~ Testosterone + PDS
### Female participants
```{r, echo=FALSE}

dataformodel <- data_no_test_outliers_females

confirmatory2B_testosterone_CBCL_female <- gamm4(cbcl_scr_syn_withdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  PDS_score +
                                                   race.ethnicity.5level +
                                                   interview_age + bmi + household.income + high.educ +
                                                   demo_race_hispanic,
                                                 data = dataformodel,  
                                                 random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_female$gam)
```
### Male participants
```{r, echo=FALSE}

dataformodel <- data_no_test_outliers_males 

confirmatory2B_testosterone_CBCL_male <- gamm4(cbcl_scr_syn_withdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  PDS_score +
                                                 race.ethnicity.5level +
                                                 interview_age + bmi + household.income + high.educ +
                                                 demo_race_hispanic,
                                               data = dataformodel,
                                               random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_male$gam)
```
## 1.18 Model: CBCL Withdrawn-Depressed ~ Testosterone + Pubertal category
### Female participants
```{r, echo=FALSE}
# PDS category.

#dataformodel <- subset(PDS_correct_females, hormone_scr_ert_mean_z > -3 & hormone_scr_ert_mean_z < 3 & pds_p_ss_category !="5")
dataformodel <- subset(PDS_correct_females, pds_p_ss_category !="5")

confirmatory2B_testosterone_CBCL_female_category <- gamm4(cbcl_scr_syn_withdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  pds_p_ss_category +
                                                            race.ethnicity.5level +
                                                            interview_age + bmi + household.income + high.educ +
                                                            demo_race_hispanic,
                                                          data = dataformodel,  
                                                          random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_female_category$gam)
```
### Male participants
```{r, echo=FALSE}
# PDS category.

#dataformodel <- subset(PDS_correct_males, hormone_scr_ert_mean_z > -3 & hormone_scr_ert_mean_z < 3 & pds_p_ss_category !="5")
dataformodel <- subset(PDS_correct_males, pds_p_ss_category !="5")

confirmatory2B_testosterone_CBCL_male_category <- gamm4(cbcl_scr_syn_withdep_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  pds_p_ss_category +
                                                          race.ethnicity.5level +
                                                          interview_age + bmi + household.income + high.educ +
                                                          demo_race_hispanic,
                                                        data = dataformodel,
                                                        random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_male_category$gam)
```
## 1.19 Model: CBCL Depressed DSM-5 ~ Testosterone + PDS 
### Female participants
```{r, echo=FALSE}

dataformodel <- data_no_test_outliers_females

confirmatory2B_testosterone_CBCL_female <- gamm4(cbcl_scr_dsm5_depress_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  PDS_score +
                                                   race.ethnicity.5level +
                                                   interview_age + bmi + household.income + high.educ +
                                                   demo_race_hispanic,
                                                 data = dataformodel,  
                                                 random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_female$gam)
```
### Male participants
```{r, echo=FALSE}

dataformodel <- data_no_test_outliers_males 


confirmatory2B_testosterone_CBCL_male <- gamm4(cbcl_scr_dsm5_depress_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  PDS_score +
                                                 race.ethnicity.5level +
                                                 interview_age + bmi + household.income + high.educ +
                                                 demo_race_hispanic,
                                               data = dataformodel,
                                               random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_male$gam)
```

## 1.20 Model: CBCL Depressed DSM-5 ~ Testosterone + Pubertal category 
### Female participants
```{r, echo=FALSE}
# PDS category.

#dataformodel <- subset(PDS_correct_females, hormone_scr_ert_mean_z > -3 & hormone_scr_ert_mean_z < 3 & pds_p_ss_category !="5")
dataformodel <- subset(PDS_correct_females, pds_p_ss_category !="5")

confirmatory2B_testosterone_CBCL_female_category <- gamm4(cbcl_scr_dsm5_depress_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  pds_p_ss_category +
                                                            race.ethnicity.5level +
                                                            interview_age + bmi + household.income + high.educ +
                                                            demo_race_hispanic,
                                                          data = dataformodel,  
                                                          random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_female_category$gam)
```
### Male participants
```{r, echo=FALSE}
# PDS category.

#dataformodel <- subset(PDS_correct_males, hormone_scr_ert_mean_z > -3 & hormone_scr_ert_mean_z < 3 & pds_p_ss_category !="5")
dataformodel <- subset(PDS_correct_males, pds_p_ss_category !="5")

confirmatory2B_testosterone_CBCL_male_category <- gamm4(cbcl_scr_dsm5_depress_r ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  pds_p_ss_category +
                                                          race.ethnicity.5level +
                                                          interview_age + bmi + household.income + high.educ +
                                                          demo_race_hispanic,
                                                        data = dataformodel,
                                                        random = ~ (1 | site_id_l/rel_family_id))

summary(confirmatory2B_testosterone_CBCL_male_category$gam)
```







# 2---Reward~Puberty---

## 2.11 Model: Caudate Anticipation ~ Testosterone
### Female participants
```{r, echo = FALSE}
dataformodel <- data_no_caudate_ant_no_test_outliers_females 

confirmatory1_caudate_females <- gamm4(caudate_rvsn_ant_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                       random = ~ (1 | site_id_l/rel_family_id),
                                       data = dataformodel)

summary(confirmatory1_caudate_females$gam)

```
### Male participants
```{r, echo = FALSE}
dataformodel <- data_no_caudate_ant_no_test_outliers_males

confirmatory1_caudate_males<- gamm4(caudate_rvsn_ant_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                    random = ~ (1 | site_id_l/rel_family_id),
                                    data = dataformodel)

summary(confirmatory1_caudate_males$gam)

```

## 2.12 Model B: Putamen Anticipation ~ Testosterone
### Female participants
```{r, echo = FALSE}
dataformodel <- data_no_putamen_ant_no_test_outliers_females 

confirmatory1_putamen_females <- gamm4(putamen_rvsn_ant_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                       random = ~ (1 | site_id_l/rel_family_id),
                                       data = dataformodel)

summary(confirmatory1_putamen_females$gam)

```
### Male participants
```{r, echo = FALSE}
dataformodel <- data_no_putamen_ant_no_test_outliers_males 

confirmatory1_putamen_males <- gamm4(putamen_rvsn_ant_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                     random = ~ (1 | site_id_l/rel_family_id),
                                     data = dataformodel)

summary(confirmatory1_putamen_males$gam)
```

## 2.13 Model: Accumbens Anticipation ~ Testosterone
### Female participants
```{r, echo = FALSE}
dataformodel <- data_no_accumbens_ant_no_test_outliers_females 

confirmatory1_accumbens_females <- gamm4(accumbens_rvsn_ant_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                         random = ~ (1 | site_id_l/rel_family_id),
                                         data = dataformodel)

summary(confirmatory1_accumbens_females$gam)
```
### Male participants
```{r, echo = FALSE}
dataformodel <- data_no_accumbens_ant_no_test_outliers_males 

confirmatory1_accumbens_males <- gamm4(accumbens_rvsn_ant_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                       random = ~ (1 | site_id_l/rel_family_id),
                                       data = dataformodel)

summary(confirmatory1_accumbens_males$gam)
```


## 2.14 Model: Caudate Feedback  ~ Testosterone
### Female participants
```{r, echo = FALSE}
dataformodel <- data_no_caudate_feed_no_test_outliers_females

exploratory1A_caudate_females <- gamm4(caudate_posvsneg_feedback_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                       random = ~ (1 | site_id_l/rel_family_id),
                                       data = dataformodel)

summary(exploratory1A_caudate_females$gam)
```
### Male participants
```{r, echo = FALSE}
dataformodel <- data_no_caudate_feed_no_test_outliers_males

exploratory1A_caudate_males <- gamm4(caudate_posvsneg_feedback_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                     random = ~ (1 | site_id_l/rel_family_id),
                                     data = dataformodel)

summary(exploratory1A_caudate_males$gam)

```
## 2.15 Model: Putamen Feedback ~ Testosterone
### Female participants
```{r, echo = FALSE}
dataformodel <- data_no_putamen_feed_no_test_outliers_females

exploratory1A_putamen_females <- gamm4(putamen_posvsneg_feedback_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                       random = ~ (1 | site_id_l/rel_family_id),
                                       data = dataformodel)

summary(exploratory1A_putamen_females$gam)
```
### Male participants
```{r, echo = FALSE}
dataformodel <- data_no_putamen_feed_outliers_no_test_males

exploratory1A_putamen_males <- gamm4(putamen_posvsneg_feedback_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                     random = ~ (1 | site_id_l/rel_family_id),
                                     data = dataformodel)

summary(exploratory1A_putamen_males$gam)
```
## 2.16 Model: Accumbens Feedback ~ Testosterone
### Female participants
```{r, echo = FALSE}
dataformodel <- data_no_accumbens_feed_no_test_outliers_females

exploratory1A_accumbens_females <- gamm4(accumbens_posvsneg_feedback_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                         random = ~ (1 | site_id_l/rel_family_id),
                                         data = dataformodel)

summary(exploratory1A_accumbens_females$gam)
```
### Male participants
```{r, echo = FALSE}
dataformodel <- data_no_accumbens_feed_no_test_outliers_males

exploratory1A_accumbens_males <- gamm4(accumbens_posvsneg_feedback_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                                       random = ~ (1 | site_id_l/rel_family_id),
                                       data = dataformodel)

summary(exploratory1A_accumbens_males$gam)

```



## 2.17 Model: OFC Anticipation ~ Testosterone
### Female participants
```{r, echo = FALSE}

# Female participants (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_ant_test_outliers_females
modelC_females_lOFC <- gamm4(lOFC_rvsn_ant_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                             random = ~ (1 | site_id_l/rel_family_id),
                             data = dataformodel)

summary(modelC_females_lOFC$gam)


# Female participants (medial OFC; mOFC).
dataformodel <- data_no_mOFC_ant_test_outliers_females
modelC_females_mOFC <- gamm4(mOFC_rvsn_ant_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                             random = ~ (1 | site_id_l/rel_family_id),
                             data = dataformodel)

summary(modelC_females_mOFC$gam)

```

### Male participants
```{r, echo=FALSE}
# Male participants (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_ant_test_outliers_males
modelC_males_lOFC <- gamm4(lOFC_rvsn_ant_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                           random = ~ (1 | site_id_l/rel_family_id),
                           data = dataformodel)

summary(modelC_males_lOFC$gam)


# Male participants (medial OFC; mOFC).
dataformodel <- data_no_mOFC_ant_test_outliers_males
modelC_males_mOFC <- gamm4(mOFC_rvsn_ant_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                           random = ~ (1 | site_id_l/rel_family_id),
                           data = dataformodel)

summary(modelC_males_mOFC$gam)
```

## 2.18 Model: OFC Feedback ~ Testosterone
### Female participants
```{r, echo = FALSE}

# Female participants (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_feed_test_outliers_females
modelD_females_lOFC <- gamm4(lOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                             random = ~ (1 | site_id_l/rel_family_id),
                             data = dataformodel)

summary(modelD_females_lOFC$gam)


# Female participants (medial OFC; mOFC).
dataformodel <- data_no_mOFC_feed_test_outliers_females
modelD_females_mOFC <- gamm4(mOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                             random = ~ (1 | site_id_l/rel_family_id),
                             data = dataformodel)

summary(modelD_females_mOFC$gam)
```

### Male participants
```{r, echo=FALSE}

# Male participants (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_feed_test_outliers_males
modelD_males_lOFC <- gamm4(lOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                           random = ~ (1 | site_id_l/rel_family_id),
                           data = dataformodel)

summary(modelD_males_lOFC$gam)


# Male participants (medial OFC; mOFC).
dataformodel <- data_no_mOFC_feed_test_outliers_males
modelD_males_mOFC <- gamm4(mOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + MRI_minus_hormone_date_time + bmi,
                           random = ~ (1 | site_id_l/rel_family_id),
                           data = dataformodel)

summary(modelD_males_mOFC$gam)
```

## 2.19 Model: MID Reaction Time ~ Testosterone
### Female participants
```{r, echo = FALSE}

# Female participants: large reward vs. neutral.
dataformodel <- data_no_RT_test_outliers_females # No MID RT difference score or testosterone outliers.
modelE_lg_neutral_RT_females <- gamm4(rt_diff_large_neutral_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + bmi,
                                      random = ~ (1 | site_id_l/rel_family_id),
                                      data = dataformodel)

summary(modelE_lg_neutral_RT_females$gam)

# Female participants: large reward vs. small reward.
dataformodel <- data_no_RT_test_outliers_females # No MID RT difference score or testosterone outliers.
modelE_lg_small_RT_females <- gamm4(rt_diff_large_small_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + bmi,
                                    random = ~ (1 | site_id_l/rel_family_id),
                                    data = dataformodel)

summary(modelE_lg_small_RT_females$gam)
```

### Male participants
```{r, echo=FALSE}
# Male participants: large reward vs. neutral.
dataformodel <- data_no_RT_test_outliers_males # No MID RT difference score or testosterone outliers.

modelE_lg_neutral_RT_males <- gamm4(rt_diff_large_neutral_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + bmi,
                                    random = ~ (1 | site_id_l/rel_family_id),
                                    data = dataformodel)

summary(modelE_lg_neutral_RT_males$gam)

# Male participants: large reward vs. small reward.
modelE_lg_small_RT_males <- gamm4(rt_diff_large_small_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + bmi,
                                  random = ~ (1 | site_id_l/rel_family_id),
                                  data = dataformodel)

summary(modelE_lg_small_RT_males$gam)
```

## 2.20 Model: BIS-BAS-RR ~ Testosterone
### Female participants
```{r, echo = FALSE}

dataformodel <- data_no_bisbas_test_outliers_females
modelF_females <- gamm4(bisbas_ss_basm_rr_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + bmi,
                        random = ~ (1 | site_id_l/rel_family_id),
                        data = dataformodel)

summary(modelF_females$gam)
```
### Male participants
```{r, echo=FALSE}
dataformodel <- data_no_bisbas_test_outliers_males
modelF_males <- gamm4(bisbas_ss_basm_rr_z ~ hormone_scr_ert_mean + hormone_sal_end_min_since_midnight +  interview_age + bmi,
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(modelF_males$gam)
```








# 4---Internalizing~Puberty x Reward---


## 4.14 Model: CBCL internalizing factor ~ Testosterone x Accumbens activity (anticipation stage) + PDS
### Female participants
```{r, echo = FALSE}

dataformodel <- data_no_accumbens_ant_no_test_outliers_females

confirmatory4Ea_accumbens_test_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                  PDS_score+
                                                  hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                  accumbens_rvsn_ant_z+
                                                  race.ethnicity.5level +
                                                  demo_race_hispanic +
                                                  interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                                data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4Ea_accumbens_test_females $gam)
#plot_model(confirmatory4_accumbens_ant_females,type = "int", show.data = TRUE) #Interaction plot
```
### Male participants
```{r, echo = FALSE}

dataformodel <- data_no_accumbens_ant_no_test_outliers_males

confirmatory4Ea_accumbens_test_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                PDS_score+
                                                hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                accumbens_rvsn_ant_z+
                                                race.ethnicity.5level +
                                                demo_race_hispanic +
                                                interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                              data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4Ea_accumbens_test_males $gam)
#plot_model(confirmatory4_accumbens_ant_females,type = "int", show.data = TRUE) #Interaction plot
```

## 4.15 Model: CBCL internalizing factor ~ Testosterone x Caudate activity (anticipation stage) + PDS
### Female participants
```{r, echo = FALSE}

dataformodel <- data_no_caudate_ant_no_test_outliers_females

confirmatory4Ea_caudate_test_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                PDS_score+
                                                hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                caudate_rvsn_ant_z+
                                                race.ethnicity.5level +
                                                demo_race_hispanic +
                                                #high.educ +
                                                #household.income +
                                                #married.or.livingtogether +
                                                interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                              data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4Ea_caudate_test_females $gam)
#plot_model(confirmatory4_accumbens_ant_females,type = "int", show.data = TRUE) #Interaction plot
```

### Male participants
```{r, echo = FALSE}

dataformodel <- data_no_caudate_ant_no_test_outliers_males

confirmatory4Ea_caudate_test_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                              PDS_score+
                                              hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                              caudate_rvsn_ant_z+
                                              race.ethnicity.5level +
                                              demo_race_hispanic +
                                              interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4Ea_caudate_test_males $gam)
```

## 4.16 Model: CBCL internalizing factor ~ Testosterone x Putamen activity (anticipation stage) + PDS
### Female participants
```{r, echo = FALSE}

dataformodel <- data_no_putamen_ant_no_test_outliers_females

confirmatory4Ea_putamen_test_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                PDS_score+
                                                hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                putamen_rvsn_ant_z+
                                                race.ethnicity.5level +
                                                demo_race_hispanic +
                                                interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                              data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4Ea_putamen_test_females $gam)
```

### Male participants
```{r, echo = FALSE}

dataformodel <- data_no_putamen_ant_no_test_outliers_males

confirmatory4Ea_putamen_test_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                              PDS_score+
                                              hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                              putamen_rvsn_ant_z+
                                              race.ethnicity.5level +
                                              demo_race_hispanic +
                                              interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4Ea_putamen_test_males $gam)
```


## 4.17 Model: CBCL internalizing factor ~ Testosterone x Accumbens activity (feedback stage) + PDS
### Female participants
```{r, echo = FALSE}

dataformodel <- data_no_accumbens_feed_no_test_outliers_females

exploratory4Eb_accumbens_test_feed_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                      PDS_score+
                                                      hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                      accumbens_posvsneg_feedback_z+
                                                      race.ethnicity.5level +
                                                      demo_race_hispanic +
                                                      interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                                    data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4Eb_accumbens_test_feed_females$gam)

```
### Male participants
```{r, echo = FALSE}

dataformodel <- data_no_accumbens_feed_no_test_outliers_males

exploratory4Eb_accumbens_test_feed_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                    PDS_score+
                                                    hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                    accumbens_posvsneg_feedback_z+
                                                    race.ethnicity.5level +
                                                    demo_race_hispanic +
                                                    interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                                  data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4Eb_accumbens_test_feed_males$gam)
```

## 4.18 Model: CBCL internalizing factor ~ Testosterone x Caudate activity (Feedback stage) + PDS
### Female participants
```{r, echo = FALSE}
dataformodel <- data_no_caudate_feed_no_test_outliers_females

confirmatory4Eb_caudate_test_feed_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                     PDS_score+
                                                     hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                     caudate_posvsneg_feedback_z+
                                                     race.ethnicity.5level +
                                                     demo_race_hispanic +
                                                     interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                                   data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4Eb_caudate_test_feed_females$gam)
```

### Male participants
```{r, echo = FALSE}

dataformodel <- data_no_caudate_feed_no_test_outliers_males

confirmatory4Eb_caudate_test_feed_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                   PDS_score+
                                                   hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                   caudate_posvsneg_feedback_z+
                                                   race.ethnicity.5level +
                                                   demo_race_hispanic +
                                                   interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                                 data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4Eb_caudate_test_feed_males$gam)
```

## 4.19 Model: CBCL internalizing factor ~ Testosterone x Putamen activity (Feedback stage) + PDS
### Female participants
```{r, echo = FALSE}
dataformodel <- data_no_putamen_feed_no_test_outliers_females

confirmatory4Eb_putamen_test_feed_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                     PDS_score+
                                                     hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                     putamen_posvsneg_feedback_z+
                                                     race.ethnicity.5level +
                                                     demo_race_hispanic +
                                                     interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                                   data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4Eb_putamen_test_feed_females$gam)

```

### Male participants
```{r, echo = FALSE}

dataformodel <- data_no_putamen_feed_outliers_no_test_males

confirmatory4Eb_putamen_test_feed_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                   PDS_score+
                                                   hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                   putamen_posvsneg_feedback_z+
                                                   race.ethnicity.5level +
                                                   demo_race_hispanic +
                                                   interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ,
                                                 data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4Eb_putamen_test_feed_males$gam)
```

## 4.20 Model: CBCL internalizing factor ~ Testosterone x Lateral OFC activity (anticipation stage) + PDS
### Female participants
```{r, echo=FALSE}
#Lateral OFC

dataformodel <- data_no_lOFC_ant_test_outliers_females 

exploratory4c_OFC_ant_allCBCL_test_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                      PDS_score+
                                                      hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                      lOFC_rvsn_ant_z+
                                                      race.ethnicity.5level +
                                                      demo_race_hispanic +
                                                      interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4c_OFC_ant_allCBCL_test_females$gam )
```

### Male participants
```{r, echo=FALSE}
#Lateral OFC
dataformodel <- data_no_lOFC_ant_test_outliers_males 

exploratory4c_OFC_ant_allCBCL_test_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                    PDS_score+
                                                    hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                    lOFC_rvsn_ant_z+
                                                    race.ethnicity.5level +
                                                    demo_race_hispanic +
                                                    interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4c_OFC_ant_allCBCL_test_males$gam )
```


## 4.21 Model: CBCL internalizing factor ~ Testosterone x Medial OFC activity (anticipation stage) + PDS
### Female participants
```{r, echo=FALSE}
#Medial OFC
dataformodel <- data_no_mOFC_ant_test_outliers_females 

exploratory4c_mOFC_ant_allCBCL_test_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                       PDS_score+
                                                       hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                       mOFC_rvsn_ant_z+
                                                       race.ethnicity.5level +
                                                       demo_race_hispanic +
                                                       interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4c_mOFC_ant_allCBCL_test_females$gam )
```

### Male participants
```{r, echo=FALSE}
#Medial OFC
dataformodel <- data_no_mOFC_ant_test_outliers_males 

exploratory4c_mOFC_ant_allCBCL_test_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                     PDS_score+
                                                     hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*  
                                                     mOFC_rvsn_ant_z+
                                                     race.ethnicity.5level +
                                                     demo_race_hispanic +
                                                     interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4c_mOFC_ant_allCBCL_test_males$gam )
```

## 4.22 Model: CBCL internalizing factor ~ Testosterone x Lateral OFC activity (feedback stage) + PDS
### Female participants
```{r, echo = FALSE}
#Lateral OFC feedback

dataformodel <- data_no_lOFC_feed_test_outliers_females 

exploratory4d_OFC_feed_allCBCL_test_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                       PDS_score+
                                                       hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean* 
                                                       lOFC_posvsneg_feedback_z+
                                                       race.ethnicity.5level +
                                                       demo_race_hispanic +
                                                       interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4d_OFC_feed_allCBCL_test_females$gam )
```

### Male participants
```{r, echo = FALSE}
#Lateral OFC feedback

dataformodel <- data_no_lOFC_feed_test_outliers_males 

exploratory4d_OFC_feed_allCBCL_test_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                     PDS_score+
                                                     hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean* 
                                                     lOFC_posvsneg_feedback_z+
                                                     race.ethnicity.5level +
                                                     demo_race_hispanic +
                                                     interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4d_OFC_feed_allCBCL_test_males$gam )
```

## 4.23 Model: CBCL internalizing factor ~ Testosterone x Medial OFC activity (feedback stage) + PDS
### Female participants
```{r, echo=FALSE}
#Medial OFC feedback

dataformodel <- data_no_mOFC_feed_test_outliers_females 

exploratory4d_mOFC_feed_allCBCL_test_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                        PDS_score+
                                                        hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean* 
                                                        mOFC_posvsneg_feedback_z+
                                                        race.ethnicity.5level +
                                                        demo_race_hispanic +
                                                        interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4d_mOFC_feed_allCBCL_test_females$gam )
```

### Male participants
```{r, echo=FALSE}
#Medial OFC feedback

dataformodel <- data_no_mOFC_feed_test_outliers_males 

exploratory4d_mOFC_feed_allCBCL_test_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                      PDS_score+
                                                      hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean* 
                                                      mOFC_posvsneg_feedback_z+
                                                      race.ethnicity.5level +
                                                      demo_race_hispanic +
                                                      interview_age + MRI_minus_hormone_date_time + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4d_mOFC_feed_allCBCL_test_males$gam )

```


## 4.24 Model: CBCL internalizing factor ~ Testosterone x BIS-BAS RR + PDS
### Female participants
```{r, echo = FALSE}

dataformodel <- data_no_bisbas_test_outliers_females 

exploratory4e_bisbas_allCBCL_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                                PDS_score+
                                                hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*
                                                bisbas_ss_basm_rr+
                                                race.ethnicity.5level +
                                                demo_race_hispanic +
                                                interview_age + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4e_bisbas_allCBCL_females$gam )
```

### Male participants
```{r, echo = FALSE}

dataformodel <- data_no_bisbas_test_outliers_males 

exploratory4e_bisbas_allCBCL_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                              PDS_score+
                                              hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*
                                              bisbas_ss_basm_rr+
                                              race.ethnicity.5level +
                                              demo_race_hispanic +
                                              interview_age + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4e_bisbas_allCBCL_males$gam )
```


## 4.25 Model: CBCL internalizing factor ~ Testosterone x MID Reaction Time + PDS (large reward vs. neutral) 
### Female participants 
```{r, echo = FALSE}

dataformodel <- data_no_RT_test_outliers_females

#Large reward vs. neutral.
exploratoryFa_lg_neutral_RT_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                               PDS_score+
                                               hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*
                                               rt_diff_large_neutral_z+
                                               race.ethnicity.5level +
                                               demo_race_hispanic +
                                               interview_age + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratoryFa_lg_neutral_RT_females$gam)
```
### Male participants 
```{r, echo = FALSE}
dataformodel <- data_no_RT_test_outliers_males

#Large reward vs. neutral.
exploratoryFa_lg_neutral_RT_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                             PDS_score+
                                             hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*
                                             rt_diff_large_neutral_z+
                                             race.ethnicity.5level +
                                             demo_race_hispanic +
                                             interview_age + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratoryFa_lg_neutral_RT_males$gam)
```


## 4.26 Model: CBCL internalizing factor ~ Testosterone x MID Reaction Time + PDS (large vs. small reward)
### Female participants 
```{r, echo = FALSE}
#Large reward vs. small reward positive.
dataformodel <- data_no_RT_test_outliers_females

exploratoryFb_lg_small_RT_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                                             PDS_score+
                                             hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*
                                             rt_diff_large_small_z+
                                             race.ethnicity.5level +
                                             demo_race_hispanic +
                                             interview_age + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratoryFb_lg_small_RT_females$gam)
```

### Male participants
```{r, echo = FALSE}
#Large reward vs. small reward positive.

dataformodel <- data_no_RT_test_outliers_males

exploratoryFb_lg_small_RT_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                                           PDS_score+
                                           hormone_sal_end_min_since_midnight +  hormone_scr_ert_mean*
                                           rt_diff_large_small_z+
                                           race.ethnicity.5level +
                                           demo_race_hispanic +
                                           interview_age + bmi + household.income + high.educ, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratoryFb_lg_small_RT_males$gam)
```