---
title: "Research Question 4: Do neural and self-reported responses to reward moderate the relationship between pubertal development and internalizing symptoms?"
date: "August 2020"
output:
  html_document: default
  pdf_document: default
authors: Natalie Saragosa-Harris 
---
``` {r loadPackages, echo = FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(gamm4)
library(dplyr)
library(sjPlot)
library(here)
library(jtools)
library(interactions)
library(gamm4.test)
library(ggstatsplot)
```

```{r LoadData, echo = FALSE}

# Elizabeth.
# Data: Desktop⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code: Desktop⁩ ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code⁩

# Lucia.
# Data:  Github⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Github ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# Natalie.
# Data:  Desktop ▸ ABCD⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Desktop ▸ ABCD ⁩▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# LMW alternative to read in the data.

data_dir = ((dirname(here()))) 

phase_folder = "exploratory"  # select the appropiate folder.
#phase_folder = "confirmatory"  # select the appropiate folder.

data_folder <- file.path(data_dir,"ABCD","derivatives",phase_folder)

file_name <- "nda30_exploratory.csv" # specify file name here. 

fulldata <- read.csv(file.path(data_folder,file_name))
length(fulldata$src_subject_id) # 5934.

# Call function to define all of the dataframes.
script_path <- file.path(data_dir,"rewardprocesses_internalizing_puberty_exploratory","code","define_dataframes.R")
source(script_path)
```

#Basic data checks and transformations
```{r Data check and transformations, echo = FALSE}
# Use combined score for accumbens, caudate, and putamen?
# Jen: I would probably run the 3 separately and control for multiple comparisons. If the three give you highly correlated results you could take a composite measure for subsequent analyses.
cor.test(data$accumbens_rvsn_ant_z,data$caudate_rvsn_ant_z) # Exp 0.57.
cor.test(data$accumbens_rvsn_ant_z,data$putamen_rvsn_ant_z) # Exp 0.53.
cor.test(data$caudate_rvsn_ant_z,data$putamen_rvsn_ant_z) # Exp 0.81. 

#Explore outliers
boxplot(data$accumbens_rvsn_ant_z)
boxplot(data$caudate_rvsn_ant_z)
boxplot(data$putamen_rvsn_ant_z)
boxplot(data$cbcl_scr_syn_internal_r)
```
#Count NAs per variable 
```{r Count NAs}
#Count NAs per variable 
# We are missing many cases of maternal depression - consider dropping
dataformodel <- data_no_CBCL_outliers 
nrow(data_no_CBCL_outliers)
nrow(PDS_correct)
dataformodel <- PDS_correct

sum(is.na(dataformodel$src_subject_id)) #0 missing  
sum(is.na(dataformodel$sex))  #0 missing   
sum(is.na(dataformodel$mri_info_deviceserialnumber)) #0 missing 
sum(is.na(dataformodel$rel_family_id)) #0 missing 
sum(is.na(dataformodel$race.ethnicity.5level)) #41
sum(is.na(dataformodel$demo_race_hispanic))  #50
sum(is.na(dataformodel$high.educ))  #3
sum(is.na(dataformodel$household.income)) #293
sum(is.na(dataformodel$married.or.livingtogether))  #22
sum(is.na(dataformodel$fam_history_q6d_depression)) #1937 missing!

summary(dataformodel)

#Also, some brain variables seem to have large outliers. Check before including in the models 
```

#Exploring PDS outliers
```{r Exploring PDS outliers}
d <- density(PDS_correct_females$PDS_score) # returns the density data
plot(d) # plots the results

p2 <- ggplot(data=PDS_correct, aes(x=PDS_score, group=sex, fill=sex)) +
    geom_density(adjust=1.5, alpha=.4) 
p2

summary(PDS_correct$PDS_score)
boxplot(PDS_correct$PDS_score,spread_text = F)

ggbetweenstats(data = PDS_correct, 
               x = sex,
               y = PDS_score, 
               outlier.coef = 3.0,
               outlier.tagging = TRUE,
               outlier.label = src_subject_id)
```


# Confirmatory Hypothesis 4: We predict that striatal responses to reward will moderate the effect of pubertal stage such that the relationship between advanced pubertal status and internalizing symptoms will be stronger among participants with attenuated activation in striatal reward circuitry during reward anticipation.

##  Model: CBCL internalizing factor ~ PDS*Striatal activity (anticipation stage)
```{r Confirmatory4, both sexes, echo = FALSE}
# Composite striatum score, exlcuding outliers.
# No CBCL exclusions
# With covariates

dataformodel <- data_no_striatal_ant_outliers  #Specify data subset here

confirmatory4_compositestriatum <- gamm4(cbcl_scr_syn_internal_r ~ 
                            interview_age+
                            PDS_score_z+
                            striatum_rvsn_ant_z+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether 
                            , data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4_compositestriatum$gam)

plot_model(confirmatory4_compositestriatum,type = "pred", show.data = TRUE) #Interaction plot

plot_model(confirmatory4_compositestriatum,type = "est", show.data = TRUE) #Forest plot

#p <- plot_model(confirmatory4_compositestriatum,type = "int", terms = "PDS_score",            show.data = TRUE, jitter = 0.1, line.size = 2) +

#file.name = (here("output","question4_exploratory.tiff"))
#ggsave(file.name,plot = last_plot(), dpi = 150, device = "tiff")

#p <- ggplot( data = subset(PDS_correct, striatum_rvsn_ant_z > -3 & striatum_rvsn_ant_z < 3), aes(x=sex, y=striatum_rvsn_ant_z)) + 
#  geom_boxplot()
#p
```

## Core model (no covariates)
```{r Confirmatory4_coremodel_nocovariates}
# Core model (no covariates)
# Composite striatum score.
# Excluding CBCL outliers 
# Without covariates

dataformodel <- data_no_CBCL_striatal_ant_outliers

#Select only cases that have complete data for all covariates of intest. It seems that we are missing many cases of maternal depression. We might drop it going forwards. 
tempdata <- dataformodel[which(complete.cases(dataformodel[,c("race.ethnicity.5level",
                            "demo_race_hispanic",
                            "high.educ",
                            "household.income",
                            "married.or.livingtogether",
                            "interview_age"
                            )])),]
nrow(dataformodel)
nrow(tempdata)

confirmatory4_compositestriatum_excludingoutliers_core <- gamm4(cbcl_scr_syn_internal_r ~
                                           PDS_score*striatum_rvsn_ant_z+
                                           sex,
                                           data = tempdata,random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4_compositestriatum_excludingoutliers_core)

print.gamtest(confirmatory4_compositestriatum_excludingoutliers_core,2)

plot_model(confirmatory4_compositestriatum_excludingoutliers_core,type = "int", show.data = FALSE, show.p = TRUE) #Interaction plot

plot_model(confirmatory4_compositestriatum_excludingoutliers_core,type = "std", show.data = FALSE) #Forest plot

# p <- plot_model(confirmatory4_compositestriatum_excludingoutliers_core,
#                 type = "pred", # To specify values for striatal response, have to use "pred" instead.
#                 terms = c("PDS_score","striatum_rvsn_ant_z [-2.0,0,2.0]"),
#                 show.data = TRUE, jitter = 0.1, line.size = 2) +
#                 ylab("Internalizing Score") +
#                 xlab("Average PDS score") +
#                 labs(colour = "MID Striatal activity z-score \n (reward anticipation vs neutral)")+
#                 scale_y_continuous(breaks = seq(0, 45, by = 10), limits = c(0,45)) +
#                 theme(title= element_text(size=20, vjust=2, face="bold"),
#                 plot.title = element_blank(),
#                 axis.title.x= element_text(size=18, vjust=-0.3),
#                 axis.title.y= element_text(size=18, vjust=1.5),
#                 axis.text.x= element_text(size=18, colour="black"),
#                 axis.text.y= element_text(size=18, colour="black"),
#                 legend.title=element_text(size=12, colour = "black"),
#                 legend.position = c(.80, .80),
#                 # legend.position="none",
#                 strip.text = element_text(size=18, face="bold"),
#                 panel.background = element_blank(),
#                 axis.line = element_line(colour = "black"))
# p 
```

## Core model (no covariates) females, no interaction
```{r Confirmatory4_coremodel_nocovariates}
# Core model (no covariates)
# Composite striatum score.
# Excluding CBCL outliers 
# Without covariates

dataformodel <- PDS_correct_females

#Select only cases that have complete data for all covariates of intest. It seems that we are missing many cases of maternal depression. We might drop it going forwards. 
tempdata <- dataformodel[which(complete.cases(dataformodel[,c("race.ethnicity.5level",
                            "demo_race_hispanic",
                            "high.educ",
                            "household.income",
                            "married.or.livingtogether",
                            "interview_age"
                            )])),]
nrow(dataformodel)
nrow(tempdata)

female_CBCL_PDS_core <- lmer(cbcl_scr_syn_internal_r ~
                                           PDS_score+
                                           interview_age+
                                           (1 | site_id_l/rel_family_id), data = tempdata)
summary(female_CBCL_PDS_core)



female_CBCL_PDS_covariates <-  lmer(cbcl_scr_syn_internal_r ~ 
                            PDS_score+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age+(1 | site_id_l/rel_family_id), data = tempdata)

summary(female_CBCL_PDS_covariates)

anova(female_CBCL_PDS_core,female_CBCL_PDS_covariates)
```

## Core model (no covariates) males, no interaction
```{r Confirmatory4_coremodel_nocovariates}
# Core model (no covariates)
# Composite striatum score.
# Excluding CBCL outliers 
# Without covariates

dataformodel <- PDS_correct_males

#Select only cases that have complete data for all covariates of intest. It seems that we are missing many cases of maternal depression. We might drop it going forwards. 
tempdata <- dataformodel[which(complete.cases(dataformodel[,c("race.ethnicity.5level",
                            "demo_race_hispanic",
                            "high.educ",
                            "household.income",
                            "married.or.livingtogether",
                            "interview_age"
                            )])),]
nrow(dataformodel)
nrow(tempdata)

male_CBCL_PDS_core <- lmer(cbcl_scr_syn_internal_r ~
                                           PDS_score+
                                           interview_age+
                                           (1 | site_id_l/rel_family_id), data = tempdata)
summary(male_CBCL_PDS_core)



male_CBCL_PDS_covariates <-  lmer(cbcl_scr_syn_internal_r ~ 
                            PDS_score+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age+(1 | site_id_l/rel_family_id), data = tempdata)

summary(male_CBCL_PDS_covariates)

anova(male_CBCL_PDS_core,male_CBCL_PDS_covariates)
```



```{r}
#Excluding outliers in CBCL 
#Reveals main effect of striatum as well as interaction, but in the opposite way?

dataformodel<- data_no_CBCL_striatal_ant_outliers_males
dataformodel<-data_no_CBCL_striatal_ant_outliers_females_pubertal

#Select only cases that have complete data for all covariates of intest. It seems that we are missing many cases of maternal depression. We might drop it going forwards. 
tempdata <- dataformodel[which(complete.cases(dataformodel[,c("race.ethnicity.5level",
                            "demo_race_hispanic",
                            "high.educ",
                            "household.income",
                            "married.or.livingtogether",
                            "interview_age"
                            )])),]

confirmatory4_compositestriatum_excludingoutliers <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z+
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

confirmatory4_compositestriatum_excludingoutliers <- lme4::lmer(cbcl_scr_syn_internal_r ~ 
                            pds_p_ss_category*
                            striatum_rvsn_ant_z+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age+
                          #  fam_history_q6d_depression + #added mother's depression
                            (1 | site_id_l/rel_family_id),  #same thing as site is the same thing as (1|site) + (1|family:site), this is what done in paper by Paulus et al. (2019), 22 sites 
#data = subset(PDS_correct, striatum_rvsn_ant_z > -3 & striatum_rvsn_ant_z < 3 & cbcl_scr_syn_internal_r_z > -3 & cbcl_scr_syn_internal_r_z < 3))
data = tempdata)
summary(confirmatory4_compositestriatum_excludingoutliers)


mod <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z^2+
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

plot_model(mod$mer,type = "est", show.data = FALSE, show.p = TRUE) #Interaction plot


print(mod$gam)
print(summary(mod))

summary(mod$gam)

vis.gam(mod$gam)

summary(confirmatory4_compositestriatum_excludingoutliers)
gam.grptest(confirmatory4_compositestriatum_excludingoutliers)

```

```{r}
#Quick plots
plot_model(confirmatory4_compositestriatum_excludingoutliers,type = "int", show.data = FALSE) #Interaction plot

plot_model(confirmatory4_compositestriatum_excludingoutliers,type = "std", show.data = FALSE) #Forest plot with standarized coefficients
```
## Compare model with and without covariates
```{r Compare model with and without covariates}
#Compare model with and without covariates - adding covariates makes the model significantly improve
anova(confirmatory4_compositestriatum_excludingoutliers_core,confirmatory4_compositestriatum_excludingoutliers)
```
## Publication plot
```{r}
#Publication plot
#Both sexes

p <- plot_model(confirmatory4_compositestriatum_excludingoutliers,
                type = "pred", # To specify values for striatal response, have to use "pred" instead.
                terms = c("PDS_score","striatum_rvsn_ant_z [-2.0,0,2.0]"),
                show.data = TRUE, jitter = 0.1, line.size = 2) +
                ylab("Internalizing Score") +
                xlab("Average PDS score") +
                labs(colour = "MID Striatal activity z-score \n (reward anticipation vs neutral)")+
                scale_y_continuous(breaks = seq(0, 45, by = 10), limits = c(0,45)) +
                theme(title= element_text(size=20, vjust=2, face="bold"),
                plot.title = element_blank(),
                axis.title.x= element_text(size=18, vjust=-0.3),
                axis.title.y= element_text(size=18, vjust=1.5),
                axis.text.x= element_text(size=18, colour="black"),
                axis.text.y= element_text(size=18, colour="black"),
                legend.title=element_text(size=12, colour = "black"),
                legend.position = c(.80, .80),
                # legend.position="none",
                strip.text = element_text(size=18, face="bold"),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"))
p 
                 
file.name = (here("output","question4_exploratory_excludingCBCLoutliers.tiff"))
#ggsave(file.name,plot = last_plot(), dpi = 150, device = "tiff")
```


### Females, excl outliers in CBCL, striatal anticipation
```{r}
# Excluding outliers in CBCL 
# Splitting by sex
# FEMALES

dataformodel <- data_no_CBCL_striatal_ant_outliers_females

confirmatory4_compositestriatum_excludingoutliersCBCL_femalesonly <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(PDS_correct_females$interview_age)
anova(confirmatory4_compositestriatum_excludingoutliersCBCL_femalesonly)$lme
```

### Females, all CBCL values, striatal anticipation
```{r}
# Not excluding outliers in CBCL 
# Splitting by sex
# FEMALES

dataformodel <- data_no_striatal_ant_outliers_females

confirmatory4_compositestriatum_allCBCL_femalesonly <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(confirmatory4_compositestriatum_allCBCL_femalesonly$gam)
```
```{r}
#Quick plots
plot_model(confirmatory4_compositestriatum_excludingoutliers_femalesonly,type = "pred", terms = c("PDS_score","striatum_rvsn_ant_z [-2.0,0,2.0]"),show.data = FALSE) #Interaction plot

plot_model(confirmatory4_compositestriatum_excludingoutliers_femalesonly, type= "std",how.data = FALSE) #Forest plot with standardized coefficients
```

### Males, excluding CBCL values, striatal anticipation
```{r}
# Excluding outliers in CBCL 
# Splitting by sex
# MALES

dataformodel <- data_no_CBCL_striatal_ant_outliers_males

confirmatory4_compositestriatum_excludingoutliersCBCL_malesonly<- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(confirmatory4_compositestriatum_excludingoutliersCBCL_malesonly$gam)
```

### Males, all CBCL values, striatal anticipation
```{r}
# Excluding outliers in CBCL 
# Splitting by sex
# MALES

dataformodel <- data_no_striatal_ant_outliers_males

confirmatory4_compositestriatum_allCBCL_malesonly <- 
  gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4_compositestriatum_allCBCL_malesonly$gam)
```


```{r}
#Quick plots
plot_model(confirmatory4_compositestriatum_excludingoutliers_malesonly,type = "pred", terms = c("PDS_score","striatum_rvsn_ant_z [-2.0,0,2.0]"),show.data = FALSE) #Interaction plot

plot_model(confirmatory4_compositestriatum_excludingoutliers_malesonly,type = "std", show.data = FALSE) #Forest plot with standarized coefficients
```

```{r}
#Excluding outliers in CBCL 
#PDS category 

confirmatory4_compositestriatum_excludingoutliers_cat <- lmer(cbcl_scr_syn_internal_r ~                                       pds_p_ss_category*striatum_rvsn_ant_z +
                            race.eth.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age+
                            fam_history_q6d_depression + #added mother's depression
                            (1 | site_id_l/rel_family_id),
                            data = subset(PDS_correct, 
                                          striatum_rvsn_ant_z > -3 & striatum_rvsn_ant_z < 3 & cbcl_scr_syn_internal_r_z > -3 & cbcl_scr_syn_internal_r_z < 3))

summary(confirmatory4_compositestriatum_excludingoutliers_cat)

plot_model(confirmatory4_compositestriatum_excludingoutliers_cat,type = "int", show.data = FALSE) #Interaction plot

plot_model(confirmatory4_compositestriatum_excludingoutliers,type = "est", show.data = FALSE) #Forest plot

p <- plot_model(confirmatory4_compositestriatum_excludingoutliers_cat,
                type = "pred", # To specify values for striatal response, have to use "pred" instead.
                terms = c("pds_p_ss_category","striatum_rvsn_ant_z [-2.0,0,2.0]"),
                show.data = TRUE, jitter = 0.1, line.size = 2) +
                ylab("Internalizing Score") +
                xlab("PDS category") +
                labs(colour = "MID Striatal activity z-score \n (reward anticipation vs neutral)")+
                scale_y_continuous(breaks = seq(0, 45, by = 10), limits = c(0,45)) +
                theme(title= element_text(size=20, vjust=2, face="bold"),
                plot.title = element_blank(),
                axis.title.x= element_text(size=18, vjust=-0.3),
                axis.title.y= element_text(size=18, vjust=1.5),
                axis.text.x= element_text(size=18, colour="black"),
                axis.text.y= element_text(size=18, colour="black"),
                legend.title=element_text(size=12, colour = "black"),
                legend.position = c(.80, .80),
                # legend.position="none",
                strip.text = element_text(size=18, face="bold"),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"))
p 
                   
file.name = (here("output","question4_exploratory_excludingCBCLoutliers_PDScat.tiff"))
#ggsave(file.name,plot = last_plot(), dpi = 150, device = "tiff")
```



# Exploratory Hypothesis 4A: We will investigate whether striatal responses to reward during reward feedback moderates the effect of pubertal stage on internalizing symptoms. 
## Model: CBCL internalizing factor ~ PDS*Striatal activity (feedback stage) Females


## Females, excluding outliers CBCL, striatal feedback
```{r Exploratory4A, echo = FALSE}
#Composite striatum score, FEMALES

dataformodel <- data_no_CBCL_striatal_feed_outliers_females

exploratory4a_compositestriatum_feedback_excludingoutliers_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            striatum_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4a_compositestriatum_feedback_excludingoutliers_females$gam )
```

## Females, all CBCL, striatal feedback
```{r Exploratory4A, echo = FALSE}
#Composite striatum score, FEMALES

dataformodel <- data_no_striatal_feed_outliers_females

exploratory4a_compositestriatum_feedback_allCBCL_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            striatum_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4a_compositestriatum_feedback_allCBCL_females$gam )
```
## Model: CBCL internalizing factor ~ PDS*Striatal activity (feedback stage) Males
```{r Exploratory4A, echo = FALSE}
#Composite striatum score, MALES

dataformodel <- data_no_CBCL_striatal_feed_outliers_males

exploratory4a_compositestriatum_feedback_excludingoutliers_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            striatum_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4a_compositestriatum_feedback_excludingoutliers_males$gam )
```

## Males, all CBCL, striatal feedback
```{r Exploratory4A, echo = FALSE}
#Composite striatum score, FEMALES

dataformodel <- data_no_striatal_feed_outliers_males

exploratory4a_compositestriatum_feedback_allCBCL_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            striatum_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4a_compositestriatum_feedback_allCBCL_males$gam )
```

```{r}
#Quick plots
plot_model(exploratory4a_compositestriatum_feedback_allCBCL_males,type = "pred", terms = c("PDS_score_z","striatum_posvsneg_feedback_z [-2.0,0,2.0]"),show.data = FALSE) #Interaction plot

#plot_model(exploratory4a_compositestriatum_feedback_allCBCL_males$mer,type = "std", show.data = FALSE) #Not working
```

# Exploratory Hypothesis 4B: We will investigate whether OFC activation during reward anticipation and feedback moderates the relationship between pubertal stage and internalizing symptoms.
## Model A: CBCL internalizing factor ~ PDS*OFC activity (anticipation stage)
## Model B: CBCL internalizing factor ~ PDS*OFC activity (feedback stage)


## Females, excl CBCL, lOFC anticipation
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, FEMALES

dataformodel <- data_no_CBCL_lOFC_ant_outliers_females

exploratory4b_OFC_ant_excludingoutliers_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_ant_excludingoutliers_females$gam )
```
## Females, all CBCL, lOFC anticipation
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, FEMALES

dataformodel <- data_no_lOFC_ant_outliers_females

exploratory4b_OFC_ant_allCBCL_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_ant_allCBCL_females$gam )
```



# Exploratory Hypothesis 4B: We will investigate whether OFC activation during reward anticipation and feedback moderates the relationship between pubertal stage and internalizing symptoms.
## Model A: CBCL internalizing factor ~ PDS*OFC activity (anticipation stage) MALES

## Males, excl CBCL, lOFC anticipation
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, FEMALES

dataformodel <- data_no_CBCL_lOFC_ant_outliers_males

exploratory4b_OFC_ant_excludingoutliers_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_ant_excludingoutliers_males$gam )
```



## Males, all CBCL, lOFC anticipation
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, FEMALES

dataformodel <- data_no_lOFC_ant_outliers_males

exploratory4b_OFC_ant_allCBCL_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_ant_allCBCL_males$gam )
```



# Exploratory Hypothesis 4B: We will investigate whether OFC activation during reward anticipation and feedback moderates the relationship between pubertal stage and internalizing symptoms.
## Model A: CBCL internalizing factor ~ PDS*OFC activity (feedback stage) FEMALES

## Females, excl CBCL, lOFC feedback
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, MALES

dataformodel <- data_no_CBCL_lOFC_feed_outliers_females

exploratory4b_OFC_feed_excludingoutliers_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_feed_excludingoutliers_females$gam )
```
## Females, all CBCL, lOFC feedback
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, MALES

dataformodel <- data_no_lOFC_feed_outliers_females

exploratory4b_OFC_feed_allCBCL_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_feed_allCBCL_females$gam )
```

# Exploratory Hypothesis 4B: We will investigate whether OFC activation during reward anticipation and feedback moderates the relationship between pubertal stage and internalizing symptoms.
## Model A: CBCL internalizing factor ~ PDS*OFC activity (feedback stage) MALES

## Males, excl CBCL, lOFC feedback
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, MALES

dataformodel <- data_no_CBCL_lOFC_feed_outliers_males

exploratory4b_OFC_feed_excludingoutliers_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_feed_excludingoutliers_males$gam )
```
## Males, all CBCL, lOFC feedback
```{r Exploratory4B, echo = FALSE}
#OFC anticipation, MALES

dataformodel <- data_no_lOFC_feed_outliers_males

exploratory4b_OFC_feed_allCBCL_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            lOFC_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4b_OFC_feed_allCBCL_males$gam )
```


# Exploratory Hypothesis 4C: We hypothesize that the association between advanced puberty and internalizing symptoms will be moderated by self-reported reward responsiveness. We predict that advanced puberty will be associated with higher internalizing in individuals who report lower reward responsiveness on the BIS-BAS questionnaire.

## Model: CBCL internalizing factor ~ PDS*BIS-BAS

## Females, excl CBCL, BIS/BAS
```{r Exploratory4C, echo = FALSE}
#FEMALES
dataformodel <- data_no_CBCL_outliers_females

exploratory4c_bisbas_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            bisbas_ss_basm_rr+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4c_bisbas_females$gam )
```
## Females, all CBCL, BIS/BAS
```{r Exploratory4C, echo = FALSE}
#FEMALES
dataformodel <- PDS_correct_females

exploratory4c_bisbas_allCBCL_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            bisbas_ss_basm_rr+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4c_bisbas_allCBCL_females$gam )
```

```{r}
#Quick plots
plot_model(exploratory4c_bisbas_allCBCL_females$gam,type = "pred", terms = c("PDS_score_z","bisbas_ss_basm_rr [-2.0,0,2.0]"),show.data = FALSE) #Interaction plot

#plot_model(exploratory4a_compositestriatum_feedback_allCBCL_males$mer,type = "std", show.data = FALSE) #Not working
```





# Exploratory Hypothesis 4C: We hypothesize that the association between advanced puberty and internalizing symptoms will be moderated by self-reported reward responsiveness. We predict that advanced puberty will be associated with higher internalizing in individuals who report lower reward responsiveness on the BIS-BAS questionnaire.
## Model: CBCL internalizing factor ~ PDS*BIS-BAS

## Males, excl CBCL, BIS/BAS
```{r Exploratory4C, echo = FALSE}
dataformodel <- data_no_CBCL_outliers_males

exploratory4c_bisbas_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            bisbas_ss_basm_rr+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4c_bisbas_males$gam )
```

```{r}
#Quick plots
plot_model(exploratory4c_bisbas_males$gam,type = "pred", terms = c("PDS_score_z","bisbas_ss_basm_rr [-2.0,0,2.0]"),show.data = FALSE) #Interaction plot

#plot_model(exploratory4a_compositestriatum_feedback_allCBCL_males$mer,type = "std", show.data = FALSE) #Not working
```
## Males, all CBCL, BIS/BAS
```{r Exploratory4C, echo = FALSE}
dataformodel <- PDS_correct_males

exploratory4c_bisbas_allCBCL_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            bisbas_ss_basm_rr+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4c_bisbas_allCBCL_males$gam )
```





# Exploratory Hypothesis 4D: We hypothesize that the association between advanced puberty and internalizing symptoms will be moderated by behavioral reward responsiveness (i.e., MID reaction time). We predict that advanced puberty will be associated with higher internalizing in individuals who demonstrate lower behavioral reward responsiveness.
## Model: CBCL internalizing factor ~ PDS*MID reaction time
```{r Exploratory4D, echo = FALSE}
#FEMALES
dataformodel <- data_no_RT_MID_CBCL_outliers_females

#LARGE REWARD VS. NEUTRAL POSITIVE
exploratory4c_lg_neutral_RT_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            rt_diff_large_neutral_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4c_lg_neutral_RT_females$gam)

#LARGE REWARD VS. SMALL REWARD POSITIVE
exploratory4c_lg_small_RT_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            rt_diff_large_small_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4c_lg_small_RT_females$gam)
```

```{r}
#MALES
dataformodel <- data_no_RT_MID_CBCL_outliers_males

#LARGE REWARD VS. NEUTRAL POSITIVE
exploratory4c_lg_neutral_RT_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            rt_diff_large_neutral_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4c_lg_neutral_RT_males$gam)

#LARGE REWARD VS. SMALL REWARD POSITIVE
exploratory4c_lg_small_RT_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z*
                            rt_diff_large_small_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4c_lg_small_RT_males$gam)

```

# Exploratory Hypothesis 4E: We will investigate whether testosterone, and its relationship with reward, relates to internalizing symptoms, while controlling for PDS.
## Model A: CBCL internalizing factor ~ Testosterone*Striatal activity (anticipation stage) + PDS
## Model B: CBCL internalizing factor ~ Testosterone*Striatal activity (feedback stage) + PDS
## Model C: CBCL internalizing factor ~ Testosterone*OFC activity (anticipation stage) + PDS
## Model D: CBCL internalizing factor ~ Testosterone*OFC activity (feedback stage) + PDS
## Model E: CBCL internalizing factor ~ Testosterone*BIS-BAS RR
## Model F: CBCL internalizing factor ~ Testosterone*MID Reaction Time


## Females, all outliers in CBCL, striatal anticipation, testosterone
```{r}
dataformodel <- data_no_striatal_ant_test_outliers_females

confirmatory4Ea_striatum_allCBCLL_test_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z+
                            hormone_scr_ert_mean_z*
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4Ea_striatum_allCBCLL_test_females$gam)
```

## Males, all outliers in CBCL, striatal anticipation, testosterone
```{r}
dataformodel <- data_no_striatal_ant_test_outliers_males

exploratory4Ea_striatum_allCBCLL_test_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z+
                            hormone_scr_ert_mean_z*
                            striatum_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4Ea_striatum_allCBCLL_test_males$gam)
```

## Females, all outliers in CBCL, striatal feedback, testosterone
```{r}
dataformodel <- data_no_striatal_feed_outliers_females

exploratory4Ea_striatum_feedback_allCBCL_test_females  <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z+
                            hormone_scr_ert_mean_z*
                            striatum_posvsneg_feedback_z+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4Ea_striatum_feedback_allCBCL_test_females$gam )
```
## Males, all outliers in CBCL, striatal feedback, testosterone
```{r}
dataformodel <- data_no_striatal_feed_outliers_males

exploratory4Ea_striatum_feedback_allCBCL_test_males  <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score_z+
                            hormone_scr_ert_mean_z*
                            striatum_posvsneg_feedback_z+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(exploratory4Ea_striatum_feedback_allCBCL_test_males$gam )
```


#Exploring whether BIS/BAS is related to brain activity  -- no association with any of the brain regions or stages

#BISBAS_striatal_anticipation
```{r}
dataformodel <- data_no_striatal_ant_outliers
bisbas_striatal_ant <- gamm4(striatum_rvsn_ant_z ~ 
                        #    bisbas_ss_basm_rr+
                            sex,#+
                         #   race.ethnicity.5level +
                        #    demo_race_hispanic +
                        #    high.educ +
                        #    household.income +
                        #    married.or.livingtogether +
                        #    interview_age, 
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(bisbas_striatal_ant$gam )
```

#BISBAS_striatal_feedback
```{r}
dataformodel <- data_no_striatal_feed_outliers
bisbas_striatal_feed <- gamm4(striatum_posvsneg_feedback_z ~ 
                            #bisbas_ss_basm_rr+
                            sex,#+
                            #race.ethnicity.5level +
                            #demo_race_hispanic +
                            #high.educ +
                            #household.income +
                            #married.or.livingtogether +
                            #interview_age, 
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(bisbas_striatal_feed$gam )
```


#BISBAS_lOFC_anticipation
```{r}
dataformodel <- data_no_lOFC_ant_outliers
bisbas_lOFCanticipation <- gamm4(lOFC_posvsneg_feedback_z ~ 
                            striatum_posvsneg_feedback_z,#+
                           # sex,#+
                            #race.ethnicity.5level +
                            #demo_race_hispanic +
                            #high.educ +
                            #household.income +
                            #married.or.livingtogether +
                            #interview_age, 
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(bisbas_lOFCanticipation$gam )
```

#BISBAS_lOFC_feedback
```{r}
dataformodel <- data_no_lOFC_feed_outliers
bisbas_lOFCfeedback <- gamm4(lOFC_posvsneg_feedback_z ~ 
                            #bisbas_ss_basm_rr+
                            sex
                            #race.ethnicity.5level +
                            #demo_race_hispanic +
                            #high.educ +
                            #household.income +
                            #married.or.livingtogether +
                            #interview_age
                            ,
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(bisbas_lOFCfeedback$gam )
```

#BISBAS_lOFC_feedback
```{r}
dataformodel <- data_no_lOFC_feed_outliers
bisbas_lOFCfeedback <- gamm4(lOFC_posvsneg_feedback_z ~ 
                            #bisbas_ss_basm_rr+
                            sex
                            #race.ethnicity.5level +
                            #demo_race_hispanic +
                            #high.educ +
                            #household.income +
                            #married.or.livingtogether +
                            #interview_age
                            ,
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(bisbas_lOFCfeedback$gam )
```
#Females testosterone and age
```{r}
dataformodel <- PDS_correct_females
testosterone_age_females  <- gamm4(hormone_scr_ert_mean_z ~ 
                            #bisbas_ss_basm_rr+
                            #race.ethnicity.5level +
                            #demo_race_hispanic +
                            #high.educ +
                            #household.income +
                            #married.or.livingtogether +
                            interview_age
                            ,
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(testosterone_age_males $gam )
```
#Females testosterone and PDS
```{r}
dataformodel <- PDS_correct_females
testosterone_pds_females  <- gamm4(hormone_scr_ert_mean_z ~
                                     PDS_score_z+
                            #bisbas_ss_basm_rr+
                            #race.ethnicity.5level +
                            #demo_race_hispanic +
                            #high.educ +
                            #household.income +
                            #married.or.livingtogether +
                            interview_age
                            ,
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(testosterone_pds_females $gam )
```


#Males testosterone and PDS
```{r}
dataformodel <- PDS_correct_males
testosterone_pds_males  <- gamm4(hormone_scr_ert_mean_z ~
                                     PDS_score+
                            #bisbas_ss_basm_rr+
                            #race.ethnicity.5level +
                            #demo_race_hispanic +
                            #high.educ +
                            #household.income +
                            #married.or.livingtogether +
                            interview_age
                            ,
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(testosterone_pds_males $gam )
```




#Males Testosterone and age males
```{r}
dataformodel <- PDS_correct_males
testosterone_age_males <- gamm4(hormone_scr_ert_mean_z ~ 
                                  PDS_score+
                            #bisbas_ss_basm_rr+
                            #race.ethnicity.5level +
                            #demo_race_hispanic +
                            #high.educ +
                            #household.income +
                            #married.or.livingtogether +
                            interview_age
                            ,
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(testosterone_age_males $gam )
```
#Males age and PDS 
```{r}
dataformodel <- PDS_correct_males
age_pds_males<- gamm4(PDS_score ~ 
                            #bisbas_ss_basm_rr+
                            #race.ethnicity.5level +
                            #demo_race_hispanic +
                            #high.educ +
                            #household.income +
                            #married.or.livingtogether +
                            interview_age
                            ,
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(age_pds_males$gam )
```


#Females PDS and age
```{r}
dataformodel <- PDS_correct_females
PDS_age_females  <- gamm4(PDS_score ~ 
                            #bisbas_ss_basm_rr+
                            #race.ethnicity.5level +
                            #demo_race_hispanic +
                            #high.educ +
                            #household.income +
                            #married.or.livingtogether +
                            interview_age  
                            ,
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(PDS_age_females$gam)
```
#Dummy model to check effect sizes, regressing two very correlated variables does give an Rsq of 0.70
```{r}
dataformodel <- PDS_correct_females
PDS_age_females_score_category  <- gamm4(PDS_score_z ~ 
                            #bisbas_ss_basm_rr+
                            #race.ethnicity.5level +
                            #demo_race_hispanic +
                            #high.educ +
                            #household.income +
                            #married.or.livingtogether +
                            pds_p_ss_category  
                            ,
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())


PDS_age_females_score_category <- lm(PDS_score_z ~pds_p_ss_category    ,
                            data=dataformodel)
summary(PDS_age_females_score_category)
#We get comparable Rsq with lm and gamm
```

# Confirmatory Hypothesis 4: Anticipation, SEPARATE REGIONS

##  Model: CBCL internalizing factor ~ PDS*Striatal activity (anticipation stage)

### Females
```{r Confirmatory4Accumbens_Females, echo = FALSE}
# Composite striatum score, exlcuding outliers.
# No CBCL exclusions
# With covariates

dataformodel <- data_no_accumbens_ant_outliers_females  #Specify data subset here

confirmatory4_accumbens_ant_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score*
                            accumbens_rvsn_ant_z+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age,
                            data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4_accumbens_ant_females$gam)
plot_model(confirmatory4_accumbens_ant_females,type = "int", show.data = TRUE) #Interaction plot
```

###Females
```{r Confirmatory4Putamen_Females, echo = FALSE}
# Composite striatum score, exlcuding outliers.
# No CBCL exclusions
# With covariates

dataformodel <- data_no_putamen_ant_outliers_females  #Specify data subset here

confirmatory4_putamen_ant_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            interview_age+
                            PDS_score*
                            putamen_rvsn_ant_z+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether 
                            , data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4_putamen_ant_females$gam)
```

###Females
```{r Confirmatory4Caudate_Females, echo = FALSE}
# Composite striatum score, exlcuding outliers.
# No CBCL exclusions
# With covariates

dataformodel <- data_no_caudate_ant_outliers_females  #Specify data subset here

confirmatory4_caudate_ant_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            interview_age+
                            PDS_score*
                            caudate_rvsn_ant_z+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether 
                            , data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4_caudate_ant_females$gam)
```



###Males
```{r Confirmatory4Accumbens_males, echo = FALSE}
# Accumbens anticipation exlcuding outliers.
# No CBCL exclusions
# With covariates

dataformodel <- data_no_accumbens_ant_outliers_males  #Specify data subset here

confirmatory4_accumbens_ant_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            interview_age+
                            PDS_score*
                            accumbens_rvsn_ant_z+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether 
                            , data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4_accumbens_ant_males$gam)
plot_model(confirmatory4_accumbens_ant_males,type = "int", show.data = TRUE) #Interaction plot
```

###Males
```{r Confirmatory4Putamen_Males, echo = FALSE}
# Putamen anticipation exlcuding outliers.
# No CBCL exclusions
# With covariates

dataformodel <- data_no_putamen_ant_outliers_males  #Specify data subset here

confirmatory4_putamen_ant_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            interview_age+
                            PDS_score*
                            putamen_rvsn_ant_z+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether 
                            , data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4_putamen_ant_males$gam)
plot_model(confirmatory4_putamen_ant_males,type = "int", show.data = TRUE) #Interaction plot
```

###Males
```{r Confirmatory4Caudate_Males, echo = FALSE}
# Composite striatum score, exlcuding outliers.
# No CBCL exclusions
# With covariates

dataformodel <- data_no_caudate_ant_outliers_males  #Specify data subset here

confirmatory4_caudate_ant_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            interview_age+
                            PDS_score*
                            caudate_rvsn_ant_z+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether 
                            , data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())

summary(confirmatory4_caudate_ant_males$gam)
```

# Exploratory Hypothesis 4: SEPARATE REGIONS

##  Model: CBCL internalizing factor ~ PDS*striatal (separate regions) activity (feedback stage)

###Females
```{r Exploratory4Accumbens_Females, echo = FALSE}
# Accumbens feedback, exlcuding outliers.
# No CBCL exclusions
# With covariates

dataformodel <- data_no_accumbens_feed_outliers_females

exploratory4a_accumbens_feedback_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score*
                            accumbens_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4a_accumbens_feedback_females$gam )
```

###Females
```{r Exploratory4Caudate_Females, echo = FALSE}
# Caudate feedback, exlcuding outliers.
# No CBCL exclusions
# With covariates

dataformodel <- data_no_caudate_feed_outliers_females

exploratory4a_caudate_feedback_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score*
                            caudate_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4a_caudate_feedback_females$gam )
```

###Females
```{r Exploratory4Putamen_Females, echo = FALSE}
# Putamen feedback, exlcuding outliers.
# No CBCL exclusions
# With covariates
dataformodel <- data_no_putamen_feed_outliers_females

exploratory4a_putamen_feedback_females <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score*
                            putamen_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4a_putamen_feedback_females$gam )
```

###Males
```{r Exploratory4Accumbens_Males, echo = FALSE}
#Accumbens feedback, maleS

dataformodel <- data_no_accumbens_feed_outliers_males

exploratory4a_accumbens_feedback_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score*
                            accumbens_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4a_accumbens_feedback_males$gam )
```
###Males
```{r Exploratory4Caudate_Females, echo = FALSE}
#Caudate feedback", maleS

dataformodel <- data_no_caudate_feed_outliers_males

exploratory4a_caudate_feedback_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score*
                            caudate_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4a_caudate_feedback_males$gam )
```
###Males
```{r Exploratory4Putamen_Females, echo = FALSE}
#Putamen feedback", maleS

dataformodel <- data_no_putamen_feed_outliers_males

exploratory4a_putamen_feedback_males <- gamm4(cbcl_scr_syn_internal_r ~ 
                            PDS_score*
                            putamen_posvsneg_feedback_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4a_putamen_feedback_males$gam )
```

###Depression only
```{r Exploratory4Accumbens_Males, echo = FALSE}
#Accumbens feedback, maleS

dataformodel <- data_no_accumbens_feed_outliers_males

#cbcl_scr_dsm5_depress_r ~
#cbcl_scr_syn_internal_r ~

exploratory4a_accumbens_feedback_males <- gamm4(
                           cbcl_scr_dsm5_depress_r ~
                            PDS_score*
                            accumbens_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4a_accumbens_feedback_males$gam)


coef_test(exploratory4a_accumbens_feedback_males$mer, vcov = "CR2", coeffs = "all")
```

###Anxiety only
```{r Exploratory4Accumbens_Males, echo = FALSE}
#Accumbens feedback, maleS

dataformodel <- data_no_accumbens_feed_outliers_males

#cbcl_scr_dsm5_depress_r ~
#cbcl_scr_syn_internal_r ~

exploratory4a_accumbens_feedback_males <- gamm4(
                            cbcl_scr_dsm5_depress_r ~
                            PDS_score*
                            accumbens_rvsn_ant_z+
                            #sex+
                            race.ethnicity.5level +
                            demo_race_hispanic +
                            high.educ +
                            household.income +
                            married.or.livingtogether +
                            interview_age, data=dataformodel, random = ~ (1 | site_id_l/rel_family_id),family=gaussian())
summary(exploratory4a_accumbens_feedback_males$gam)


coef_test(exploratory4a_accumbens_feedback_males$mer, vcov = "CR2", coeffs = "all")
# beta = -0.35; t= -0.64; p = 0.53.
```