---
title: "Research Question 1: Research Question 1: Does pubertal development relate to neural and behavioral responses to reward?"
date: "August 2020"
output:
  html_document: default
  pdf_document: default
authors: Natalie Saragosa-Harris 
---
``` {r loadPackages, echo = FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(gamm4)
library(dplyr)
library(sjPlot)
library(here)
```

```{r LoadData, echo = FALSE}

# Elizabeth.
# Data: Desktop⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code: Desktop⁩ ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code⁩

# Lucia.
# Data:  Github⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Github ▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# Natalie.
# Data:  Desktop ▸ ABCD⁩ ▸ ⁨ABCD⁩ ▸ ⁨derivatives⁩ ▸ ⁨exploratory⁩
# Code:  Desktop ▸ ABCD ⁩▸ ⁨rewardprocesses_internalizing_puberty_exploratory⁩ ▸ ⁨code

# LMW alternative to read in the data.

data_dir = ((dirname(here()))) 

phase_folder = "confirmatory"  # select the appropiate folder.
#phase_folder = "confirmatory"  # select the appropiate folder.

data_folder <- file.path(data_dir,"ABCD","derivatives",phase_folder)

file_name <- "nda30_confirmatory.csv" # specify file name here. 

fulldata <- read.csv(file.path(data_folder,file_name))
length(fulldata$src_subject_id) # 5935.

# Call function to define all of the dataframes.
script_path <- file.path(data_dir,"rewardprocesses_internalizing_puberty_exploratory","code","define_dataframes.R")
source(script_path)

min(PDS_correct$interview_age)
max(PDS_correct$interview_age)
mean(PDS_correct$interview_age)

female_subset <- subset(fulldata, sex=="F")
male_subset <- subset(fulldata, sex=="M")


#Full data females N=2841
#PDS_correct females N=2069

#Full data males N=3094
#PDS_correct males N=2173
```

```{r settheme, echo = FALSE}
nsh_theme <- theme(title= element_text(size=26, vjust=2, face="bold"),
         plot.title = element_blank(),
         axis.title.x= element_text(size=18, vjust=-0.3),
         axis.title.y= element_text(size=18, vjust=1.5),
         axis.text.x= element_text(size=18, colour="black"),
         axis.text.y= element_text(size=18, colour="black"),
         strip.text = element_text(size=24, face="bold"),
         panel.background = element_blank(),
         axis.line = element_line(colour = "black"))

```

# Confirmatory Hypothesis 1: We hypothesize that pubertal stage will be associated with neural response to reward during a monetary incentive delay task (Braams et al., 2015). In particular, we expect heightened striatal activation during reward anticipation for more advanced pubertal stages.
## Model: Striatal activation (anticipation stage) ~ Pubertal stage

#### Females.
```{r Confirmatory1Female, echo = FALSE}
dataformodel <- data_no_striatal_ant_outliers_females

confirmatory1_females <- gamm4(striatum_rvsn_ant_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(confirmatory1_females$gam)

# None of these plots are working?
#plot.gam(confirmatory1_females$gam,residuals=TRUE,all.terms=TRUE)
#plot_model(confirmatory1_females$mer,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_females$mer,type = "est", show.data = FALSE) # forest plot.
```

#### Males.
```{r Confirmatory1Male, echo = FALSE}
dataformodel <- data_no_striatal_ant_outliers_males

confirmatory1_males<- gamm4(striatum_rvsn_ant_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(confirmatory1_males$gam)

#plot_model(confirmatory1_males,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_males,type = "est", show.data = FALSE) # forest plot.
```

# Exploratory Hypothesis 1A: We will explore whether striatal activation during reward feedback is related to pubertal stage.
## Model: Striatal activation (feedback stage) ~ Pubertal stage
## Females.
```{r Exploratory1AFemales, echo = FALSE}
dataformodel <- data_no_striatal_feed_outliers_females

exploratory1A_females <- gamm4(striatum_posvsneg_feedback_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(exploratory1A_females$gam)

```

## Males.
```{r Exploratory1AMales, echo = FALSE}
dataformodel <- data_no_striatal_feed_outliers_males

exploratory1A_males <- gamm4(striatum_posvsneg_feedback_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(exploratory1A_males$gam)

```
# Exploratory Hypothesis 1B: We hypothesize that more advanced pubertal stages will be associated with greater self-reported reward responsiveness (BAS - RR) (Harden et al. 2018).
## Model: BIS-BAS-RR ~ Pubertal stage
# Females.
```{r Exploratory1BFemales, echo = FALSE}
dataformodel <- data_no_bisbas_outliers_females

exploratory1B_females <- gamm4(bisbas_ss_basm_rr_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(exploratory1B_females$gam)
coef_test(exploratory1B_females$mer, vcov = "CR2", coeffs = "all")
# beta = 0.03; t = 0.65; p = 0.52.

```
# Males.
```{r Exploratory1BMales, echo = FALSE}
dataformodel <- data_no_bisbas_outliers_males

exploratory1B_males <- gamm4(bisbas_ss_basm_rr_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(exploratory1B_males$gam)
coef_test(exploratory1B_males$mer, vcov = "CR2", coeffs = "all")
# beta = 0.04; t = 0.48; p = 0.64.
```
# Exploratory Hypothesis 1C: We hypothesize that greater pubertal stage will be associated with greater behavioral reactivity to reward (i.e., reaction time on reward vs. neutral trials).
## Model: Reaction Time ~ Pubertal Stage

# Females.
```{r Exploratory1CFemales, echo = FALSE}
dataformodel <- data_no_RT_MID_outliers_females

#LARGE REWARD VS. NEUTRAL POSITIVE
exploratory1C_lg_neutral_RT_females <- gamm4(rt_diff_large_neutral_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(exploratory1C_lg_neutral_RT_females$gam)
coef_test(exploratory1C_lg_neutral_RT_females$mer, vcov = "CR2", coeffs = "all")
# beta = 0.001; t = 0.042; p = 0.97.

#LARGE REWARD VS. SMALL POSITIVE
exploratory1C_lg_small_RT_females <- gamm4(rt_diff_large_small_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(exploratory1C_lg_small_RT_females$gam)
```

# Males..
```{r Exploratory1CMales, echo = FALSE}
dataformodel <- data_no_RT_MID_outliers_males

#LARGE REWARD VS. NEUTRAL POSITIVE
exploratory1C_lg_neutral_RT_males <- gamm4(rt_diff_large_neutral_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(exploratory1C_lg_neutral_RT_males$gam)
coef_test(exploratory1C_lg_neutral_RT_males$mer, vcov = "CR2", coeffs = "all")
# beta = 0.004; t = 0.07; p = 0.95.

#SMALL REWARD VS. NEUTRAL POSITIVE
exploratory1C_lg_small_RT_males <- gamm4(rt_diff_large_small_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(exploratory1C_lg_small_RT_males$gam)
```
# Exploratory Hypothesis 1D: We hypothesize that testosterone will be positively associated with our indicators of reward (neural activity, behavioral reaction time, and self-reported reward responsiveness).
## Model A: Striatal activation (anticipation stage) ~ Testosterone
```{r}
## Model A: Striatal activation (anticipation stage) ~ Testosterone
# Females.
dataformodel <- data_no_striatal_ant_test_outliers_females # No striatal anticipation or testosterone outliers.
modelA_females <- gamm4(striatum_rvsn_ant_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelA_females$gam)

# Males.
dataformodel <- data_no_striatal_ant_test_outliers_males # No striatal anticipation or testosterone outliers.
modelA_males <- gamm4(striatum_rvsn_ant_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelA_males$gam)

```
## Model B: Striatal activation (feedback stage) ~ Testosterone
```{r}
## Model B: Striatal activation (feedback stage) ~ Testosterone
# Females.
dataformodel <- data_no_striatal_feed_test_outliers_females # No striatal feedback or testosterone outliers.
modelB_females <- gamm4(striatum_posvsneg_feedback_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelB_females$gam)

# Males.
dataformodel <- data_no_striatal_feed_test_outliers_males # No striatal feedback or testosterone outliers.
modelB_males <- gamm4(striatum_posvsneg_feedback_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelB_males$gam)

```
## Model C: OFC activation (anticipation stage) ~ Testosterone
```{r}
## Model C: OFC activation (anticipation stage) ~ Testosterone

# Females (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_ant_test_outliers_females
modelC_females_lOFC <- gamm4(lOFC_rvsn_ant_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelC_females_lOFC$gam)

# Males (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_ant_test_outliers_males
modelC_males_lOFC <- gamm4(lOFC_rvsn_ant_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelC_males_lOFC$gam)

# Females (medial OFC; mOFC).
dataformodel <- data_no_mOFC_ant_test_outliers_females
modelC_females_mOFC <- gamm4(mOFC_rvsn_ant_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelC_females_mOFC$gam)

# Males (medial OFC; mOFC).
dataformodel <- data_no_mOFC_ant_test_outliers_males
modelC_males_mOFC <- gamm4(mOFC_rvsn_ant_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelC_males_mOFC$gam)

```

## Model D: OFC activation (feedback stage) ~ Testosterone
```{r}
## Model D: OFC activation (feedback stage) ~ Testosterone

# Females (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_feed_test_outliers_females
modelD_females_lOFC <- gamm4(lOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelD_females_lOFC$gam)

# Males (lateral OFC; lOFC).
dataformodel <- data_no_lOFC_feed_test_outliers_males
modelD_males_lOFC <- gamm4(lOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelD_males_lOFC$gam)

# Females (medial OFC; mOFC).
dataformodel <- data_no_mOFC_feed_test_outliers_females
modelD_females_mOFC <- gamm4(mOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelD_females_mOFC$gam)

# Males (medial OFC; mOFC).
dataformodel <- data_no_mOFC_feed_test_outliers_males
modelD_males_mOFC <- gamm4(mOFC_posvsneg_feedback_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelD_males_mOFC$gam)
```

## Model E: MID Reaction Time ~ Testosterone
```{r Exploratory1D, echo = FALSE}
## Model E: MID Reaction Time ~ Testosterone
# Females - LARGE REWARD VS. NEUTRAL
dataformodel <- data_no_RT_test_outliers_females # No MID RT difference score or testosterone outliers.
modelE_lg_neutral_RT_females <- gamm4(rt_diff_large_neutral_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelE_lg_neutral_RT_females$gam)

# Females - LARGE REWARD VS. SMALL REWARD
dataformodel <- data_no_RT_test_outliers_females # No MID RT difference score or testosterone outliers.
modelE_lg_small_RT_females <- gamm4(rt_diff_large_small_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelE_lg_small_RT_females$gam)
```

```{r}
# Males - LARGE REWARD VS. NEUTRAL
dataformodel <- data_no_RT_test_outliers_males # No MID RT difference score or testosterone outliers.

modelE_lg_neutral_RT_males <- gamm4(rt_diff_large_neutral_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelE_lg_neutral_RT_males$gam)

# Males - LARGE REWARD VS. SMALL REWARDS
modelE_lg_small_RT_males <- gamm4(rt_diff_large_small_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelE_lg_small_RT_males$gam)
```

## Model F: BIS-BAS-RR ~ Testosterone
```{r Exploratory1D, echo = FALSE}

## Model F: BIS-BAS-RR ~ Testosterone
dataformodel <- data_no_bisbas_test_outliers_females
modelF_females <- gamm4(bisbas_ss_basm_rr_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelF_females$gam)

dataformodel <- data_no_bisbas_test_outliers_males
modelF_males <- gamm4(bisbas_ss_basm_rr_z ~ hormone_scr_ert_mean_z +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(modelF_males$gam)
```


# Confirmatory Hypothesis 1 SEPARATE REGIONS

## Model: Striatal activation (anticipation stage) ~ Pubertal stage

#### Caudate Anticipation Females.
```{r Confirmatory1Female, echo = FALSE}
dataformodel <- data_no_caudate_ant_outliers_females 

confirmatory1_caudate_females <- gamm4(caudate_rvsn_ant_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(confirmatory1_caudate_females$gam)

# None of these plots are working?
#plot.gam(confirmatory1_females$gam,residuals=TRUE,all.terms=TRUE)
#plot_model(confirmatory1_females$mer,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_females$mer,type = "est", show.data = FALSE) # forest plot.
```

#### Caudate Anticipation Males
```{r Confirmatory1Male, echo = FALSE}
dataformodel <- data_no_striatal_ant_outliers_males

confirmatory1_caudate_males<- gamm4(caudate_rvsn_ant_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)
summary(confirmatory1_caudate_males$gam)

#plot_model(confirmatory1_males,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_males,type = "est", show.data = FALSE) # forest plot.
```

#### Putamen Anticipation Females.
```{r Confirmatory1Female, echo = FALSE}
dataformodel <- data_no_putamen_ant_outliers_females 

confirmatory1_putamen_females <- gamm4(putamen_rvsn_ant_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(confirmatory1_putamen_females$gam)

# None of these plots are working?
#plot.gam(confirmatory1_females$gam,residuals=TRUE,all.terms=TRUE)
#plot_model(confirmatory1_females$mer,type = "pred", terms = "PDS_score", show.data = FALSE)
#plot_model(confirmatory1_females$mer,type = "est", show.data = FALSE) # forest plot.
```

#### Putamen Anticipation Males.
```{r Confirmatory1Female, echo = FALSE}
dataformodel <- data_no_putamen_ant_outliers_males 

confirmatory1_putamen_males <- gamm4(putamen_rvsn_ant_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(confirmatory1_putamen_males$gam)

```

#### Accumbens Anticipation Females.
```{r Confirmatory1Female, echo = FALSE}
dataformodel <- data_no_accumbens_ant_outliers_females 

confirmatory1_accumbens_females <- gamm4(accumbens_rvsn_ant_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(confirmatory1_accumbens_females$gam)
coef_test(confirmatory1_accumbens_females$mer, vcov = "CR2", coeffs = "all")
# beta = -0.05; t = -1.27; p = 0.22.
```

#### Accumbens Anticipation Males.
```{r Confirmatory1Female, echo = FALSE}
dataformodel <- data_no_accumbens_ant_outliers_males 

confirmatory1_accumbens_males <- gamm4(accumbens_rvsn_ant_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(confirmatory1_accumbens_males$gam)
coef_test(confirmatory1_accumbens_males$mer, vcov = "CR2", coeffs = "all")
# beta = 0.04; t = 0.73; p = 0.48.
```

# Exploratory Hypothesis 1A: SEPARATE REGIONS
## Model: Striatal activation (feedback stage) ~ Pubertal stage

#### Caudate Feedback Females.
```{r Exploratory1A_Caudate_Females, echo = FALSE}
dataformodel <- data_no_caudate_feed_outliers_females

exploratory1A_caudate_females <- gamm4(caudate_posvsneg_feedback_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(exploratory1A_caudate_females$gam)

```
#### Caudate Feedback Males.
```{r Exploratory1A_Caudate_Males, echo = FALSE}
dataformodel <- data_no_caudate_feed_outliers_males

exploratory1A_caudate_males <- gamm4(caudate_posvsneg_feedback_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(exploratory1A_caudate_males$gam)

```

#### Putamen Feedback Females.
```{r Exploratory1A_Putamen_Females, echo = FALSE}
dataformodel <- data_no_putamen_feed_outliers_females

exploratory1A_putamen_females <- gamm4(putamen_posvsneg_feedback_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(exploratory1A_putamen_females$gam)

```

#### Putamen Feedback Males.
```{r Exploratory1A_Putamen_males, echo = FALSE}
dataformodel <- data_no_putamen_feed_outliers_males

exploratory1A_putamen_males <- gamm4(putamen_posvsneg_feedback_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(exploratory1A_putamen_males$gam)

```
#### Accumbens Feedback Females.
```{r Exploratory1A_Accumbens_Females, echo = FALSE}
dataformodel <- data_no_accumbens_feed_outliers_females

exploratory1A_accumbens_females <- gamm4(accumbens_posvsneg_feedback_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(exploratory1A_accumbens_females$gam)
coef_test(exploratory1A_accumbens_females$mer, vcov = "CR2", coeffs = "all")
# beta = 0.07; t = 1.68; p = 0.11.
```

#### Accumbens Feedback Males.
```{r Exploratory1A_Accumbens_Males, echo = FALSE}
dataformodel <- data_no_accumbens_feed_outliers_males

exploratory1A_accumbens_males <- gamm4(accumbens_posvsneg_feedback_z ~ PDS_score +
                      race.ethnicity.5level +
                      high.educ +
                      household.income +
                      married.or.livingtogether +
                      interview_age +
                      demo_race_hispanic, 
                      random = ~ (1 | site_id_l/rel_family_id),
                      data = dataformodel)

summary(exploratory1A_accumbens_males$gam)
coef_test(exploratory1A_accumbens_males$mer, vcov = "CR2", coeffs = "all")
# beta = -0.02; t = -0.38; p = 0.71.

```